He'd come out of the dark paths to plenty of surprises\textemdash enraged genies and merely excitable ones, a volcano and a sinking island once, and once a rain of frogs\textemdash and that was before he'd lost and then regained the knack of it, traveling now on the King's orders. In the year since Mickey had sent that message in a bottle and everything that had come after, he'd roamed further and further afield, out past the easy paths worn by gummi travel and the ties between worlds' hearts and into the real dark, worlds known more by rumor than report.

Stepping from a dark portal into the midst of a pitched battle was never high on his list of things to do, but it wasn't the whine of gunfire and the shock of magic released at his back or the massive line of Heartless beginning a ponderous charge before him that shocked him careless for just a moment too long. It was the startled curse and the solid form that hit him like a runaway train, tackling him to the dirt and rolling them both until the stranger had him covered with the man's own body as some nasty bit of magic went crackling overhead.

Breathless, nonplused, he stared up into wide violet eyes just in time to see stunned hope collapse, the man's face crumpling into resignation and sheepish amusement as he watched.
``Sorry 'bout that,'' the man said, scrubbing a hand through wild black spikes. ``Er\ldots actually, no, I'm not.''

``What was that?'' Riku asked, glancing warily at the approaching Heartless and the line of fortifications behind him, little more than a hastily cobbled-together wall. He could see maybe a dozen men, all of them in identical charcoals like the guy who'd tackled him, and all of them were staring at him in varying degrees of shock.

``Uh\ldots reflex?''

``I meant the spell.''

``Scourge, if Hall got it right,'' the guy said, hauling him to his feet with a hand under his elbow and urging him back to the others. ``New spells, new ways to screw up royally,'' he added cheerfully.

``So you're not from this world?''

``How'd you\textemdash ?''

``Down!'' someone shouted, and Riku whipped around, saw a Bolt Tower's flash heading their way, and jerked his hands up, throwing out a dark shield for it to shatter harmlessly off of.

He yelped despite himself when a huge hand closed on the back of his coat\textemdash still Organization black, but not nearly so distinctive\textemdash and lifted him over the wall as easily as a mama cat dragging off a stubborn kitten. The dark-haired guy went over under his own power, and Riku narrowed his eyes at the way the man was grinning, violet eyes shifting between him and the giant who'd grabbed him by the scruff.

Funny, the way the guy's eyes glowed. Just like Cloud's\ldots or Sephiroth's.

``Please don't tell me you're trying to stop an entire Heartless army by yourselves,'' he deadpanned, taking another headcount and\ldots yeah, twelve on the nose. Against all that.

``It's a dirty job,'' the friendly guy said with a shrug, sticking out his hand. 

``Zack Fair.''

``Riku.''

``Pleased to meet you, kid. So listen, the town's about a mile up the hill if you want to get a head start. We'll be along once we've taken care of this mess,'' he said, jerking his head towards the mass of darkness coming their way.

``Are you serious?''

``Hey,'' Zack said. ``we're SOLDIERs First Class.''

Riku blinked, brows arching as that sank in. ``Okay\ldots that does even the odds,'' he admitted, ignoring Zack's start and the way the guy's eyes got wide and fragile again. ``Look. I'll need you to flank them. Bunch them up if you can, so I can take out as many as possible in one go. Just try not to get too close to me, because I won't be able to watch for you.''

``What?'' Zack sputtered as Riku got to his feet again, calling Way to Dawn\textemdash Soul Eater\textemdash to him.

``Just trust me,'' he said, taking a good long look at what was coming and nearly missing Zack's incredulous laugh, his snapped salute.

``Yes, sir, mini-Boss, sir!''

Vaulting over the embankment, Riku took off at a dead sprint, bracing himself and angling his Keyblade so that when he hit the first ranks, he plowed into them like a scythe, spinning with all his momentum behind him to clear himself a space in which to stand. The darkness was thrumming inside him, straining to rend and devour, but he waited until the Heartless were nearly too thick around him for breathing room before he turned it loose, grimacing as thick pillars of darkness howled up on every side, scattering the Heartless to shreds and flickering hearts.

It was the light he called on next, as much to clear the air as to give his darkness time to replenish itself. Despite what he'd said to Zack, when he had the chance, he kept an eye out for the SOLDIERs fighting with him, not surprised to see them right in the thick of things, holding their own. It made him smile to watch Zack swinging around a sword as big as the one Cloud lugged around, and that he wasn't the only one\textemdash there were four more swordsmen besides him, one guy spinning a polearm that looked heavier than Riku like it was a kid's baton, a few others\textemdash like the giant\textemdash fighting with their fists. Only one of them didn't seem to know any spells, but the grim way he swung that sword of his told Riku he wasn't letting that be any kind of handicap. They were all good\textemdash beyond good. It was just that Riku was starting to run out of steam, magic-wise, and he was still holding the center.

As strong as his light had grown, he healed so fast these days that he didn't bother hauling potions around, but he always stocked an ether or three no matter where he went. There just wasn't time to toss one back as closely as he was pressed, so he set his jaw and set about clearing himself a space the hard way. It was blind chance that made him glance over the heads of the Neoshadows trying to swarm him, catching violet eyes looking back. He couldn't have said what passed between them then, but in less time than it would have taken him to call the man over, Zack had cut a path to his side, moving to take his back as the Heartless surged closer.

``Hey,'' Zack said, and it didn't quite sound like a greeting.

``Yes?''

``How's the view on that side?''

``Boring,'' he said, smiling despite himself at Zack's irreverence. ``Too much of the same thing.''

He felt the concussion of whatever Zack did just then, magic exploding out of him, or\textemdash no, what Cloud called a Limit\textemdash a bright, shattering burst that smelled a little of ozone and a little of fire at the same time. He smelled hearts, sweet and sharp, and that meant dead Heartless, lots of them.

``Wanna swap?'' Zack asked, so innocently Riku found himself laughing out loud, soft and low.

``Love to,'' he said, circling right along with Zack like they could feel the pivot point in their spines.

Shifting his blade to one hand and thumbing off the cap of an ether was so familiar he could have done it in his sleep. One fast swallow and he felt the rush go through him, magic filling him up, enough for what he needed.

``Stick close,'' he called over his shoulder, and without looking back, he reached behind him to curve his free hand to Zack's side, needing the contact to tell the spell what not to hit.

He was still afraid he'd cut it too close when he felt Zack jerk, not away but back toward him, but by then it was too late. Sin Harvest was easily the nastiest spell he knew, and it'd taken a lot of convincing to get Sephiroth to teach it to him, but he'd never been more grateful that he had.

Heartless shredded, collapsed, went up in long streamers of black or exploded like puffballs as their stolen hearts were ripped free. All across the battlefield, the darkness lashed down and shattered everything in its path, and he was just glad the SOLDIERs took one look at what was happening and pulled back out of range before any of them got caught by accident. He would have called out a warning, but he was breathless from the power he'd just poured out, leaning thoughtlessly against the steady figure at his back, solid as a statue.

``Man,'' Zack said, blowing out a harsh sigh. ``Never thought I'd see that again.''

``You are seriously far from home,'' Riku agreed, letting go of Zack to fumble for another ether, still propped up against the SOLDIER since he wasn't positive his legs would hold him.

``I don't guess you know the way back?'' Zack asked, studiedly casual, not moving an inch, though in Zack's place, Riku thought he'd be trying to shake a few answers loose by now.

``Know the way? Yeah. Can I take you there without a gummi ship?'' He felt Zack tense, so slight he wouldn't have noticed if they hadn't been leaning back to back, smelled the sharp spike of weariness and longing Zack could have hidden from just about anyone else. Anyone not a SOLDIER or touched by the darkness, anyway. He knew what he ought to say; taking Kairi through the dark paths had just about killed him the first time, but he was stronger now, knew better how to pace himself. And he didn't know these people, but there'd always been names never spoken amongst the ones he'd made his second family, and what were the odds?

And he'd been silent long enough, and Zack still wasn't asking. It was the sort of stupid, selfless, heroic thing Sora would do, and he trusted that better than he trusted his own judgment when it came to dealing with strangers.

``Well,'' he said, gathering himself to stand on his own two feet. ``I hope you're not in any huge hurry, because it's going to be slow going, I'm afraid.''

He didn't look back at the man behind him, but he didn't have to. He could scent Zack's relief, the anticipation and dawning joy as it sank in that he was really going home. That they all were.

``Lead on, mini-Boss,'' Zack said, his voice so warm Riku could only roll his eyes, and he didn't quite duck out from under Zack's ruffling hand on his head.

He just hoped the stupid nickname didn't stick, because if it turned out Sephiroth wanted these men back, someone just might find out the hard way whether Seph was in the mood to share his toys\textemdash and it might even be him.