\renewcommand{\pfbreakdisplay}{%
\ding{33}\quad\ding{33}\quad\ding{33}}
Stepping through the portal and into a mass of shifting shadows had to be one of the strangest things Zack had ever done in his life. There didn't seem to be anything solid under his feet when he looked down, just eddying layers of bruise-violet and black, wisps peeling up to drift around his boots like fog. Worse was how his eyes kept sliding away when he tried to stare out across the black, focusing and refocusing as perspective shifted with the tide of the dark, one moment an endless void, the next a claustrophobic tunnel. There were no landmarks that he could see, nothing to set a course by, and though he'd probably come this way once before, the emptiness had flashed by too quickly at the time to really bother him.

``Holy,'' Hall yelped behind him, and he turned with a sympathetic grin as the other man came stumbling through, nearly tripping over himself until he realized the not-ground would hold him. ``We've gotta go through this? How many times?''

``As many times as it takes,'' Titus said as he stepped through, calmly shifting Hall to one side to make way for the others. Hall just let himself be moved, staring in rapt fascination at what wasn't under his feet. Titus, solid and immovable as ever, kept his eyes fixed on Zack.

Good thinking. He wouldn't be surprised to find your eyes started playing tricks on you if you stared too long into the abyss, and now he was doubly glad not to be making this trip alone.

One by one they came filing in, some fighting a moment of vertigo like Hall, some stopping dead in their tracks to stare until they were jostled from behind. Stiegler gave the place one disbelieving glare before narrowing his eyes at their disorganized milling. 
``What? Don't tell me you girls are scared of the dark.''

They'd formed up before their last traveler slipped through: Riku, who cast one sharp glance over their ranks, seemed to relax a fraction at what he saw, and immediately turned his gaze outward. Though Zack was tempted to glance behind him again, instead he watched as Riku, focused and intent, oriented himself with the certainty of a compass needle, nodding just past Zack's right shoulder.

``This way,'' He said, voice tight but sure. ``Come on.''

He was off without a backward glance, setting a brisk, confident pace any one of them could have kept up for hours without breaking a sweat. Though the dark fog the kid passed through stole bits of him now and then\textemdash curling up over his boots, snatching at the edges of his long coat\textemdash the silver of his hair kept him always in sight.

``Kind of reminds you of the old days,'' Hall murmured on Zack's left, ``doesn't it?''

Zack grinned and nodded, but he didn't take his eyes off Riku. He wouldn't say he was any kind of expert, but after following the kid around for a day, he didn't think it was his imagination that Riku was moving more stiffly than before, coiled tight and working hard at hiding it. Whatever effort it was costing the kid to pull them through this place, it didn't show in the determined set of his shoulders, the stubborn way he kept his eyes fixed straight ahead.

``Pick up your damn feet, Schumann,'' He heard Stiegler snap once behind him, a startled grunt as someone got elbowed back on course, but otherwise it was a pretty quiet march. The darkness muffled their voices when anyone did speak, and feet kept wanting to wander off at odd angles despite knowing what a bad idea it would be, but worse than that was the eerie feeling that they needed to stay alert, that if trouble showed, it might come at them from any direction at all.

He wasn't sure how long they'd been walking before he realized he'd gotten lost in the monotony himself, that the quiet figure he'd been following had slowed, and he pulled himself up quickly before he could run Riku down. Riku didn't seem to notice. ``There you are,'' the kid muttered, and Zack bit back a sheepish sputter until he realized Riku was talking to himself if anyone.

Holding out a hand, Riku gathered himself visibly, pushed against nothing, and opened a rift in the darkness that swirled up in smoky curls of carbon-black, utterly lightless.

``Go on,'' Riku said, turning his head a little while his eyes remained glued to the portal. ``I'll hold it open.''

Titus went through first without a word, Hall a bare two steps behind, ready with his ever-growing battery of spells to mop up what the big guy didn't knock into next week. It wasn't until Titus rumbled an ``All clear'' from the other side of the portal that the rest of them moved, falling out fast but cautious into unknown territory.

``You too,'' Riku said as Zack came up alongside him, the last ones to go. Though he opened his mouth to argue, Riku ducked behind him before he could sidestep and started to push, one hand braced between Zack's shoulder blades. He could have dug in his feet, but he didn't like how heavily Riku was leaning on him, the slight stumble to the kid's step as he got Zack moving.

Stepping out into broad daylight after the half-lit dimness of the dark corridors had Zack wincing his eyes closed, just for a second. He missed seeing the portal flicker out, though he heard the change when the low thrum of it faded to nothing. Half-turning as Riku's hand fell away from his back, he lifted an arm, ready to catch the kid or offer a shoulder if he faltered, but Riku just came up to stand beside him, a little pale but still on his feet.

``That's weird,'' Ochs said as Riku stiffened and began to frown. Nervously rolling the haft of his voulge between his hands, Ochs caught Zack's eye and hunched a shoulder. ``I mean\ldots where are the people?''

Though they were standing in the middle of a city, in a little cul-de-sac branching off from a street wide enough to have been a main thoroughfare, the place was eerily quiet. There were none of the sounds he would have expected to hear, even if the city's residents had congregated briefly elsewhere: no far-off drone of a crowd, none of the clatter and bustle of tramping feet, carts or cars. No smoke rising over the roofline from any direction, and the cobbled streets had begun to crack and craze, grass pushing up between the stones.

``This place reeks of the dark,'' Riku said tightly, eyes intent but focused past the sagging houses all around. ``I haven't smelled it this strong since\ldots'' Something made him trail off then, mouth twisting unhappily.

``I don't suppose you know where we are?'' Zack asked, more to bring Riku back from his memories than from any real hope that he'd be able to put a name to the place.

``Afraid not. This was just the closest open world.''

``Right. Guess we'd better take a look around, then; if this place isn't as empty as it looks, I'd rather know now than\textemdash ''

He didn't make it more than a step away, head still turned towards Riku, before he noticed that something was wrong. Already distracted, the kid's expression went from sharp to confused in the space of a breath, and when Riku moved automatically to follow, Zack could see the moment when the kid realized the ground wasn't going to be where he expected by the fuzzy alarm in wide eyes gone a startling shade of blue.

He caught the kid just as Riku's legs went out from under him, getting an arm around the kid's shoulders and one hand under an elbow as Riku landed against his shoulder. ``Whoa,'' He said as Riku cursed muzzily, ``easy there. Looks like you maybe overdid it, mini-Boss.''Gaia. He'd known he shouldn't have pushed the kid\textemdash 

``I'm fine,'' Riku grumbled, brushing off Zack's circling arm as he struggled to pull himself straight, not looking at any of them.

``Uh-huh.''Catching two pairs of worried eyes, blue and gold, he jerked his head at the quiet streets and watched Stiegler and Titus melt away from the pack, going to take that look around Zack had been suggesting just moments before. ``Well, this looks like a pretty good place to take a break. What d'you say?''

``Can't leave until I close this world anyway,'' Riku muttered, but he didn't protest when Zack led him over to sit on the low wall of a half-circle fountain, set into the back of a house at the far end of the shady side-street. Riku still looked a bit wobbly as he dropped down, and if Zack had thought all that black had made the kid look pale before, that was before he'd seen Riku go dead white. He didn't like it at all when the kid slumped over, like he was fighting nausea, and hesitated only a moment before resting his hand on Riku's back.

``Hey.'' He was pretty sure he'd get his head bitten off if he tried to apologize, but he couldn't help it if it came though in his tone. ``You going to be okay?''

``I'm fine,'' Riku repeated firmly. ``It just took more fine control than I'm used to. There's not much subtle about a Dark Firaga,'' He added with a determined smirk, meeting Zack's worried look head-on as he sat up, leaning his elbows on his knees.

``I'll bet,'' Zack said, and then, to keep him talking and focused, ``Is that your knack, then?''

``Darkness and light,'' Riku agreed with a nod. ``The only way I'll be starting a real fire is with a match.''

``Still. That's a pretty sweet combination,'' Zack offered. Most of the time when folks were strong in one element, it meant they were weak to the opposite. In Riku's case, he had the problem neatly sewn up.

Riku didn't look convinced. Not envious; just unimpressed.

Zack shrugged. ``Magic's a pretty standard part of SOLDIER training, y'know. Most of us picked up a knack for it when we went through the treatments.'' Riku nodded like he knew enough about the process that made a SOLDIER to follow along, which wasn't too surprising. ``Of course, not all of us can just pick up a spell by seeing it done, like Hall here,'' He continued, grinning at Hall's embarrassed shuffle. ``And for those of us who just couldn't get the hang of it at all, well, there's always materia.''

``Summons?'' Riku asked, perking up as Zack hit on a topic the kid had a more personal stake in.

``Those too, but there's other kinds. They're just really rare.''

``Huh.'' Riku frowned, eyes sharpening as he went thoughtful again, but the question that followed wasn't the one Zack would have expected. Not 'where can I get some?' but: ``What about\ldots Stiegler?'' He asked, arching a brow to inquire whether he'd gotten the name right.

He hadn't realized Riku had noticed that one of them hadn't been using magic in that fight, and he was sort of thrown that that would be Riku's first thought, like he was politely asking why one of Zack's men had been disarmed, and was there anything they could do to fix it?

``The Sarge is something of a special case,'' He said, offering a smile when it looked like Riku might back off and clam up, embarrassed at having brought it up. ``Maybe he'll tell you about it sometime.''

``Right.''

Already the kid was starting to look more rested, the pallor of his fair skin deepening to faint gold as his color returned, and he no longer looked like he might pitch backward into the brackish water of the still fountain if he tried to sit up. He really was in pretty good shape, not quite as tall as Zack but getting there already, solid with muscle, with the stamina of three to keep up the pace he'd set to get them here when he was that close to dropping. He could joke, at least, which probably put him one up on Seph at that age, but once he got serious, he tended to stay that way.

It was to see if he couldn't drag a smile out of the kid that he nodded meaningfully Riku's way and asked, ``So\ldots what does Sephiroth think of the coat?''

Riku snorted, the corners of his mouth pulling down in a desperate attempt not to laugh. ``First he tells me to stay out of Cloud's closet, then he bitches at me if I don't wear it. It's got protections against the darkness, so you don't lose your heart when you're traveling the dark paths,'' He explained, smirking like he knew very well how uncanny the resemblance was between him and Sephiroth, how Seph had felt about his fan club back in the day. And though he couldn't quite see Sephiroth bitching\ldots

``You mean he gives you that look,'' He said, grinning at the memory, only to feel his breath catch as Riku's face went cool and chiding, a touch long-suffering beneath the rebuke.

``You're not invulnerable,'' Riku said, dropping his voice, and though he couldn't counterfeit the same deep, rich tone, the inflection was near-perfect. ``Stop behaving as if you think you are.''

Zack was aware his own jaw had dropped, but it wasn't until he heard the other guys break into stunned laughter that he identified the twinge just under his ribs as homesickness\ldots and maybe something a little stronger.

``Oh, man,'' Hall was saying, ``you've got that down. Guess you've heard it more than once, huh?''

``Try more times than I can count,'' Riku muttered without much heat, setting the others off again.

A few sly glances were thrown Zack's way\textemdash ``Now who does that remind you of?''Ochs snickered under his breath\textemdash and he was just opening his mouth to give as good as he got when the rest of what Riku said finally sank in.

``Wait a minute\ldots Cloud's closet?''


\scenechange


Though the city turned out to be just as dead as it had looked on arrival, it had apparently been that way for some time. The official diagnosis was earthquake, Zack's men bringing back tales of fissured streets and half-crumbled houses, trees growing through gaps in the defensive walls. While that didn't explain why the city hadn't been reclaimed, it was a relief to know it hadn't been due to the Heartless, that he hadn't been too late. On a world like this, way off the usual hyperspace routes they'd only just started to reclaim, it was more likely than he cared to think about.

``There's an inn not far from here,''one of the SOLDIERs\textemdash Titus\textemdash offered with a shrug as he ended his report, glancing between Zack and Riku, like he was waiting for orders and didn't much mind where they came from. ``It's in better shape than most of the buildings on this side of town, and its back door has a clear line on that forest out there if you don't mind going over a wall.''Considering that the man looked like he wouldn't mind going through a wall, Riku didn't figure that was going to be a problem.

The problem was when Zack looked to him too, like his opinion mattered.

I'm not a strategist, he felt like protesting. And yeah, maybe Sephiroth had drilled a thing or two into his head, but it was mostly the sort of strategy you used to keep yourself alive when you were flying solo. If he had to move through enemy territory, he just made sure he wasn't seen; he didn't worry too much about leaving himself an escape route, because so long as he had the darkness, he could be two planets away before anything could pin him down.

He almost expected it to be a test, only no one looked like they were waiting to point out how stupid that idea was, and as pathetic as it sounded even in his head, it was just\ldots his turn to be the one listening now. They'd trusted him to get them through the darkness and out the other side. The least he could do was return the favor and trust in their area of expertise.

``Sounds good to me,'' He said, eyes flicking towards Zack, just in case, and relaxing inside when he found the man's smile unchanged. ``I've never had to find a Keyhole without people before; we may be here a few days.''

``Not a problem, kid,'' Their other scout\textemdash unmagical Stiegler, who swore more than Cid and fought like the Beast with a grudge\textemdash said with a suspiciously large grin. ``Wait'll you get a load of the size of the seafood around here.''

He might have known a crab the size of a Behemoth pretty much meant ``dinner'' To a SOLDIER. Then again, so long as it didn't talk, he'd eat just about anything, so he probably shouldn't be throwing any stones.

Though he was careful not to slow or stumble as they left the cul-de-sac and its dead fountain behind, Zack still shadowed him like a mama chocobo, cheerfully oblivious to Riku's pointed looks in his direction. He really was fine, damn it. All he'd needed was a moment to catch his breath. Only now he had Zack to glare at on his right, when he wasn't keeping his eyes fixed on Titus' ridiculously broad and immovable back right in front of him, and he was just going to ignore the way the others had formed up around him like the most embarrassing honor guard ever.

At the same time, he didn't mind it as much as he should have, because at least their familiar, everyday scents\textemdash steel and boot polish, leather and clean human musk\textemdash lightened some of the heavy weight of darkness he tasted with every breath. Whatever this city was or had been, the very stones underfoot had soaked up the dark like a sponge, and though it didn't smell anything like the Heartless, that wasn't much comfort.

The inn Titus led them to looked like it could have weathered three earthquakes without rattling the doors. Built of heavy stone veined with yellow and orange, it stood untouched in the middle of a street where few of the houses still had all their roofs, much less their window glass. ``Weird,'' Zack said, shaking his head as he stood outside the front doors with Riku as the others filed cautiously in. ``Maybe someone rebuilt this after the quake?''

``Like headquarters for the excavation?'' Riku offered.

``Maybe,'' Titus said on his left, unconvinced. ``But the houses I checked weren't stripped. It's like the whole city dropped everything and left one day.''

``Okay, that's creepy,'' Zack decided, shooting Titus a reproachful look over Riku's head. ``No campfire tales from you tonight. I'll never get to sleep.''

``Then you can take first watch,'' Titus replied with a faint little smile.

Distracted by Zack's attempts to draw him into the argument\textemdash if that was even what it was\textemdash Riku almost didn't notice Hall standing on Titus' other side, frowning up at the line of runes etched into the lintel. They were spiky, unfamiliar, unlike anything he'd seen around Radiant Garden or the little village they'd left, but Hall was moving his lips, slowly sounding them out.

``Hama gyl\ldots gylmothes es\ldots ensu?'' He stopped to chew on his lip, cocking a puzzled brow, unaware he was being stared at as Riku's interest caught the other two's. ``Not sure about that next part.''

``Holly,'' Titus said slowly, one big hand coming down on the slighter man's shoulder. ``What have we told you about messing with strange languages?''

``That I should do it in my head?'' Hall asked with an apologetic grin, hunching away from Titus and eyeing the other man sidelong.

``Oh, Gaia. Get him inside before he summons a god,'' Zack said, laughing, and shooed them all in ahead of him with a casual wave.

Funnily enough, Riku didn't think Zack was kidding in the slightest.

Though the dust was sticky-thick on everything, it didn't take much time to make the wide common room of the inn habitable. Haxby went around collecting lamps, and Stiegler found a sealed cask of oil in the cellar that was still good, and there was enough broken timber from the houses around them to keep the big fireplace the common room shared with the kitchen fueled for days. The beds they found were moth-eaten and mouse-nibbled, but no one really wanted to split up into rooms anyway. They didn't say it, but Riku could feel it in the silences and how quick they were to fill it. Quiet as it was, the dead city was eerie; an actual enemy to fight against would have been easier to deal with.

With nothing much to do as the others fell to debating the merits of field rations versus a crab bake, he settled himself sideways into the long window seat near the front door and stared out at the streets beyond. It was strange that the place looked so peaceful and felt so unsettling; most of the dark places he'd visited couldn't have been mistaken for anything but. Here there was just\ldots the quiet, and the crumbling houses, and the slowly-rusting remnants of interrupted lives. Maybe the Heartless had attacked this world, and the earthquake had come after\ldots but if the Heartless had been here, in large enough numbers to take out an entire city, then why was the world itself still here? It didn't make sense, and he wished there was someone he could ask, anyone at all. He hated to think that this world might have just\ldots slipped through the cracks, though he probably hadn't even been born at the time.

It was worlds like these, deep in what Sora had once called the Outer Darkness, that King Mickey worried about the most, and that was the whole reason Riku was even here. Cid and Tron had finally found a way to convert a gummi drive that could run the worlds without the peculiar tricks Kingdom Hearts played on the laws of physics when it got dragged into the light side of the cosmos, the lattice it made of freed hearts still struggling to remain connected. With regular gummi travel, folks stopped forgetting absent friends even after their worlds were locked, the door to Kingdom Hearts safely closed. But there were still limits when it came to fuel, repairs, ports of call, and at a certain distance, the dark paths were really the only reliable means of transportation.

Where he was now was out past every border station, every friendly outpost, off every chart he'd ever seen, and Tron had compiled plenty. He couldn't say himself how he knew the way back, but he could feel how far he was from the center of things, and though his heart's ties were still as unbreakable as ever, the vague feeling of presence on the other side of those bonds had thinned to nothing. All except one.

He knew they were still there\textemdash Sora, Kairi, Mickey, even Gaia herself\textemdash but it was Sephiroth he was steering by, a constant, unwavering pull dragging him ever homeward. That much never changed.

He just hoped Sephiroth wouldn't take it into his head to start moving around, looking for him, or he was going to be in trouble.

``Just have to beat him to it,'' He murmured to himself.

``Who's that?''

He started a little, but it was just Zack, standing over him with a smile. ``Sephiroth,'' He said, shaking his head and pulling up his legs, nodding to the other side of the bench seat in invitation. ``Not sure I could explain it if I tried.''

``That's pretty common where Seph's concerned,'' Zack said with a laugh, dropping down to sit in a casual sprawl. ``Unless this is one of those\ldots new things?''

``I wouldn't know,'' Riku admitted, hunching a shoulder. ``I didn't meet him until\ldots you know. After. He just likes to know where people are,'' He hedged, not sure what Zack would make of his former commander's occasional lapses into scary stalker behavior. Even if it had stopped being scary right about the time he narrowed his focus from Cloud-and-Riku to Riku alone.

To his relief, Zack just grinned, snorting fondly. ``That hasn't changed.''

Maybe not the inclination to it. Maybe just the degree of it. But it was sort of hopeful to think that maybe Sephiroth's old friends wouldn't be too put off by the changes in the man.

According to Cloud, even now, they were\ldots not inconsequential.

``Anyway,'' Zack said, ``about the next trip. Maybe we should break it up and go in smaller groups after all. It might take a little more time\textemdash ''

``No,'' He said, breaking in before he even had time to consider it himself. ``You were right. Look, I know you're worried about what happened when we came out,'' He pressed on while Zack was still drawing breath to argue, ``but it's always hard to bring someone else through with you, and I probably overdid it because I wasn't sure how much help you'd need keeping the darkness out of your hearts. The thing is, I'm probably always going to be a bit drained when we come out, no matter how few of you I take at a time, and it's not like I have any forewarning of what we'll be walking into. I mean, if you thought I wanted to get between you and an entire army of Heartless, you might want to think again.''

``And if we end up facing another army\ldots''

``I'm not going to be much help to you,'' Riku admitted, holding Zack's eyes steadily. He wasn't going to think about the fact that they weren't exactly having this conversation in private, because they all deserved to know the stakes, that he wasn't infallible, wasn't claiming to be. ``But I don't think there's much a dozen SOLDIERs can't handle, and if you can buy me enough time, I don't think there's anything a dozen SOLDIERs and a Keyblade master can't take care of. So it's better if we all go together.''

``You sure?'' Titus asked before Zack could, concerned but game.

``Positive,'' Riku said, meeting each man's eyes in turn with a silent promise. ``That, and I'm not leaving anybody in this creepy city overnight. No way in Tartarus.''

A few of them laughed at that; all of them grinned, even though he was pretty sure none of them actually knew what Tartarus was, on reflection. Then again, from what he'd gathered, Hel seemed to be a pretty universal concept.

That was actually sort of depressing when he thought about it.

``All right,'' Zack said as the others made a point of going on about their business, ``I give. Just remember you're not doing this alone, okay? If there's anything we can do\ldots''

He had to laugh. ``You really do remind me of Sora sometimes,'' He said, shaking his head.

``The kid from the photo?'' Zack sounded wistful, but Riku was pretty sure it was because that picture had been taken in the computer room at Radiant Garden, Sora mugging for the camera in the midst of the entire Restoration Committee. He'd dug it out to show Zack the new-and-improved Cloud: still in all that black leather, still hanging back at the very edge of the group, but sort of smiling as Aeris dragged him closer, glancing past her at Leon, who was sort of smiling back. He'd always thought Cloud and Leon made a weird couple until it finally dawned that\textemdash with Aeris\textemdash they made a pretty good threesome\ldots though Aeris had teased him for a month after she realized why he'd started blushing around her.

``Yeah. Nothing's ever so bad that Sora can't see the light at the end of the tunnel, and he's always on my case to stop doing everything myself and rely on others more.''

``Hmm\ldots sounds like a pretty smart guy to me.''

``Oh, he is,'' Riku was able to admit, smirking fondly. ``That's why I listen to him. Sometimes.''

Though it had seemed like a minor eternity at the time, he was pretty sure they'd only spent an hour walking the dark paths. All the same, even though they'd left the other world in the early morning, it had already been late in the afternoon when they reached the dead city, and now night was falling. Riku knew he didn't really have any time to lose, that it was going to take weeks, even months, to reach the nearest world with a gummi port, and that he should be out scouring the city for its Keyhole despite the advancing hour. He just\ldots felt like he was waiting for something, either for an invitation or for the other shoe to drop.

Beyond the dusty windows, the sky over the uneven rooftops was edging from twilight to black, the last smears of red and violet long faded. Far off, the tall, cracked dome of what looked like a cathedral or a palace caught a last, stray glimmer of sun, its stained-glass windows briefly catching fire, but then all was dark, a patch of deeper shadow looming against emerging stars. Sighing, Riku leaned the side of his head against the glass, listening to the SOLDIERs' idle banter without trying to make sense of the words: Titus' deep rumble, the friendly mockery of Stiegler's drawl, Hall's voice light and quick as he leapt from thought to thought, Zack's warm laughter brighter than all the rest as they laughed at one of Ochs' jokes.

The low murmur, uncertain but insistent, from nowhere and everywhere at once, half-heard words in many voices, not all of them human.

Stilling himself as his eyes went wide and his breath caught in his chest, he strained his ears to pick up that sound again and found it wasn't difficult at all. It'd been weaving through their conversations for some time now, but he'd only just noticed it as a separate entity.

\emph{Who? Who are they? \textemdash They're inside the walls now.}

\emph{\textemdash OUR walls.}

\emph{Yes, ours, but these are new. Have they come to join us?}

\emph{\ldots this one tastes of the Dark.}

He started at that, lifting his head from the glass, just as Giese let out a low, startled curse from the other window. ``Guys,'' The man said tightly, hands clenching unconsciously on the hilts of his shortswords. ``I think I know where the civilians got to.''

There was a man just up the street, moving at a slow, disjointed pace that wouldn't have looked natural under any light. He was dressed in the armor of a knight, or what remained of it; his breastplate was battered in on one side, half his helmet sheared away and part of his face besides. Riku didn't suppose that troubled the man any more than his missing eyes, though the blue shine deep in hollow sockets was maybe an antidote to blindness. That the man was dead and had been for some time wasn't in question. But was his one of the voices Riku had heard?

``Hold on,'' He said as weapons came out all around him, Zack and Titus already making for the door. The dead man outside had shuffled to a halt, staring at the lit windows of the inn intently, though his battered expression was hard to read.

``Something out there is talking,'' He said uncomfortably, the back of his own neck crawling at how creepy that sounded aloud. ``I want to try talking back.''

``No campfire tales from you, either,'' Zack muttered, but though he didn't look happy with the idea, he nodded once and opened the door, slipping out before Riku but staying out of his way.

Out in the open, when the evening breeze shifted, Riku could smell the dead man more clearly: old rot and dry musk, the darkness so thick it clung to the back of his throat. No whiff of the Heartless, though, and that was what made it so strange. It was clearly the darkness that was animating the knight, but he'd never seen it so strongly at work where hearts weren't involved.

Swaying slightly on his feet, the dead man watched as Riku came as close as he dared\textemdash as close as he thought Zack would let him without trying to get between them, if it came to that. He was still several yards away when the dead man took a halting half-step forward and stopped, the deep flames of his eyes flickering, going calm.

\emph{Ours,} the city whispered beneath his feet. \emph{This one's one of ours.}

\textemdash Or we could make him ours.

\emph{Why do you taste of the Light, little brother?}

There were more of them, he realized with awful suddenness\textemdash in the shadows of the houses along the road, coming out of open doorways, some more whole than others and some little more than bones. They seemed more curious than menacing at first, but that was before Zack edged closer on one side, Titus on the other, Zack calling his name in a low, warning tone.

The change was instantaneous, hunger and a dim, territorial fury sparking in the blue coals of their eyes as the dead focused on something other than him. If they'd seemed slow and stupid before, it was only because they hadn't been properly motivated.

Riku didn't doubt that the SOLDIERs would make short work of this tattered army\ldots but at the same time, he knew from personal experience just how hard it was to kill something that was technically already dead.

``Hold,'' someone snapped before the tension could break, a sharp voice that stopped the dead in their tracks. There was no tell-tale flare of shadows to mark a portal, but between one heartbeat and the next, a man appeared out of nowhere to stand between Riku and the dead, and this one was alive. Blond, whipcord-lean, he stood bare-chested and armed from shoulders to fingertips in silver, claws like butcher knives tipping each finger, and he smelled so strongly of the Dark, Riku half-choked on his first breath. When the stranger smirked at the same instant with a curious jerk of his brows, Riku tried to tell himself that was a coincidence and failed miserably.

``Not these,'' The blond man said abruptly\textemdash to the dead, half-turning his head without shifting his eyes from Riku's. ``Your prey are in the forecourt of the Keep\ldots though I imagine they're coming this way.''

As the dead shuffled obediently to do his bidding, his smirk stretched into a smile, fierce but amused, and his next words were addressed to the living. ``Ours happen to be the only hearts in Le치 Monde at present, and the shadows are hungry.''

``So the Heartless are here,'' Riku said, too surprised to edit himself. On the other hand, it wasn't often that he saw the dark at war with the dark; usually they'd decide they had more in common than not and meet as allies.

``Hmph. I'd wonder if you brought them with you, but you can't have been here a full day yet, or the city would have left its mark.''

\emph{Ours, ours, ours,} the city agreed, greedy and complacent at once, and this time Riku saw Zack start beside him out of the corner of his eye.

``What\ldots was that?'' Zack asked before Riku could get the question out himself.

``The dead. Le치 Monde keeps its own\ldots in one way or another. And it doesn't admit strangers lightly,'' The man added, regarding them narrowly. ``I felt a drawing of the Dark, but no alarms from our walls. How did you come to be here, and what was your purpose in coming?''

``We didn't mean to come here specifically,'' Riku said. ``We only meant to pass through this world on our way home. As for the Heartless\ldots I can lock the door to this world's heart, and that should keep them away.''If he could just find the Keyhole, and if this world would let him.

``Ah. So this is a Keyblade master.'' Though it was one less thing to explain, the knowledge didn't seem to set the man at ease. ``This world is old, and the tales of your kind are not unmixed. What assurance have I that you haven't come to destroy?''

For a moment he wondered if the man had heard something about him personally, whether tales of his earlier stupidity had somehow reached even this remote place, but that was just his own shame talking. Swallowing embarrassment and discomfort, he spread his hands helplessly. Whether this man was one of the world's defenders or not, he still deserved to be answered. 

``What would it take to convince you?''

He got a sharp smile for that, the flash of sharp claws as one silver hand was raised.

``Show me your soul.''

He blinked, and the world changed around him, the dark streets giving way to bright sunlight, the roar of the tide and the raucous conversation of gulls. He leapt backwards, Keyblade coming instantly to hand, but surprise made him falter. He'd expected\ldots when the man had said his soul\ldots but this wasn't Destiny Islands. It was Costa del Sol as he'd only seen it once before, when Sephiroth had brought him here before Gaia had been restored.

``That's right,'' He heard, familiar as his own voice because it was, and though he suspected a trap, he turned to look anyway. ``Who wears leather pants to a beach, anyway?''

There he was, and Sephiroth too, and the man was smirking the way he had when his watchfulness was as much uncertainty as ingrained distrust. Not knowing what he wanted or whether it was allowed or what Riku would stand for. Riku could have told the man that he probably had a lot more leeway than he'd realized at the time; it was right there in his own grin as his double was skinning out of his clothes, challenge bright in his eyes. Because he was daring Sephiroth to soak up some rays with him. Yeah, right.

``Are you sure you should be showing me this?'' An amused voice asked on his right, and he whipped around in startlement, face heating at the implications as he remembered how that little dare had ended.

``Oh\ldots Gaia.''

Something in the man's laugh, honest and without mockery, made something inside him relax despite itself. Though the man was clearly of the dark, so was Sephiroth, even now, and he didn't have one doubt in his heart where he and Sephiroth stood.

``Interesting,'' The man said, turning away from the spectacle on the beach to regard Riku with a slightly cocked head, grey eyes intent but less wary than before. ``You wield the light and dark in equal measure, and though you consort with both, your light is here. You're a bundle of contradictions,'' He accused in a way that seemed almost friendly. ``Most people,'' He added with a smile, ``would be showing me the most wretched moment in their existence right about now.''

``My friends would kick my ass if they caught me dwelling on the past.''

The smile quirked, reached grey eyes at last. ``Sydney Losstarot,'' The man introduced himself, nodding formally. Riku realized almost too late that the guy probably wouldn't be offering his hand to shake. ``You'd have likely had an easier time of it with the Riskbreaker, but that fool is halfway across Ivalice right now, pouring water into the ocean.''

``Friend of yours?'' Riku hazarded, wondering if the city really had only two occupants\textemdash living ones, anyway\textemdash and whether this Riskbreaker was one of the defenders he should have been placating.

``Ashley wears the mark of what we serve,'' Sydney replied with a shrug, ``but I was born to this city. It keeps no secrets from me.''

``Then you can help me find the Keyhole?''

``There's no need to search; I can lead you to it. The problem,'' Sydney added lightly, ``is what you're like to find with it.''

``I was afraid you'd say that,'' Riku muttered, releasing his Keyblade at last. ``I'm Riku, by the way.''

Sydney smirked. ``Yes,'' He said, ``I know.''

Blink, and the world was back\textemdash and none too soon, if his memory of that day on the beach served. It was just that things\textemdash or rather people\textemdash hadn't stayed where he'd left them.

Sydney was still standing just as he had been, but now he had Titus looming at his back, the big man a heartbeat from snapping his neck, and Zack had just thrown himself between Sydney and Riku, sword out, ready to strike.

``Wait!'' He cried, voice tearing as he tried to force the word out faster, loud enough to be listened to. He'd been grateful in the past for SOLDIER reflexes, but somehow he was never so relieved as when he got a clear demonstration of how quickly they could be restrained.

One moment Zack was a steel and charcoal blur, and the next he was utterly still, that oversized sword of his held at a precise right angle, without a tremor despite its weight. Titus' gold eyes were fixed on Riku, glowing like a Heartless' but utterly human in their uncertainty.

``You sure?''

``It's okay,'' He said, amazed his voice came out as steady as it did as reaction caught up to him. ``This is Sydney Losstarot. He's going to lead us to the Keyhole.''

``And to a rather annoying problem as well,'' Sydney added. ``I wouldn't want anyone to think I'd been less than forthcoming.''

Something about the sheer innocence of the man's smile just then made Riku shoot him a look, but Zack was slowly lowering his sword and Titus was taking a reluctant step back, and it just didn't seem like a good time to ask.

``This problem,'' He began instead. ``Is it Heartless, or is it\ldots ?''

``It's Guildenstern,'' Sydney said with a grimace of distaste, eyes flicking to the broken dome standing at the heart of the city. ``He was a knight of the Church once, before his craving for the Dark outstripped his control. He hoped to gain the power of the Rood Inverse once, but the Dark rejected him and Ashley defeated him, as it should be. Unfortunately,'' He added, his momentary satisfaction souring, ``once marked, the stain runs deep. Though the Dark stripped his humanity when it took him, his death remains\ldots incomplete. It seems he can still be summoned under the right conditions, and some fool has apparently succeeded.''

He didn't know what a Rood Inverse was or how someone could be incompletely dead, unless Sydney meant this Guildenstern was another zombie like the ones from before. He did understand one thing perfectly clear.

``We're going to have to fight him to get to the Keyhole, aren't we?''

``He was a Rood Bearer once, however briefly,'' Sydney said, frustration clear in his voice. ``My hands are tied. My usurper can defeat me; my heir can avenge me; but once the mark has passed, my interference in the lives of those who come after must sadly be of the non-lethal kind.''

Somehow he got the feeling that Sydney interfered a lot, if the smugly proprietary way he spoke of that Ashley of his was any clue. It didn't seem like a good time to bring that up either, though.

``Right,'' He said, glancing to Zack\textemdash who still looked a little strained about the eyes\textemdash then around at the others. ``Let's get moving. Whether this Guildenstern is still human or not, if he's still got a heart, I don't think we want to meet his Heartless.''



\scenechange


It was weird. He didn't know what had passed between Riku and Losstarot during that endless moment they'd spent staring at each other, but it had apparently convinced the kid the guy was fine. And sure, Losstarot seemed genuine enough, but Zack wasn't sure he trusted it. Or maybe he was just still keyed up from before, and not just for the simple, uncomplicated reasons he'd own up to in a heartbeat if anyone called him on it. Riku was a good kid, clearly needed someone to look out for him with the way he pushed himself, and he suspected their mutual friends would be asking him some hard questions if he brought the kid back home in less than perfect condition. Only that wasn't all of it, and part of it was the resemblance, a hardwired reaction to seeing danger come at anything Sephiroth-shaped, and part of it\ldots

He hadn't been there. Sephiroth had needed him there, and he hadn't been. And maybe that wasn't his fault\textemdash and maybe Gaia was going to get an earful when he got back, and he'd get Aeris to translate if he had to; see if he didn't\textemdash but that didn't change the fact that he'd been absent when it counted. And that wasn't ever going to happen again.

So maybe Losstarot wasn't really the bad guy here, and he should just tell his nerves to settle down. On the other hand, he was really sort of tempted to clap a hand over Riku's eyes and turn the kid around until Losstarot fixed his pants.

And now the guy was smirking at him, but that had to be a coincidence. Really.

``So, er\ldots what does the rest of it say?'' Hall asked suddenly just before they moved out, reddening a little when Losstarot glanced his way. ``After \emph{ensu},'' he added, pointing at the carving over the door.

Losstarot arched a brow, but rattled off, ``\emph{Ensunir vedes ama}. It's Ancient Kildean; it means\ldots `as I your creatures have sheltered, shelter also me.' A plea to the Powers, to ward against fire and flood.''

``And earthquake, apparently,'' Riku added.

Sydney hummed an agreement but cast Riku a look of friendly reproach. ``You've brought me an adept, but I don't think you're going to let me keep him,'' He said, nodding at Hall, who reddened to the tips of his ears. ``How very unkind.''

``Sorry,'' Riku replied, smirking a little and not sounding sorry at all. ``But we need him more than you do.''

``Perhaps,'' Sydney agreed mildly, giving Hall one final appraising look before turning to lead them to the Keyhole.

Somehow the city looked worse by night than it had by day. The warm glow of the sun off the pale stone of the houses and the drowsy heat baking the quiet cobbled streets made for a lazy kind of peacefulness in retrospect. Under the moon and the eerie blue streetlamps that had boiled alight with a breathy hiss when the last smudge of orange on the horizon was gone, the houses lurked in battered, broken piles, leaned ominously into the street, and every creak of abused masonry made him look for the blue spark of dead eyes, the graceless shuffle of things he didn't want to think about too closely.

Which didn't mean he wasn't going to.

``So what were those things?'' He asked Losstarot, hunching a shoulder when the man glanced back at him. ``The\ldots people from before.''

``The Cold Ones? They were Le치 Monde's former residents, for the most part, though some of them were knights of the Church who came with Guildenstern when he tried to take the city.''

``But why were they like that? I mean\ldots you can't tell me that's normal for here. Er\ldots is it?''

Sydney chuckled, shaking his head. ``No. Le치 Monde was a Dark city while it stood, and the Cardinal's men were neither as holy nor as prudent as they should have been. What the Dark once touches, it keeps; those who die outside the ward of the Church's palings are given the incomplete death, which\ldots can be as you've seen.''

``Those guys from earlier.''

``And Guildenstern, and the city's shades. I've had more than my share of deaths myself,'' Sydney added. ``Is it not the same in your world?''

``Not even close,'' he said, noticing too late Sydney's puzzled glance at Riku, Riku's pale face. Oh, Gaia. ``Unless something's changed since we've been gone\ldots ?''

``No,'' Riku said quickly. ``Just\ldots I know someone who's come back a few times. Actually, I know a couple,'' he muttered, but Zack was really only interested in one. Riku hadn't said, but\ldots he couldn't mean\ldots just how much had Zack missed?

Sydney hummed something noncommittal, but his sharp face went almost kind. ``Your friend must be beloved of the Dark, then.''

Zack could tell Riku wanted to bristle at that, but the kid mastered himself quicker than Zack would have in his shoes, shaking his head. 

``Maybe so,'' Riku said. ``And you know\ldots I don't think it was even the darkness' fault when he went\ldots well, what happened to him. I just\ldots I keep wondering why you're not trying to take control of the Heartless and take over the universe.''

Sydney gave him an arch look for that, and Riku smirked right back. ``I know why he's not. I'm asking about you.''

``I'm not interested in the universe,'' Sydney replied, hunching a shoulder with a faint chime of silver. ``There is a fundamental difference, you realize, between the Heartless and the Dark.''

Zack frowned, caught Riku's eyes cutting his way with the same troubled expression. Shrugging for them both, he asked, ``Care to point out some of the particulars?''

``The Dark is\ldots'' Sydney frowned, eyes going unfocused, like he was looking for words his language just didn't have. ``Darkness\ldots is,'' He said at last. ``It waits for you to come to it, and what it takes, it keeps. It also likes to change things, and the only thing it likes more is the strength and will to resist that change. It will test you, to see whether you'll break or give in to fear\textemdash or to greed, or if you'll take it too much for granted\textemdash but if you're mindful, it will shield you and keep you 'til the end.''

Losstarot waited for Riku's nod, oddly self-conscious, before going on with a rueful smile. ``Hearts, though\ldots hearts are more troublesome. They want connection; they want to be surrounded with others like themselves. A heart that's given in to darkness is a corrupted heart, and the heart wants what it wants. And mostly what it wants is more. The Dark can't help being what it is any more than fire should apologize for burning. The Heartless want to grow and multiply and feed. The Dark,'' He said with a sly little smile, ``would rather make you work for its notice.''

``Don't I wish,'' Riku grumbled, shaking his head. ``It's harder to keep out of its notice. Believe me, I've tried.''

``That's because it's your nature,''Losstarot replied, as satisfied as if he'd gotten just the answer he wanted, and way too intent on the kid for Zack's peace of mind. Whatever Losstarot was mulling over just then, if it included Riku beyond the time it took to lock this world, he'd better get used to disappointment.

It was the second time grey eyes flicked his way after he'd been thinking a little too fixedly on the man, and this time he didn't dare trust that it was only unlucky chance. Not with Losstarot smiling like that, amused and acknowledging. I'm not going to fight you, the man might as well have said, but it's not because I can't.

``Here we are,'' Sydney announced before the staring match could go on too long, and Zack glanced warily past him to the tall edifice Losstarot had brought them to. ``The Great Cathedral. I'm afraid it's seen better days, but we'll find the Keyhole at the top\ldots and Guildenstern as well, more's the pity.''

It was a long trip, much longer than a mere three stories should have warranted. The Cathedral hadn't been spared in the general destruction of the city, and it looked like it'd seen hard battle more than once, the floor charred and cratered where it hadn't simply crumbled. The stairs\textemdash where there were stairs\textemdash couldn't be relied upon, so they had to trust in floating stones and magic of a sort Zack hadn't seen used very often. All the spells he knew were either for fighting or its aftermath, not for convenience.

``Remind me to show you my pockets sometime,'' Riku said with a grin as Zack poked a cloudstone with helpless fascination, just to watch it bobble in midair.

``Do I even want to know?''

``If you get hungry enough, you will.''

He sort of had to shake a few thoughts out of his skull before they stuck there as Riku strode cockily away, and oh, that was bad. It wasn't like Riku had meant anything by that, and just because the kid looked like Sephiroth, that was no reason to start making an idiot of himself a second time.

Actually, 'just because the kid looked like Sephiroth' was no reason to start anything at all.

``Are we there yet?'' Ochs joked as they gathered in another room with another cloudstone and no other way out he could see. He had a pretty good sense of direction, and as high as they were, as close to the heart of the Cathedral as they had to be, he didn't figure there were too many more hoops they could jump through. He just didn't like the look of that cloudstone, because those floating bricks just weren't that big\textemdash or that fast.

``Actually,'' Losstarot said, ``yes. All that lies above is the atrium and the Cathedral's dome. Unfortunately, the only way up is there.''

One silver claw flicked towards the cloudstone Zack had been eyeing, and his bad feeling expanded into a full-blown premonition.

``I don't like this,'' He said, frowning up at the far-away square cut into the ceiling high overhead. They'd found out they could fit three on one of those rocks if the three were pretty good friends, but every additional man slowed the stone's flight considerably. By the time the last man got up there, if trouble was waiting, the first set of guys would already be up to their necks in it. ``What d'you say I head up there first and take a look around? At least then we'd know what we're walking into.''

Riku gave him a weighing look, took a deep breath as he glanced up at the ceiling\ldots and grimaced as he dropped his eyes to Zack again. ``The darkness is too strong here,'' The kid said, shaking his head. ``I can't tell if there's anyone else up there or not.''

``All the more reason for me to take a look.''

``Not alone,'' Riku insisted, so levelly Zack knew arguing over it wouldn't be worth the breath.

``Fine, fine,'' He said, grinning at the mama chocobo look he was being given and glancing sidelong at Losstarot as if to say `so there.' ``I'll take Titus.''

He could tell Riku wanted to be on that cloudstone too, was used to leading the charge when he wasn't fighting solo. It was written all over his face. He could also tell Riku knew he'd picked Titus because they would not be fitting a third guy on that floating hunk of rock no matter how friendly they were.

``All right,'' Riku said after the faintest of hesitations, and Zack breathed an inward sigh of relief at not being forced to dig in. When it came to the dark paths, he needed the others to jump the instant Riku told them to, and he wasn't sure how long that'd last if he started countermanding the kid's orders. ``Who's coming up with me?''

``Stiegler and Hall,'' Zack said, glancing at the other two and collecting a pair of sharp nods, anticipatory grins. They worked well together anyway\textemdash pure magic and pure force, or just about\textemdash and Stiegler was steady and stubborn enough to keep everybody thinking if anything went wrong. ``We'll need someone covering support in the next run,'' He added, glancing around for volunteers, but the man who spoke up wasn't the one he expected.

``I'll handle that,''Losstarot said calmly, smirking at Zack's raised brow. ``Just because I can't kill him, that doesn't mean I can't make Guildenstern's life as miserable as possible. I'll deal with healing and support. Just be wary of his magic. Even without the power of the Rood, the man is formidable, and not all his spells are of the Dark.''

``Got it,'' Zack said, gathering Titus up with a look. ``All right\textemdash see you guys upstairs.''

It was probably just his imagination that made this cloudstone's flight seem to take longer than all the others, but at least it gave him time to focus, setting aside the creeping sense of walking right into an ambush for the determination to survive it.

They were moving before the cloudstone came to a stop, clearing the last six feet at a leap that made the stone wobble in midair and start early on its slow trek back down. On first glance the room appeared to be empty of everything but the crumbled remains of a set of stairs heading up to the dome, a few guttering mage-lights casting spiky shadows over piles of rubble and an alarmingly wide bloodstain in the center of the floor. Maybe someone had gotten to Guildenstern before them, because somebody had definitely died here once upon a time.

Before he could advance that theory aloud, something shifted in the dark dome overhead, ragged motion just glimpsed through the gaping hole in the ceiling. Wings, he thought, only maybe not very good ones; maybe like something pieced together by someone who had only the vaguest idea of how wings should work.

Sort of like how the man those wings were attached to had clearly forgotten everything he ever knew about being human.

``I blame Hojo,'' Zack muttered, and then he was off, circling the monster from one direction while Titus took the other, pushing hard for speed, because that\ldots carapace looked ominously tough. For an unholy blending of vulture, moth and man, it didn't look the slightest bit delicate, and the sword that thing was carrying rivaled his Buster.

``I don't think Hojo's made it out this far,'' Titus said while Zack was busy locking blades with the thing, the sweep of one massive fist staggering the creature in midair. The thing turned faster than either of them expected, one brittle vulture wing lashing out with an odd keen that widened Zack's eyes and made Titus drop into a crouch, the blade-sharp line of the monster's primaries just missing a decapitating blow.

``It's the principle of it,'' Zack said through gritted teeth, and that time he wounded the thing, the edge of his blade biting deep.

His stomach clenched as he watched the creature's mouth gape open, voiceless, its mostly human face twisting in pain while its pale amber eyes remained perfectly blank, soulless. Sydney had warned them the darkness liked to change things, but he hadn't dreamed the man meant anything this drastic. If this was what it did to people it didn't like, it was a wonder anyone ever risked its temper, whatever the temptation.

Or maybe Guildenstern was just special that way. Who knew?

``Well,'' Titus said, bobbing to his feet again with a grace no one ever expected from a guy that big, fists swinging before the thing could recover. ``Far be it from me to get between a man and his principles.''

He was just starting to think they had this thing's number when it opened up on them with a spell that just about brought down the rest of the ceiling on top of them. Boiling pillars of light howled to life on every side, one after the other, so many he just knew he wouldn't be able to dodge them all. And if he was in trouble, then Titus, fast as he was, was in worse shape still.

It was in between twisting away from one fiery column and realizing the next was going to come down square on his head that he saw Riku come flying up through the hole in the floor, so fast he must have convinced Stiegler to give him a boost. Hitting the ground running, Riku tore right through the midst of the attack, and Zack just plain forgot to worry about the searing light pouring down all around him and the ozone prickle of a spell settling into his skin as he watched Riku charge right through one of those pillars and out the other side. Unharmed. Not stopping. Hitting Guildenstern hard enough to knock the thing right into the wall, breaking the creature's focus on the spell.

It occurred to him only belatedly that he was still on his feet himself, not even singed, though there'd been an unsettling instant when he'd felt like he'd been encased in an eggshell-thin layer of glass, and it had just shattered all around him. It wasn't until he saw Losstarot standing just at the far edge of the room that he understood just how much ground an offer of 'support' could cover when the person offering was a Dark, possibly-undead mage. Whatever that spell had been\textemdash some sort of magic-proof ward?\textemdash he couldn't fault Losstarot for his timing. Especially since one of them apparently needed to hear Seph's lecture on invulnerability again, because it clearly wasn't sinking in.

``We gotta teach mini-Boss to delegate,'' He threw over his shoulder, hefting his sword again as Titus rumbled a laugh.

``At least he plays well with others.''

``Gotta start somewhere,'' Zack agreed, sprinting to join Riku as Hall and Stiegler came bounding up after the kid.

If the odds against them had looked bad at first, they were evening out with every moment that passed. Matching his timing to Stiegler's was as easy as falling back into the steps of a drill and just as familiar, and some of the spells Hall was tossing around were Guildenstern's own attacks thrown back at him, yelled in a language Hall had no business knowing. Ochs was right beside him before Zack even realized the next bunch were due, the deadly hooked edges of his polearm's blade shearing dagger-sharp feathers from bone. Giese was a flicker of lightning, shortswords biting fast before he darted away, and Schreiner waded in with a grin as wide as the blade of his axe, like he ought to be decked out in wolf skins and dedicating this battle to Odin.

Every hit they couldn't dodge, every spell that made it through, was washed away by healing spells that came in a flicker of blue, not the bright green and gold Zack was used to, and though it didn't warm him through, the cool tingle it left behind was soothing and friendly all the same.

He was just starting to think they might start moving in for the kill when he felt that eggshell ward settle down on him again, heard Hall falter midway through a spell, like he was afraid to disturb that shield. It was habit that made him look to see where Riku was, so he was staring right at the kid when the Light spell hit and shadows flickered to life in answer, wrapping Riku up and hardening to armor in the space of a breath. Even through the ward Losstarot had thrown up, the force of that spell was staggering, but Riku kept his feet, lunged forward to end it\textemdash 

And found his own blade joined and matched by a five-pointed sword the twin of Guildenstern's own.

The new guy was big, not quite on par with Titus, but then again, who was? And the next time anybody gave him any grief about his hair, he was just going to remind them of what they'd seen here today, because the redhead's own spikes made up in epic what they lacked in number. Though the guy was snarling right now, he looked like he'd be hard to rattle, and Zack might have figured him for some random passing hero if not for the grim satisfaction in his eyes as Guildenstern buckled under the final blow.

The creature never made it to the floor, fading out like a summon dismissed, and that worried Zack. It worried him a lot. On the other hand, with it banished, the next time the thing got called probably wouldn't be any business of theirs.

``You're late, Riskbreaker,'' Losstarot said into the stunned silence that followed, ignoring every other eye that turned his way.

``Not that late,'' The man said dryly, like he didn't intend to give Losstarot the satisfaction of seeing him riled. Or like he got this all the time. ``I was taking care of Batistum.''

``Oh? And how is our old friend?'' Sydney purred, eyes narrowing, glittering with malice.

``He won't be summoning any more former Rood Bearers,'' Ashley replied with a shrug, glancing around him with wary curiosity. ``M칲llenkamp did say you had it covered\ldots''

``With assistance, as you can see. The Dark brought us a Keyblade master,'' He added, and while Zack would have expected to hear something like a threat in the way he'd worded that, Losstarot sounded more like he was speaking of a favorite uncle, the one who was always available to come jump a car in the middle of the night and who always had a spare wrench he could lend you. ``Actually\ldots we should thank these people properly, don't you think? It's only fitting\ldots''

He wasn't sure he liked the sound of that, especially when he realized Losstarot was staring at him.


\scenechange


``You'd be a fool to travel so soon after a battle,'' Sydney told him bluntly when Riku would have locked the world immediately, and though he didn't like to admit it, he'd been dragging a bit after that fight. ``You may be of the Dark, but you're still mortal. You're risking enough trying to take that many with you.''

``I know,'' He said, glad the others were out of earshot, watching Ashley demonstrate a few Riskbreaker tricks they hadn't learned in SOLDIER. ``But it's the best way, and it's just\ldots something I need to do.''

``As you like,'' Sydney said with a shrug. ``But you should at least stay the night. I won't try to keep you,'' He added with a swift grin before Riku could protest, ``though if Riot had any sense, he'd make you his heir on the spot. But then, as I don't intend for him to need one, I suppose the point is moot.''

``You guys\ldots really can't die,'' Riku said slowly, ``can you?'' He wasn't sure how he felt about that, because the idea of Sephiroth losing everyone again, one by one, made his stomach knot with dread.

``Oh, we can die. It just doesn't always help. The Dark will only send us back, because of all the hands it has at its disposal, it prefers some more than others. Some of us do rest,'' He added, more gently than Riku would have expected. ``Some of us even prefer it. But some of us are far too restless to be satisfied with idleness.''

``Yeah,'' He said, wondering already how he was going to break the news to Sephiroth, whether there was anything he could do to make the prospect of eternity sound like anything less than a prison sentence. ``I know what you mean.''

Sydney merely smiled, eyes curiously intent. ``Good.''


\scenechange


``One more,'' Ashley said, smiling faintly as Zack groaned, like he knew damn well Zack didn't mean it. All the same, Zack was looking forward to that soft bed he'd been promised for the night, for all that he'd never turn down the chance to learn something new to keep himself and his people alive. ``I've shown you how to ward against a Light attack like Guildenstern's; now I'm going to show you how to ward against the Dark.''

``You sure that's not against the rules?'' Zack asked with a grin. He liked Riot, for all that the man wasn't a big talker. He was used to the quiet ones anyway.

``I'm not like Sydney,'' Ashley said with a snort. ``He was born to the Dark; it's all he knows, and he understands it better than anyone I've met. I don't know what made him pick me to follow after him, but the Dark tolerates me for his sake\ldots and because I'm very, very useful,'' He added wryly. ``If it does have rules, it hasn't mentioned them to me, and I'm going to teach you anyway. You need to know.''

``What makes you say that?''

Ashley shrugged. ``Because as much as I want to strangle him for it sometimes, Sydney is never wrong about the future.''

So he learned the Demonscale ward, which was just like Shadow Guard only backwards, and when he fell into bed at last, he was too tired to worry about the fact that Hall had spent all evening in Sydney's library, or that Stiegler had found a workshop to play in and might have to be bribed out again with food come morning, or that no one else seemed to have noticed that Riku had been avoiding them all since he'd wrapped himself in that dark armor of his.

He told himself he was even too tired to worry about Sephiroth\textemdash he can't have really died, not Seph; that guy is way too hard to kill\textemdash and if he was too tired to worry about Sephiroth, then he was definitely too tired to wonder what he was going home to in the end. A friend he'd failed, and lovers who'd moved on without him if that bright look in Aeris' eyes, the small, soft smile on Cloud's face still meant what they used to. Leon was a good kid, and they'd looked\ldots happy. So at least that was one good thing that'd come of all this.

When he finally slept, he had strange dreams, half-woke once to hear the city talking to him in his sleep, or he assumed it was the city, anyway. It hadn't seemed important at the time, and when he woke to a banging on his door, Haxby yelling something about breakfast, the memory slipped away altogether as he hauled himself out of bed. He had better things to worry about than a few weird dreams, and they had another long trip ahead of them.

``It'll be good to get home,'' He told himself, practicing. It didn't sound half as wistful as it had the night before, and that was a step in the right direction.

Then Riku slipped out into the hall, tense like he hadn't been since those first few hours when they'd all been strangers, and before he could second-guess himself, he wandered over and scruffled the kid's hair into a total mess.

``Zack!''

``Oh, that sounded familiar,'' Titus rumbled as he passed, giving Zack a tiny sidelong smile. Good idea, that look said. Just don't do anything stupid, and I won't have to hurt you.

Sometimes he thought half of Radiant Garden knew about the blind, hopeless crush he'd had on Sephiroth when he'd been Riku's age. He'd sort of minded at the time, but not so much now. At least it'd keep him honest.

And if he did do anything stupid, Titus would break him in half. So that was okay, then.

Catching Riku giving him one of Sephiroth's own alley cat looks of wary affront, he burst out laughing and refused to explain why, slinging his arm over Riku's shoulders and dragging him along, refusing to let him slip in unnoticed. And if the other guys took their lead from him and maybe went a little out of their way to make Riku feel included, that was all to the good. They were trusting their hearts to this kid, after all; it'd be one hell of a bad bargain if the kid couldn't trust them in return.

But that was another thing Zack wasn't going to let happen on his watch, not this time around, because this time he was going to get it right.
