\renewcommand{\pfbreakdisplay}{%
\ding{94}\quad\ding{94}\quad\ding{94}}

Planting his feet more comfortably in the nothingness, Riku hesitated, took a deep breath\textemdash and let it out on an exasperated snort. ``Yeah, okay, I hear you,'' he grumbled, resisting the urge to shake his head, hard. It wouldn't help; it wasn't really his ears that were ringing. As for the invisible hook buried in his middle that had practically dragged him here, it didn't matter whether the pull came from inside his heart or if it was all in his mind. Either way, it wasn't something he planned to ignore.

``Okay, there?'' Zack asked at his back, his voice a curious blend of alert concern that Riku found it hard to take exception to. Zack had said the same thing after rescuing Riku from the clutches of two duchesses with five daughters between them, with the same touch of humor and solidarity in his tone. At least Zack had had his back. Titus had just grinned at him when he'd cast a desperate glance in that direction, and Callisandra's delighted, Sora-like beam suggested she'd already started picking out heralds to announce the engagement. Who knew wedding banquets could be so dangerous?

``Yeah, it's fine. I'm just really feeling the welcome here. Literally,'' he added so no one would go into battle mode on him.

Well. Any worse than a dozen SOLDIERs First Class ever were, anyway.

It worried him that this world was calling him so strongly. Gaia had done that, and while he wasn't complaining about how that had turned out, most worlds were little more than emotion and memory, existing as one vast pool of awareness without self, on a completely different plane than the small lives contained within their sphere. Sometimes when he was traveling the dark paths he'd feel a tug\textemdash never as strong as Gaia's had been, but he'd never come across a world as awake as Gaia, either\textemdash only he could usually feel the desperation in it, too, the need to have him there before time ran out. There was need this time as well, but it was more the unsettled feeling of having things out of place than the ache of outright dislocation. That maybe explained why he didn't feel quite so drained this time around; half the work of getting them here had been done for him, the planet pulling him along whenever he'd been in danger of lagging behind. That this world was still strong enough to be able to help had to be a good sign. If it had that kind of power to spare, at least it wasn't focusing all its strength on holding itself together.

``So\ldots where do you think the zombies will crop up this time?''

``Ochs, you dumb shit, if you've fucking jinxed us here, I'm taking it out of your ass.''

``Wow, Sarge\ldots does this mean you've finally accepted my undying love?''

``No!''

Then again, maybe he'd just been too distracted on the way to notice just how far they'd traveled.

Grinning at nothing, he held up his hand, opened his heart as he hunted for connection, and\textemdash there. One touch and the portal sprang to life from nowhere, blossoming up from his feet and irising wide, just tall enough and broad enough for a big guy like Titus to pass through without ducking. There was still a film of darkness between him and that other world\textemdash he didn't quite have Sephiroth's control yet, enough to rip right through that veil and peer out onto the other side\textemdash but the prospect of flying blind wasn't enough to stop a SOLDIER.

It was Hall and Stiegler who went through first this time, the Sarge more cautiously, Hall following eagerly on his heels. It wasn't exactly Riku's favorite part of the trip, letting someone else head out into the unknown while he hung comfortably back\textemdash which was stupid, because if anyone could handle themselves in the midst of alien territory, it was a pair of SOLDIERs First Class\textemdash but he stood firm, hardly breathing as he watched the others arrange themselves on either side of the portal, ready to charge through at the first hint of danger while leaving Hall and Stiegler plenty of room to retreat in a hurry.

``All clear,'' Hall called back through a moment later, and Riku felt some of the tension roll right off his shoulders. He hadn't realized just how much he'd dreaded coming out in the middle of another pitched battle until then.

Jergensen and Ochs were just moving into position when Stiegler's mutter\textemdash "I guess"\textemdash reached them, the Sarge's voice coming through bewildered and half-disbelieving. And that was worth a moment or two of panic, because Stiegler actually sounded uncertain, and Riku hadn't thought anything could faze the Sarge.

Riku glanced back at Zack, but Zack looked as curious as Riku felt. ``Don't look at me,'' the man said with a shrug, clearly taken aback. ``But whatever it is, it's got to be good.''

Sometimes Riku wondered if all SOLDIERs weren't half cats, because as cautiously as they moved going through the portal, not one of them dragged his feet. All he saw on their faces as they passed was interest and anticipation, and a wicked grin here and there that said Stiegler would never hear the end of it if he'd gotten them worked up for nothing.

Zack actually looked torn before Riku laughed and pushed him out first, ruthlessly stomping on a stupid warm glow to see he rated higher than satisfying a SOLDIER-strength curiosity. Or maybe Zack's over-protectiveness was really just that overdeveloped.

And Riku's friends thought he was bad.

Stepping past Zack as he let the portal drop, he scanned the shady street they'd come out on, seeing nothing all that unusual at first. They were deep in the heart of a city, one he doubted would be very tech-heavy if he had to judge by the cobbled streets and wood-and-stone buildings all around. The fact that they hadn't started a panic by their unorthodox arrival was definitely a point in favor of `weird,' though, and he took careful stock of the people on the street, who were wary and puzzled and\ldots not all of them human. Not by a long shot.

It was the hulking strangers with the broad, finny tails he noticed first, most of them huge, though he did spot one in the crowd that he found himself instantly categorizing as a kid, even though she stood nearly as tall as the humans around her. They weren't mer; they had legs, looked perfectly comfortable on dry land, and he almost wondered why his head kept saying fish when he should maybe be thinking dinosaur. He didn't even blink when he noticed there was a third race as well, creatures that stood maybe hip-high on an average man, with the smooth-scaled hides of lizards. Though they were much more striking than their oversized counterparts, as brightly-colored as a pack of geckoes, their eyes were remarkably similar.

Divergent evolution? Riku wondered absently as the frozen townsfolk shook themselves and began to move again.

``Heeeey, Fourth Committee,'' a human slurred with a cheery grin, his overloud voice echoing down the street as he gave them a rather wobbly thumbs-up. ``Lookin' good!''

As the drunk staggered away from the bar he'd been startled coming out of, one by one the people on the street went warily about their business, hawking wares in hesitant voices or turning to haggle with distracted merchants, one woman scolding her child for staring as she hustled them both away.

``Okay,'' he heard on his right, and though it was definitely Titus' deep rumble, it somehow seemed more cavernous than usual. ``Now why do I suddenly have a tail?''

``Gyah!'' Zack yelped as Riku was turning to look, already half-certain of what he'd find. But, ``Hwah?'' Zack added in a strangled voice, and Riku had to bite his cheek to keep from laughing as Zack peered down at himself in horror, arms thrown wide. All four of them.

He was furry, there was that, covered with a pelt as black as the spiky mane he still sported, though the pointed ears jutting from the mess were definitely new. He'd also grown at least a foot, and it could only have been magic that had shifted his uniform along with him. Though they still glowed strong and clear, his eyes had gone rounder, more bestial, to go with the definite fangs that were on display with his mouth gaping open like that. It was the second pair of arms that seemed to be attached at Zack's hips that had Riku most curious, because apart from wings, he'd never seen a race with six limbs before.

It probably wasn't his imagination that Titus looked pleased that he wasn't the only one to have been altered unawares, and if Riku had thought the man a giant before, clearly he needed to work on his imagination. Taller even than Zack, Titus was a massive collection of muscle and scale, striking in his refitted charcoals, the black-etched grey of his new markings. His gold eyes were the same, and except for the glow, they didn't look the least bit out of place for this world, which was one less thing to worry about.

``Oh,'' Riku said, succeeding in the effort not to laugh but losing the battle to control a smirk. ``I guess I should have warned you this could happen, but I didn't think it would.''

``Huh?'' Zack managed, looking over at Riku with his arms still outstretched.

``Blending in,'' Riku explained, nodding at Zack's new form. ``Usually it takes a spell, but sometimes, if a world is different enough, it'll change you itself. That's usually a good sign; I wouldn't worry about it if I were you. It just means we're welcome here.''

``You mean this is normal?'' Titus asked, glancing over one ridiculously broad shoulder to eye the tail he was experimentally swishing around.

``Yeah, pretty much,'' Riku said, coughing into his fist as Haxby nearly got flattened by a too-enthusiastic tail-lash. ``Uh\ldots tell you what. Why don't we get off the street and talk about it somewhere else? We may not have started a panic,'' he added, watching as a few people on the edge of the crowd started sidling away a little too purposefully, ``but I think we've definitely drawn some attention to ourselves.''

``Think we should bug out of here?'' Ochs asked, eyes casually roving the street.

``No,'' Riku said slowly, eyes going unfocused as he opened his senses, trying to feel for a sense of whatever had the planet unsettled and coming up\ldots not empty, exactly. He could smell Heartless, but faintly, carried in from somewhere past the city walls. ``I think we'll let them come to us. We already look like we belong here; might as well act the part.''

Stiegler arched a brow but cocked a thumb back over his shoulder with a shrug. ``Bar's thataway,'' he offered with a smirk.

``That was exactly what I was thinking,'' Riku agreed, grinning back.

He had to sort of steer Zack along with a hand on an upper elbow for the first few steps, but then Zack shook himself, all over, his ears tilting off in strange directions as he fixed Riku with a mournful look he might have learned from Sora.

``So much for my rugged good looks,'' he said with an overdone sigh.

``Sorry, Zack,'' Riku replied, editing himself quickly before he mentioned that the new look was\ldots actually sort of intriguing. ``They weren't actually that rugged.''

``Ow!'' Zack laughed\ldots and then his ears came up on a startled double-take. ``Hey, wait\textemdash ''

There was a suspiciously Ochs-like snicker at his back, but Riku ignored that in favor of dragging Zack into the bar without looking back. He did notice himself that he hadn't let go of Zack's arm, but that was just common sense. Clearly the alteration to his body had done something to his brain as well if Zack didn't realize he was turning heads even as an oversized catboy.

Because the fact that Riku had eyes couldn't be a surprise\ldots could it?

It was always a relief to find out that gold was gold, no matter what it was stamped with or what the locals called it. Munny, gil, or restas\textemdash and they had all three, along with a few dinars Riku didn't even remember picking up and a string of copper cash that he'd been trying to forget\textemdash their currency was good as far as the bartender was concerned. Though the guy did seem a little on the friendly side when he greeted them, a meaningful cough from the pleasant young man behind the counter with him brought the bartender quickly back to business.

If there was one thing about the folks back home Riku really appreciated, it was not being teased when he ordered one beer and a pitcher of water, even though he knew the legal age for drinking in Radiant Garden happened to be the same as for joining the military. No one on the Restoration Committee had ever given him any crap about it, not even Tifa, who owned the bar they all treated as their second home. Sephiroth had asked him about it once and once only\textemdash had asked out of idle curiosity what the norm was on Destiny Island, to be precise\textemdash then left it alone once Riku told him. Sephiroth hadn't needed anyone to explain that Riku didn't like having his senses dulled even a little if he could help it, and without the metabolism of a SOLDIER, drinking didn't hold much appeal. Especially not this far from home.

Watching the SOLDIERs place their orders, on the other hand, was nothing short of hilarious, and by the time they were done, the bartender had proposed. To all of them.

``Man,'' Zack sighed as they found seats, pushing together a few tables and the tall, sturdy stools, backless and armless, that served as chairs for four wildly-disparate races. ``This feels so weird. I mean, I've heard of not knowing what to do with your hands\textemdash ''

``Heard of it,'' Hall echoed, keeping a straight face with an effort.

``\textemdash but this is ridiculous. But this isn't weirding you out at all,'' he added as he turned to Riku, what should have been accusatory coming out curious.

Riku shrugged. ``Whenever I go to Atlantica, I turn into this sea serpent mer-person thing. Finny snake coils from here down,'' he added in case they weren't getting it, hovering a hand by his hip. ``Seeing it happen to someone else for a change isn't nearly as strange.''

``Huh,'' Zack said, one ear cocking thoughtfully back until he noticed it. ``Augh,'' he said, lifting one pair of hands to his head and flattening his ears down tight to his skull, his other pair of arms folding across his hips after a brief disgruntled flail. Oddly enough, once they'd folded that way, they looked comfortable, right, and Riku noticed he didn't unlock that pair of hands from their elbows directly after, either. ``Okay, forget my looks. My poker face is never going to be the same.''

Riku blinked. ``He has a poker face?'' he asked the others, amazed.

Titus smirked, the new shape of his mouth making him look even more enigmatically evil than before. ``Believe it or not? No.''

``Hey!''

``It's not like he needs one,'' Ochs offered. ``We're still trying to figure out why he doesn't leave a trail of Luck materia behind him as fast as he must be mastering them.''

Zack rolled his eyes, and though he let his hands drop from his head, he still looked a little put out. Not about the ear thing in particular, really; he probably just wasn't used to feeling like a stranger in his own body, with nothing quite working the way however-many years of experience said it should. Riku knew exactly how that felt. He also had a pretty good idea of how to distract Zack from it, at least temporarily.

``Hey,'' he said, smirking when Zack's nearest ear twitched automatically in his direction, hair-trigger. ``C'mere a sec,'' he added, hooking a finger under a shoulder guard and tugging until Zack leaned over and down.

He'd caught himself wondering idly before this whether Zack's hair was as soft as it looked, and it might just be the change\textemdash might be a little too close to actual fur right now\textemdash but oh yeah, it really was. Zack's eyes went wide and startled for about ten whole seconds as Riku buried a hand in those spikes, but then he found the base of an ear and began to skritch, and then Zack's eyes glazed over, just like that.

He was purring twenty seconds later, not just humming in encouragement but an actual scratchy purr from somewhere low in his throat, eyes falling closed as he leaned in for more. His head probably would have hit the table if Riku hadn't shifted his hand\textemdash and if Riku had kept right on skritching, he doubted Zack would even have noticed\textemdash but he propped Zack's head up with the heel of his palm and tried desperately not to laugh. It was funny, after all: that ridiculously happy look of near-ecstasy, the drowsy purr and the boneless slump, the way he'd gone all but literally putty in Riku's hands. It was just also sort of\textemdash 

``Oh, honey,'' he heard over his shoulder, and he looked up and back to see the bartender standing behind him, fanning himself with a peculiar smile. ``I'd say to get a room, but we don't rent them by the hour.''

Zack's disappointed growl when Riku stopped skritching had him praying to any god that would listen that he hadn't just turned a ridiculous shade of red\ldots only if the way Ochs nearly fell off his seat laughing was any indication, the gods were all incredibly hard of hearing.

Or spiteful bastards. He wouldn't put anything past Hades.

``Uh,'' he said, ``sorry. I didn't\textemdash ''

Know we were making out in public was a big one. Mean to freak anybody out would have run a close second, because he did get the fact that even though Zack and Titus had retained their essential\ldots Zack and Titus-ness to him, that didn't mean that everybody else felt the same way about what had probably looked like some heavy interspecies weirdness. Only no one looked offended, actually, just sort of surprised, like maybe humans and\ldots whatever-Zack-was didn't get up to that sort of thing very often.

``Hn?'' Zack said, blinking slowly back to himself. He definitely looked more comfortable in his new body, which meant Riku had at least got it partly right. He'd just meant it as a comfort and a distraction, like getting a neck-rub from Aeris or a casual sparring match from Cloud, the same sort of thoughtless physicality that had always grounded him when he didn't feel quite right in his skin and Sephiroth wasn't around to fix things his way. Though now that he thought about it, Sephiroth was nearly always around.

The bartender just laughed, saying, ``Oh, relax. You won't shock anybody here. I can't tell you how many times Caedmon used to\ldots well.''

Whoever this 'Caedmon' was, Riku didn't think it was embarrassment that made the bartender trail off like that, his story barely begun. There was something about the way that cheerful smile faded, turned rueful, that grabbed Riku's attention, instinct and curiosity alike clamoring to know more.

``We're not from around here,'' Riku said carefully, watching the bartender's smile quirk as if to ask, no, really? He wasn't sure the man would tell them anything; it was usually the patrons pouring out their troubles to a captive ear, or so he'd heard.

``Well,'' the man said at last, his faded smile going wistful. ``I guess that means you never met Rush Sykes.''

Riku shrugged. ``Afraid not.''

``That's too bad,'' the bartender said with surprising sincerity. ``He was the son of the Sykes, you know? Good kid, though, never acted like having famous parents had gone to his head. He came to Athlum looking for his sister\textemdash did you hear about any of this?''

Riku shook his head along with a few of the others. At least he had a name for the city now.

``Oh. Well, she'd been kidnapped\textemdash the not so nice thing about having famous parents, I guess\textemdash so of course the Marquis offered to help.'' Hooking his thumbs in his pockets, the man huffed a quiet little laugh, shaking his head. ``Actually, I bet poor Lord David didn't know what hit him. That Rush\textemdash he couldn't walk down a street without making three new friends, and you would not believe some of the people he brought into my bar. Everything from hill bandits to dukes! And Caedmon, of course\textemdash you know,'' he prompted expectantly, looking at Zack this time, ``of the Silver Falcons?''

``I've heard of them,'' Zack replied slowly but uncertainly, one ear tilting back. That seemed to surprise the bartender, but not unduly.

``Well! Not such a small world after all, I guess. Anyway, Caedmon. Er, no offense, but he's a bit friendlier than most of you sovani when it comes to us mitra,'' he said, grinning a little like he knew Zack couldn't possibly take offense\textemdash which happened to be true, since Zack had to be as clueless as the rest of them as to why their two races shouldn't get along. ``Well. I don't really know that they were more than good friends. I mean, I hear Rush grew up on Eulam\textemdash pretty much the back-end of anywhere,'' he explained with all the conviction of a confirmed city boy. ``And you sovani do tend to keep to yourselves, so maybe he just didn't know. But you can't grow up in Athlum without figuring out what a sovani looks like when he's being teased within an inch of his life,'' the bartender laughed, his nostalgic smile a thin patch on real regret. ``We all still miss Lady Emma terribly, of course.''

``Of course,'' Riku echoed, already trying to shuffle the stray bits of knowledge he was being doled out into something like a cohesive pattern. ``So\ldots what happened with this Rush guy?''

The bartender glanced past them\textemdash toward the door, or perhaps the castle Riku had caught a glimpse of over the rooftops\textemdash mouth tightening in sympathy. ``I think it hit Lord David hardest,'' he said at last. ``They couldn't marry, of course, not with the Marquis needing an heir, but everyone was betting he'd ask for a life betrothal at least. All you had to do was look at them. So when they went out to stop the Conqueror and Rush didn't come back\ldots ''

``He was killed?''

Shrugging helplessly, the bartender said, ``Who knows? No one's talking, and I hate to think he'd just walk away from Lord David, but\ldots it's like he just disappeared, just like the Remnants.''

Riku frowned. That sounded important, but\textemdash 

``Wait, Remnants?'' Zack piped up before Riku could find a casual way to ask. ``I thought those were just stories.''

Apparently they hadn't been giving Zack enough credit, because it turned out the guy had a poker face after all. No one could meet a pair of eyes that earnest and innocent and not cave\textemdash unless you knew him, in which case it just made you want to laugh. Not the 'earnest' part; mostly just the 'innocent.'

The bartender stared, agape, but Zack's gamble paid off. ``You're really not from around here,'' the man said, shaking his head and staring at them in something akin to awe. ``Sorry, I just\ldots you didn't have any Remnants? Where are you from?''

``It's a pretty small island,'' Riku hedged, hunching a shoulder. ``You probably won't have heard of it.''

``Huh. Must be nice,'' the bartender said, oddly wistful. ``It's been nothing but earthquakes here in Athlum since the Valeria Heart was taken.''

Now he really wanted to know\textemdash and he could guess that this Valeria Heart must be one of those vanished Remnants, and that the thing had apparently had some sort of power over seismic activity, but that still didn't tell him how, or what, or why. It was like being told that Sephiroth used to be a general, or that Sora couldn't be trusted in a kitchen. The thing really wanted background\textemdash and in Sora's case a camera\textemdash before the scope of it set in.

He was just making up his mind to find a roundabout way of asking when the street-side door opened and a pair of soldiers slipped inside, glancing around with a casual certainty that said the folks on the street had been all too accommodating about pointing out the path the strangers had taken. He sensed the others going on point around him, subtle shifts in posture that wouldn't have given them away to a casual observer but which stood out like a drawn sword to Riku's eyes: the way Stiegler leaned back just slightly to give Hall a better bead on the door, Schreiner's lazy shrug that settled the axe slung across his back to a more convenient place to draw it from, Titus' slow shift that got his massive new tail out of the way in case he had to lunge to his feet. He thought for a moment that Zack must've gotten control over his ears after all, right up until their sharp prick clicked in his head as fierce interest, wary and watchful.

The soldiers didn't hesitate coming away from the door, but their weapons stayed sheathed, hands empty as they approached. ``Are you the ones who\ldots arrived on the street earlier?'' the older man of the two asked, his stiff politeness mixed with a hearty dose of suspicion and embarrassment. He probably thought the reports his superiors had gotten were nothing more than a bunch of panicked civilians starting at shadows, was waiting to be laughed right out of the bar.

``Yes,'' Riku said simply, meeting wide dark eyes that stared at him uncertainly for a long moment before the man cleared his throat.

``Then the Marquis of Athlum has requested your presence at the castle at your earliest convenience.''

Well. That hadn't taken long at all.

``How about now?'' he asked, since they were all being polite and pretending any of them had a choice here.

The solider nodded once, embarrassment fleeing as assessment took its place. ``Yes,'' the man said slowly. ``I think that would be for the best.''


\scenechange


Zack hadn't been surprised to follow Riku out of the bar and find a dozen more soldiers just outside, waiting patient but alert for their sergeant's return. They didn't immediately snap to surround the strangers in their midst, were keeping things nice and friendly and very professional, and Zack appreciated that. He wouldn't have felt quite right squaring off against troops that didn't have the strength and durability of a SOLDIER behind them, though he was plenty pleased to see not all of the soldiers were human\textemdash or mitra, he guessed they were calling them here. No sovani\textemdash nothing that looked the way he did now\textemdash but a matched pair of bruisers like Titus and one of those rabbity little guys stood proud in the same uniform, and Zack could tell from the way the squad held themselves that they were used to fighting as a solid unit.

It was still sort of weird to have too many arms and to look down on the world from Titus' height\textemdash Titus when he was himself, anyway\textemdash but something told him no one else was going to be looking down on him, no matter what size they happened to be. The stares he got\textemdash and there were plenty\textemdash were never hostile, and he wasn't sure whether he felt more like a celebrity or a curiosity. He wondered if that was how Sephiroth felt all the time. He also wondered where all the other sovani were, because to hear the bartender talk, he'd thought they'd be more common.

What he was trying not to wonder about\textemdash not while it had the potential to be really distracting\textemdash was whether he should be apologizing for that moment in the bar or pretending it'd never happened, because even though he'd been knocked cross-eyed for a minute there, it just…hadn't been like that. Really. Riku hadn't been trying to work him up; he'd been trying to calm him down, and had, and if it'd left him a boneless, brain-extracted mess, well, so could a really good backrub. Instead he'd gone and embarrassed Riku\textemdash and he'd smelled that, bitter and prickly and sharp, only three times as clearly as even SOLDIER sensitivity should have allowed for\textemdash who for all he knew thought the bartender had a point.

Except that Riku wasn't acting any different, still as relaxed with Zack at his back as he had been an hour before. So maybe the second option\textemdash denial, denial, denial\textemdash was the one he ought to be going with.

Because part of him really wouldn't mind if Riku wanted to do that again.

To keep himself focused, he watched the people around him: the nervous and nonplused soldiers that didn't seem to know quite what to make of them, the people on the street with their carefree smiles and worried eyes. All of them were too caught up in their own problems to really pay the attention they ought to the strangers in their midst, though he had to give the soldiers credit for their guts. It wasn't like the glowing eye thing had exactly passed unnoticed, and folks who'd never even heard of SOLDIER tended to find that a little creepy. What made him want to grin\textemdash which seemed to have more to do with the corners of his eyes and the set of his ears than his mouth, at least in this body\textemdash was how their escort kept glancing at Riku, like they were trying to reassure themselves that there was at least one normal one in the bunch.

He wasn't exactly surprised to reach the castle and find it a buzzing hornet's nest, squad after squad forming up and moving out on the quick-march as they neared the wide-flung gates. He didn't see a single chocobo or horse anywhere, but there were giant lizards harnessed in tandem to entire supply trains, bawling out now and then to protest all the noise and bustle. So. Not that he'd doubted for a moment, but it looked like Riku had been right. There was definitely something going on here, and if it wasn't Heartless, then it had to be just as bad.

His gil was on the Heartless, though. Why else would a world want a Keyblade master badly enough to half-haul him here itself?

Security was tight inside the castle. There were guards everywhere, soldiers running in and out delivering orders, messages, ferrying and fielding the thousand and one questions that preceded a major campaign. Whatever was in motion here, it was big.

The throne room seemed almost peaceful by comparison, though it was hardly what you'd call empty. There was the blond guy on the throne, so bronzed his hair seemed unnaturally bright, his sober grey eyes almost colorless by contrast. The four standing closest to the foot of the dais where their lord sat were probably lords or generals in their own right, one for each of the four races he knew of, two in red, two in black. That was when Zack got his first look at another sovani, a big grey-furred guy with gold rings threaded through his alertly-pricked ears, lower arms folded forbiddingly in the same posture Zack had found himself adopting on instinct. He and the pint-sized guy were the two in red; the ones in black\textemdash to match the banner hung behind the throne and the marquis' own formal garb, at a guess\textemdash were the big fishy guy and a young woman with hair a few shades darker than Riku's own, closer to antique silver than his new-minted shine.

Zack watched the marquis take in those similarities at a glance and look to the woman, who briefly shook her head, reading her lord's thought without words. It was a funny thing, but when the marquis turned his attention back to them, the awareness of just how young the guy was just slipped away. He couldn't be more than two, maybe three years older than Riku, but they had that same air of confidence, a fixity of purpose that promised to plow right through whatever opposition cropped up in its path.

``My Lord,'' the sergeant who'd led them here began as they halted a prudent distance from the throne, and the few eyes that hadn't turned to them already were drawn in as conversation died. ``These are the strangers from town, here as you asked. They gave us no trouble,'' he added, his tone scrupulously fair. Information, not a boast.

``I see,'' the marquis replied. ``Thank you.'' Pale eyes regarded them each in turn, giving nothing away, but it took more than a level stare to cow a SOLDIER. He was rather more impressed by how quickly the marquis sized them up\textemdash twelve troops and one civilian\textemdash and made none of the perfectly reasonable assumptions another might have on seeing Zack standing side-by-side with Riku, not a deferential pace behind and to the left. ``You aren't Fourth Committee,'' the marquis stated neutrally, addressing Riku directly.

It didn't seem to be a question, but Riku answered anyway. ``No.''

``I see. We received strange reports of a group that seemed to appear out of thin air,'' the marquis added thoughtfully. ``If there's any truth to those rumors\ldots who are you, and why have you come to Athlum?''

``Knowing who we are wouldn't help you much,'' Riku said with a shrug, again leaving off any sort of honorific, though it made the woman in black narrow her eyes. ``As for why we're here\ldots we're looking for something. Something hidden.''

The marquis frowned, but he didn't look offended: a definite point in his favor. ``Explain.''

``That's\ldots easier said than done,'' Riku admitted, and Zack had to cage a smile when he realized that if the marquis was letting Riku's disrespect slide, Riku wasn't bristling at the marquis' curtness either, even a little. They probably had Sephiroth to thank for that; single-minded purpose actually started to sound like polite conversation after a while. ``We're not here to cause any trouble. We're just\textemdash ''

``Lord David,'' someone gasped from the sidelines: a mitra girl, young enough to be out of place hanging around a throne room, her wide eyes filled with a shocked sort of hope. ``He\ldots he's carrying a Remnant.''

The commotion that caused was instantaneous. The soldiers surrounding them fell back like they weren't sure whether they wanted to draw weapons or were just too startled to stand their ground, though Zack was pretty sure they were just giving their casters room to work. ``Irina,'' a grizzled man in a white lab coat said with heavy sympathy, laying a hand on the girl's shoulder, but she shook her head, her chin coming up stubbornly.

``He is,'' she said, staring at Riku like she wanted to interrogate him herself.

``Is this true?'' the marquis demanded, jerking to his feet like he couldn't bear to sit still.

``I don't even know what a Remnant is,'' Riku said warily, standing firm though it was clear they'd be fighting their way out of this one after all.

He might as well have said the sky was green.

Real anger narrowed the marquis' eyes, but the girl\textemdash Irina?\textemdash shook off the old man's hand and stepped forward, diverting Riku's attention. ``You do,'' she insisted, her voice so tight it cracked. ``I can feel it. How did\ldots where did you\textemdash ''

``Wait,'' Riku interrupted with an uncertain frown. ``You don't mean the Keyblade, do you?''

Irina shook her head, the word clearly not ringing any bells. ``Keyblade?''

Swords hissed out of sheaths on every side as Riku cautiously held out his hand and called the Keyblade to him, only Riku seemed as surprised as everyone else in the room by what actually answered.

It'd always been easy for Zack to pick out the blade's original form: the dark sweep of Soul Eater's wing, heavy and graceful at once. He'd grown up on stories of the thing, how it always picked its master, what happened to the ones that didn't measure up. The lighter wing it'd fused with at some point never quite looked out of place, but its purpose had always been just as clear. Taken together, the outline of the paired wings formed the shape of an old-fashioned skeleton key, the silver wing the teeth, Soul Eater the shaft.

They'd pulled apart now, floating just out of reach of Riku's still-outstretched hand, the two blades, falchion and rapier, circling each other like a binary star. Shreds of darkness and a hissing fog of light bled from their edges as they hovered, twining like snakes, never still.

Riku's voice sounded very loud in the sudden stillness when he spoke, his sheer consternation plain.

``What have you done to yourself now?'' he muttered\textemdash at his Keyblade, which\ldots actually made more sense than it should\textemdash reaching out to grab Soul Eater's hilt despite the darkness it was shedding.

The instant he touched it, the Keyblade snapped together again so seamlessly it might never have been split, though it still looked vaguely different: shinier, less organic. It occurred to Zack suddenly that maybe he and Titus weren't the only ones who'd been changed on arrival, that maybe this was this world's way of making sure Riku fit in, and he tucked that theory away to be brought up again later.

The marquis' jaw clenched tightly, but there wasn't a trace of fear in his eyes as he stepped down from the dais, approaching Riku without regard for the Keyblade in his hand or the SOLDIERs tensing to fight at Riku's back. ``Where,'' David began, his voice cracking the way Irina's had. ``Where did you get this? When\ldots how long has it been? Please.''

``It's not what you think,'' Riku protested, slowly shaking his head. ``It's not\ldots we're not what you think. I haven't done anything special.''

The marquis looked like he half wanted to shake some answers loose and half like he would have swallowed his pride and dropped to his knees if he thought it'd change anything. ``This blade,'' he said at last. ``What did you call it?''

``The Keyblade?''

``What does it do?''

``It locks things,'' Riku said with a wary shrug. ``Worlds, mostly.''

It was clear in the sudden, coiled tension of his stance that the marquis hadn't missed the monumental clue Riku had just let slip, but the question that followed wasn't the one Zack would have expected. ``Then it could unlock them as well?''

He couldn't have kept his ears from pinning back if he'd tried, and though he managed not to shudder as the fur on the back of his neck bristled, he was pretty sure baring his teeth like that was a dead giveaway. The big grey sovani eyed him narrowly, one pair of arms dropping casually to rest on the hilts of twin swords, but Zack was too busy watching the marquis to spare him much attention, and the marquis only had eyes for Riku.

Riku didn't quite recoil, but his face went tight and unfriendly. ``You don't want that. Trust me.''

David's smile was humorless, but his voice was soft. ``Actually\ldots I suspect there may be nothing I could want more. But I'm willing to discuss it if you're prepared to listen.''

It didn't sound like the ultimatum of a madman or a tyrant. He didn't look like he was about to set the guards on them or tell Riku to hand over the Keyblade. He just looked tired and very, very determined, like a reasonable man pushed past the limits of his common sense, and though that could be dangerous, it wasn't lost on Zack that these people looked like a collection of mourners, the battle they'd been gearing up for apparently forgotten in the face of hope.

Apparently it wasn't lost on Riku, either.

``All right\ldots I'll listen,'' Riku said, looking very much like he was agreeing against his own better judgment.

David nodded. ``That's all I ask.''

Zack wasn't the only one surprised when the marquis took a step back, met the eyes of the guard sergeants standing ready with weapons drawn and said, ``Clear the room. We'll speak with our guests alone.''

At least the guy wasn't crazy. 'We' turned out to mean his four advisors, the mitra girl and the man in the lab coat as well. All the same, that was one hell of a show of trust. Just what had happened here to make them put themselves on the line like that?

And who had they lost that had them willing to try anything to get them back?


\scenechange


Waiting for the last of the guards to file out, Riku released the Keyblade, deciding a show of trust of his own would probably not be out of line, considering the situation. Despite the unexpected changes the Keyblade had opened itself up to, it felt no different as it vanished, tucking itself away inside his heart while it waited to be called again. If he hadn't seen for himself what it'd become, he would never have guessed either of them had been touched by this world at all.

Now he really wanted to know what a Remnant was, but he got the feeling he was about to find that out.

``So,'' the marquis began once the audience room had emptied. ``How did you come to be in the possession of a Remnant without knowing what it was?''

``That's just it\textemdash it wasn't a Remnant until we came here,'' Riku insisted, watching the marquis closely.

David didn't disappoint him. ``From another world.''

``That's right.''

It'd been a stupid move, he was sure, letting that slip, but it'd just\ldots felt right at the time to throw that out there, see how these people would react. It'd been a nasty shock to have the marquis ask him point-blank to unlock their world when Riku's gut had been making different promises where the guy was concerned. Teach him to listen to his heart; he'd be better off leaving that to the experts.

He just didn't get why he still felt the nagging urge to hear these people out, to actually give back truth for truth if that was what it sounded like he was getting.

Pale eyes flicked him curiously, shifted to Zack, the SOLDIERs at their backs. He knew what they looked like\textemdash a crack troop and one crazy civilian along for the ride\textemdash but how David was interpreting that was anyone's guess. The marquis clearly figured Riku for the spokesman here; whether that job was expected to come with a title on this world remained to be seen.

``I see,'' David replied at last. ``And can you prove this?''

Riku frowned, seeing all at once how the world's open-armed welcome of them might actually work against them in this case. He couldn't just flash his Keyblade, not the way it looked now, not when it looked like he was traveling with a pair of natives. He couldn't think of anything he could show these people that would establish who they were\textemdash Hall's rifle, maybe, if he wanted to risk altering the progress of an entire civilization with off-world tech, assuming they hadn't developed firearms already. And as for magic\ldots he doubted a Dark Firaga would be all that impressive, not if coming here by dark portal had nearly gotten them labeled 'Fourth Committee'\ldots whatever that was.

``Only by showing you,'' he said at last with a shrug, ignoring Zack's sudden start beside him.

``Will you?''

And that\textemdash that right there\textemdash the way the guy asked without missing a beat, without pausing to define exactly who Riku would be showing these brave new worlds to. It made him want to trust, to agree without hesitation, and he would swear he felt the marquis' own disappointment when he reluctantly shook his head.

``Sorry\ldots but traveling between worlds takes a lot of energy even when you're just moving yourself, and we've come a long way. I don't have that kind of power to burn.'' Which wasn't exactly the whole truth\textemdash he could probably take them back out again if he really, really had to\textemdash but he wasn't going to admit that while they were still straddling the line between prisoners and guests. ``I think you're just going to have to let the fact that we appeared out of nowhere speak for itself.''

``On the contrary,'' David said with a wry, humorless smile. ``We've seen all too well the uses such portals can be put to, though I had assumed Wagram took the knack of it to the grave.''

Wagram. That didn't sound like any of the Nobodies Riku had ever tangled with, but there was no law that said Nobodies couldn't operate outside of Organization XIII. One could have traveled the dark paths and wound up here\ldots or maybe that was where this 'Fourth Committee' came in, human wizards building portals with simple magic, nothing to do with the darkness at all.

David shook his head, helpless frustration beginning to show. ``You must see how it looks. You appear, as you say, from nowhere\textemdash clearly soldiers, from the look of you\textemdash with a Remnant you claim to know nothing about, pretending an ignorance a child wouldn't own to. What would you have me do? Without proof of your claim\ldots name me one reason I should take you at your word.''

Not for the first time, Riku found himself wishing Sora had been along for the ride on this one, if only because Sora could have said ``Your heart'' with a straight face\ldots and been listened to.

Instead he found himself looking to the girl\textemdash Irina?\textemdash who'd kept silent all this time, anchored by the steady support of the scientist's hands on her shoulders. She was watching him now, tense as a wire stretched thin, standing with her hands together at her waist, steepled fingers pressed together so hard her skin was turning white and red around her neatly-trimmed nails.

``How did you know about the Keyblade?'' Riku asked her curiously.

She looked first to the marquis, but at David's nod, she met his eyes again with a stubborn sort of fearlessness he wasn't sure what to make of. ``I could feel it.''

Maybe that was weird for this place; it was definitely weird where he came from, since humans usually couldn't sense the Keyblade at all, not consciously. Only she definitely wasn't a Heartless, and he was pretty sure she wasn't a god, or a wicked faerie. He wasn't going to place any bets on her not being part Cetra, though, not after hearing Aeris' stories. It might just be a Remnant thing\ldots but he was just going to have to trust her anyway, no matter where her intuition sprung from.

``What else can you sense from it?''

She looked startled by the invitation, glanced over her shoulder at the old man\textemdash her father, maybe?\textemdash but at David's soft, ``Please,'' she nodded once to herself and lifted her hands, spreading them just wide enough to outline an orb of empty air between them.

When the first hissing rings of light lifted free of her skin, Riku stared in fascination as the rings solidified, trying to form a sphere around her hands and then\textemdash collapsing, reforming into new patterns even as Irina gasped, wide-eyed. As if she hadn't expected that either. He couldn't quite make out the shape the light was trying to form, but before it could come clear, he was distracted by the Keyblade appearing without his willing it, its two halves, light and dark, whirling around him in time with the pulses of light from Irina's hands. It made Zack fall back unwillingly, growling a little under his breath as the light half of the blade passed close enough for its shed glow to ruffle his hair, but Riku couldn't sense any threat from the Keyblade, only a sort of warning as reflexive as Zack's growl.

Shaking her head slowly, Irina dropped her hands, but though the light faded instantly, the Keyblade remained, its orbit slowing until the arcs it traced through the air looked less like a display of force than lazy complacency.

``Miss Irina?'' David asked in the silence that followed.

``I\ldots I don't know,'' Irina admitted, staring at Riku with frank bewilderment. ``It's definitely a Remnant, but\ldots it's not like any of the others. I can't take it from him.''

Was that what she'd been trying to do? Riku felt his own brows climb towards his hairline as muffled sounds of belated shock started up at his back, and for a minute he couldn't find his voice.

``Gaia,'' he heard Zack curse on his right, looked over and found the man staring at the girl with a look of horror that easily crossed the species barrier. ``I wouldn't even try. That thing\textemdash you don't\textemdash ''

``It's all right,'' Riku interrupted before Zack could give anybody nightmares, him included. He already knew Soul Eater was possessive. Getting spliced with a Keyblade hadn't exactly changed that. ``It doesn't work that way anyway.''

Irina was nodding like she knew what he meant, only what she said was, ``You haven't bound it.''

If hearing that she'd tried to steal the Keyblade out from under him had caused a minor panic in the SOLDIERs\textemdash more from having grown up on tales of how picky Soul Eater was about its wielders, he suspected, than from having any idea that it could actually be done\textemdash the news that his so-called Remnant was unbound caused more than a little consternation in the marquis' people in turn.

Riku shook his head, smiling a little at their disbelief. ``You don't bind a Keyblade. It picks you, not the other way around, and it's free to go when it chooses.''

``Then\ldots you're saying it has some sort of intelligence. A consciousness,'' David said, only without the surprise Riku would have expected.

``This one?'' Riku shrugged. ``Definitely. I don't know about the others. I don't know about your Remnants, either,'' he added before anyone could get any ideas. ``Like I said, this is all new. The one thing I do know,'' he said, realizing all at once that he did have something like proof after all, ``is that you people have a Heartless problem, and talking in circles like this isn't doing much to get that fixed.''

The marquis frowned, but it was the woman in black who stepped forward, saying with the same posh accent: ``Heartless.''

``They may not be here in the city,'' Riku said around another deep breath, just to be sure he wasn't making a liar of himself. ``But they're close. The new monsters you've got running around. We call them Heartless because that's what they feed on, and once you have your heart taken, that's what you become. Once they move in, it's just a matter of time before people start vanishing\ldots and then everything else.''

``And what do you have to do with the Heartless?'' the sovani in red demanded, two hands clenching and relaxing on the hilts of his swords.

One look at the marquis' tight, unhappy face, and Riku knew he'd just be stating the obvious, at least for one of them.

``They're what's on the other side of that door you want unlocked,'' he said, more sympathetically than he might have. It wasn't much comfort to know he'd been right in trusting the marquis after all.

``I see,'' David said softly. ``But\ldots isn't our world already unlocked? If you were able to come here\ldots if those things are already here\ldots is there no way to go and\ldots bring someone back?''

``I\textemdash ''

He would have explained that it wasn't that simple, that 'open' didn't mean 'unlocked.' And as for finding one particular person out there in all the worlds Riku knew of alone\textemdash as well try to find one particular pebble on all the beaches of Destiny Islands. It probably could be done, but there were so many factors standing in the way\textemdash time, the Heartless, the promise he'd already made to get his own\ldots people\ldots home\ldots 

From the lower courtyard below the castle, a din of trumpets rang out that drowned out his voice before he'd even gotten started. It made everyone jump, but even as the marquis was grimacing in frustration as he was called back to the present, those pale grey eyes were sharpening on Riku decisively.

``Wait,'' David said, cutting Riku off before he could try again to let the guy down easy. ``You say you're here to fix our Heartless problem.'' Which wasn't exactly what he'd said, but yeah, close enough. ``Come with us. You seem to want our trust; here's your chance to prove yourself trustworthy.''

And, not so incidentally, David's chance to talk Riku around; he was sure of it. Still\textemdash 

``Not that anyone's saying you're wrong,'' Zack piped up, folding all his arms as Riku made a grab for the Keyblade. ``But how do you figure that?''

David's smirk was almost friendly as he answered, tipping his chin up comfortably to meet Zack's stare. ``If you can travel instantaneously,'' the marquis said, ``you didn't need to wait to be summoned; you could have disappeared. Nor did you need to try to convince me of your claims. I may not understand all that you want, but that much seemed obvious. Don't you think?''

The twitch of Zack's ears could have been wry or disgruntled\textemdash was maybe both\textemdash but there was no mistaking the faint sigh of the marquis' sovani for anything but weary patience in the face of one of his lord's more outrageous schemes.

As if Riku wasn't grudgingly starting to like the marquis already.

``Well?'' David asked.

Riku glanced at Zack, who nodded gamely back.

``All right,'' he said. ``Lead on.''


\scenechange


He hadn't expected his decision to go unchallenged. Marquis he might be, but he had four of the sharpest minds and strongest voices in Athlum at his back for a reason, and it certainly wasn't for their blind obedience. All the same, he'd thought the question would come from pragmatic Torgal, long-suffering in the face of such precarious optimism as only a sovani could be, not in Pagus' thoughtful tones.

``Other worlds,'' the qsiti mused aloud, matching David's determined strides in steady bounds. ``A curious story, my lord. Perhaps too curious?''

``Indeed\ldots but that's what makes it so compelling. A clever liar would have chosen something more believable. But perhaps that's what we're supposed to think.''

``A convoluted suspicion.''

``Yes,'' David admitted with a tight smile. ``But it hardly matters. If there's any chance\ldots ''

``I understand,'' Pagus replied, bowing his head gracefully, gold eyes turned politely away. ``Shall I accompany them, my lord?''

``Please. Treat them\ldots '' He knew what he should say. They were an unknown force, possibly hostile, very likely duplicitous. And yet. It was unquestionably a conceit, but he liked that their leader had won the loyalty of a sovani, liked very much the honest, unthinking shock in that same sovani's eyes when it became clear Irina had put herself in danger. He'd liked the bluntness of their leader as well, the forthright stare of someone too proud for lies. ``Treat them as honored guests, but keep me informed.''

If Pagus thought him mad, his general kept that suspicion to himself. Having satisfied himself that David was at least not blindly clutching at straws, Pagus would do his best to see David's orders carried out. Of all his generals, Pagus had the most skill with diplomacy, the coolest head of the four.

And if these people were indeed exactly what they claimed, there was a chance that they might have no experience of qsiti to draw on, might underestimate Pagus' diminutive size and take him for the least threatening of the lot. If that happened to make them more talkative\textemdash and he dearly hoped it would\textemdash he could hardly be blamed if he learned more of them than they might wish.

Though truly, there was only one thing he wanted to know, and it made his stomach roil uneasily to think that the answer he received might depend on lightning striking twice.

He'd been trusted once before\textemdash blindly, without reason, on sight\textemdash and the odds of that happening a second time were more dismal than he cared to contemplate. But he would try, not because he had no choice, but because he'd devoted himself to deserving that trust, and he would no sooner turn his back on the man he'd become than he would on the one who'd won that same trust of him in turn.

If that made him a fool, it would at least be one Rush recognized when he returned\textemdash and he would return.

David was not prepared to believe anything else.


\scenechange


Forewarned by the lack of horses on the way in, Riku wasn't surprised to find they had a long march ahead of them. It interested him more to be shuffled into the ranks of David's party and to find that the Marquis of Athlum apparently led the troops in this, as well. It didn't take long for the man's four advisors to be called away\textemdash each one of them answering to the rank of general, as it happened\textemdash and Riku couldn't help noticing that the troops each general commanded were a casual mix of species, integrated to a degree he'd only seen on Mickey's world before. Radiant Garden came close with its moogle craftsmen, the enterprising nephews who ran one of the shops and the roving band of pixie pickpockets that made Leon mutter about flypaper and glass jars, but even they tended to keep to themselves. He did notice the lack of other sovani, but what did he know? Maybe they were just really rare.

Riku grinned. Trust Zack to stand out in a crowd.

``So,'' Zack said as the others formed up, waiting for the word to move out. ``You think these guys are for real?''

Riku chewed his lip, wishing he could say yes, unreservedly, and make it stick. ``I don't know,'' he admitted after a moment. ``I mean\ldots the marquis' been pretty up-front about wanting our help, and I don't think he knew what he was asking with the whole unlocking thing. Part of me wants to trust him, but\ldots it's not something I want to be wrong about.''

Zack cocked his head. ``You could always do that thing,'' he offered, lifting a hand to waggle his fingers like a particularly overdramatic wizard. ``You know. Losstarot's trick.''

``Soul scrying? Yeah, I've done that once. By accident,'' he added with a self-deprecating smirk. ``I'm not sure I want to pull that on a marquis in the middle of an army\ldots even if I do get it right.''

``You could practice,'' Zack offered, fearless and relaxed, and Riku didn't have one doubt in his mind who Zack was putting forth as the guinea pig.

``I\ldots don't think that's a good idea,'' he said, torn between gratitude and an instinctive horror even he didn't get at first\ldots until he did. ``Sydney said\ldots most people tend to show you the worst moment in their existence when you hit them with that. I don't\ldots think I want to just take that from someone. Especially not a friend.''

Now it was Zack who looked torn, eyeing him with mingled sympathy and alarm, ears flattening slowly as he asked, ``Is that what Losstarot saw when he\ldots ?''

He tried hard to play it cool, but the heat in his face\textemdash and the sudden, curious prick of Zack's ears, the way Ochs started coughing helplessly into his fist and Titus' dry snort\textemdash had him groaning in mortification. ``Gaia, if only,'' he muttered. ``I think I surprised him too.''

Zack was grinning like he could just imagine, but then the guy shook himself, hard.

``Right. So what happened back there with the Keyblade, anyway?'' Zack asked, dragging them back to less embarrassing topics. ``The Remnant thing, I mean. You okay?''

``Yeah,'' he said with a shrug, ``just more world magic. I shouldn't even be surprised,'' he grumbled, shaking his head.

``You sound like it's done this to you before,'' Titus rumbled at his back, amused and curious.

``Not the Keyblade so much,'' Riku admitted. ``Mostly just Soul Eater. You may have noticed he wasn't always a Keyblade, either.''

``Yeah, I was wondering about that,'' Zack said, one ear flicking distractedly as a pair of running soldiers clattered by. He must be getting comfortable in his new body; he didn't even flinch when his newly-mobile ears started gathering reconnaissance on their own.

``It's a long story, actually. Just\ldots you know. Most. Possessive. Sword. Ever.''

That made the others laugh, Zack reaching out to scruffle his hair, which was something he was not just getting used to but actually coming to expect. Zack was just a tactile kind of guy. There was absolutely no reason for them to be drawing stares from the locals over it, or for those surprised looks to have Zack tensing with a quiet, ``Oops,'' withdrawing his hand like he thought he'd done something wrong. And okay, so maybe Riku was glaring just a little at their audience, wondering if he wasn't seeing any sovani in the ranks because any idiot could tell when he wasn't wanted, when someone decided to intervene.

He started a little at the throat that was cleared on his left, looked over\textemdash and then down\textemdash to meet the amused gold eyes of one of the marquis' four generals, who looked like he was only slightly too dignified to laugh at them outright.

``You'll have to excuse them,'' said the little guy\textemdash Pagus? their introductions had been rushed\textemdash the wide corners of his mouth quirking up at the dubious arch of Riku's brow. ``Your lieutenant is\ldots remarkably approachable for a sovani.''

``He's, uh\ldots not exactly my lieutenant.''

``He's not exactly a sovani, either,'' Zack muttered under his breath, so quietly Pagus probably hadn't heard him.

Riku kicked him anyway, and that got them a raised brow even from the general\textemdash who didn't exactly have brows, so Riku wasn't quite sure how that worked. Either way, the look of thoroughly-entertained disbelief they were getting needed no interpreter.

``My apologies,'' Pagus recovered enough to say. ``I'm afraid I'm not familiar with your insignia. May I ask what rank you hold in\ldots ?''

``SOLDIER,'' Zack offered, ``and that's an organization where we come from, not just a description. It's kind of confusing for outsiders, I guess,'' he added with an easy shrug, ``but other than what class you end up in, there's not a whole lot of difference in rank between SOLDIERs\textemdash and we're all Firsts. The First Class usually work alone anyway, so it's kind of pointless to start handing out fancy titles. I mean\textemdash lieutenant colonel of what?''

``Interesting,'' Pagus murmured, glancing back at Riku. ``And you?''

``Me? No one special,'' he was quick to disclaim, hoping to avoid being my-lorded this time around. ``I'm just along for the ride.''

``I\ldots see,'' Pagus said, looking all the more like he was trying not to laugh, which had Riku darting a suspicious glance over his shoulder.

Coughing delicately, Zack stopped mouthing whatever it was he was mouthing\textemdash the tail end of it looked like ``Keyblade master"\textemdash and tucked his upper pair of hands behind his back.

The lower pair that he'd apparently forgotten were still pointing in Riku's direction.

``Approachable,'' Riku said with a huff, biting back a smile. ``Is that what we're calling it these days?''

``You're just jealous because I'm the special one here.''

``Zack's forgetting he's the 'special' one in any world,'' Titus deadpanned in a cavernous rumble, his altered features making even his attempt at an innocent expression look vaguely menacing. So that was nothing new.

With the martyred air of the unfairly maligned, Zack heaved a wounded sigh. ``I just want to say that I love you all.''

``Hey! Not in front of mini-Boss,'' Stiegler scolded, which made Zack sputter\textemdash 

And that was apparently too much for even General Pagus, who gave up his dignified air with a delighted chuckle. ``Goodness\ldots I can see this will be an interesting trip,'' the little guy offered, examining them all with friendly curiosity.

``You've been assigned to us, then?'' Zack asked, like he was already sure of the answer. Riku hadn't even considered it.

``Indeed. Lord David thought you might have questions, which I'll be more than happy to answer. You won't mind if we talk on the move?''

``Try us,'' Riku said, moments before the trumpets sounded a second time, giving the order to march.

He'd sort of wondered whose pace they'd be traveling at, assuming the big guys like Titus\textemdash yama, Pagus informed him with only a hint of surprise when he asked\textemdash would be slower, that the qsiti like Pagus himself would need more frequent breaks after keeping up that double-time hop to match pace with the longer legs of the mitra. It was a little surprising to see that they all evened out in the end, that the long, slow strides of the yama came paired with unbelievable stamina, that the energetic qsiti could have outpaced them all if strict discipline hadn't kept them smartly in rank.

Still. ``Do you guys seriously walk everywhere?'' Riku asked once they were well underway, Athlum's walls long-since disappeared into the distance.

``Nowadays, yes,'' Pagus said with a faint sigh, forgetting himself for the space of one distracted bound before curbing himself to Riku's pace again. ``Before the passing of the Remnants, you could find transportation devices throughout the world\textemdash not the most efficient means of travel, as they could only transport small parties at a time, but convenient if you found a sudden need to be quickly elsewhere. It's not safe anymore to travel off the main roads\ldots though I suppose one could argue that it's never been entirely safe. It's something the Academy is working on, of course\textemdash in Elysion,'' he added at Riku's silent headshake, as if that was supposed to help. ``They used to study the Remnants, but now they've turned their talents to developing the Mystic Arts. The Fourth Committee would be very pleased to make your acquaintance; their focus is trying to recreate the effects of the Remnants, and translocation spells are a particular interest of theirs.''

``Huh.'' That explained why they'd been mistaken for this Committee at first. ``But you still haven't explained what a Remnant is.''

Pagus eyed him for a long moment as if waiting to hear the punch line, but when Riku didn't crack, he gave in with good grace. ``Remnants are\ldots or rather were\ldots artifacts of some power. It's difficult to settle on a description, I'm afraid; they came in all shapes and sizes, some common, many unique. Some held unimaginable power, and some were little more than interesting diversions. A few\textemdash the Great Remnants\textemdash were passed down from lord to heir in each of the major cities. Athlum was fortunate enough to be graced with two: the Valeria Heart and the Gae Bolg.''

``We heard about the Valeria Heart,'' Riku offered with a shrug. ``It controlled earthquakes, right?''

``Among other things. Those who came near it often reported a feeling of well-being, and nearly everyone found its presence soothing. That always struck me as interesting,'' Pagus confided with a smile. ``'Soothing' isn't an impression I'd generally attribute to a sword.''

``A sword?''

``Yes, indeed. A most impressive sword; it used to stand in the town square, and though it was never formally measured, the hilt and guard used to be directly visible from the audience room of Athlum Castle. Needless to say, it was visible for miles.''

``That's some sword,'' Zack agreed. ``So what happened to it?''

Pagus sighed, his large eyes and wide mouth turning a sorrowful expression tragic. ``Ah. I'm afraid the Valeria Heart was taken from us even before the disappearance of the Remnants. A being known as the Conqueror attacked the city while the greater part of our forces were elsewhere, and\ldots captured the Remnant.''

``Captured?'' Riku echoed.

``Evidence suggests,'' Pagus replied grimly, ``that the Remnant did not leave us by choice.''

Well, that sounded familiar. Maybe possessiveness in swords was more common than he'd been led to believe.

``What about this Conqueror?'' Titus asked, and Riku glanced back to find him peering down at Pagus with a thoughtful frown. As immense as he was now\textemdash and he had to be pushing eight feet, if he hadn't managed to top that\textemdash he moved as lightly as ever, his unhurried amble as deceptive as his usual quiet. Big as he was, and as laconic as he tended to be, nothing much escaped him. ``You said 'being.' I take it he was different?''

``Yes,'' Pagus said slowly, tensing minutely for the first time at their questions. ``Though he appeared to be an adult mitra, in truth\ldots he was a Remnant himself.''

``And that's strange,'' Riku stated, just to make sure he had the facts straight. ``There'd never been another Remnant that\ldots looked like a person?''

``Not that we were aware of at the time,'' Pagus replied carefully. ``The Conqueror felt that the Remnants should be freed of human control\ldots and admittedly, there was some merit to his way of thinking. In the wrong hands, the power of a Remnant could be a frightful thing, and even in the right hands, there were\ldots costs involved in the loan of their power. Some even argued that our reliance on Remnants was stifling our potential as a people.'' Shaking his head, Pagus hopped along in silence for a moment before he sighed. ``I'm afraid I can't speak to that; I weighed the risks once myself and found the benefits outweighed the dangers, and I've long since made my peace with that. And I assure you, it was not easily done.

``The Conqueror, though\ldots he was of a mind to not only free his fellow Remnants, but to\ldots empower them in a most unorthodox way. Apparently it was possible for a Remnant to completely consume its wielder, and\ldots while I'm not entirely certain of the mechanics myself, the Conqueror was able to activate a device that would have rendered all life mere energy to be devoured.''

``Gaia,'' Hall breathed over the Sarge's startled curse. ``Are you serious?''

``Quite so, I'm afraid.''

``But that kind of magic\textemdash ''

``Yes, exactly,'' Pagus said, oddly startled and just as oddly pleased. ``Magick, of a kind not seen in more than a thousand years. I wonder sometimes if that wasn't what the Remnants were truly created for,'' he mused, almost to himself. ``To channel safely that which we could not. Nevertheless,'' he said firmly, shaking himself back to the present, ``we were eventually able to stop him. But in reversing that device, it was the Remnants who disappeared instead of us. They just\ldots dissolved, before our eyes. There was nothing we could do.''

Riku found himself trading a solemn look with Zack. Those weren't the words of a man who'd lost a convenient tool, however useful. That was someone missing a friend, who still hadn't gotten over the loss.

``So\ldots if the Remnants were destroyed,'' Riku began, only to trail off at Pagus' swift headshake, the fiercely-leashed hope staring up at him.

``It is a possibility\ldots but not, I think, a certainty. When I say the Remnants were created, that's little more than speculation on my part. The histories tell that when they first appeared, they appeared from nowhere. Even in more recent times, Remnants were discovered, altered, repurposed\textemdash but not fashioned. Logically, having sprung from somewhere\ldots ''

``They may have returned there,'' Riku finished for him, feeling inexplicably lighter as some of the tension he'd been carrying around drained away. ``Not a separate world\ldots a world within a world.''

``Is that possible?'' Zack asked, curious but willing to take his word for it.

``Yeah. I've been to a couple like that\textemdash you'll see what I mean if we swing by the Coliseum, or Meifu. Sometimes worlds are just sort of\ldots linked together, like conjoined twins. Pretty easy to cross over if you just know the entry points. And sometimes a world develops inside another world, like\ldots a pearl inside an oyster, I guess. Those are harder to get into, but once you have the knack, you can cross over from anywhere. It's not a matter of unlocking them, either\textemdash if their world-hearts are healthy, they're not supposed to be locked against each other. They're supposed to exist in balance.''

``So if this is one of those joined worlds,'' Titus prompted, beginning to smile along with Riku.

``Then I won't need to open this one up and risk letting things in\textemdash I'll just need to figure out how to get deeper inside it.''

Grinning in triumph, Riku turned to Pagus to interrogate him further, only to find the qsiti staring at them in mingled bafflement and uncertainty. Having a pretty good guess as to why, Riku curbed his smile a bit, letting it go wry as he asked, ``You didn't really believe us, did you? That we're not from this world. You still don't.''

``You\ldots certainly do sound sure of yourselves,'' Pagus offered diplomatically, one talontip scratching gently at the tip of his nose. ``It's just a bit much to take in.''

``Don't worry,'' Riku assured him. ``You don't have to believe that part. But if I find a way to reconnect the Remnant world\ldots won't that give that Conqueror guy a way back in too? Are you sure you want to risk that?''

``It's a risk we're willing to take,'' Pagus replied, his reedy voice firming with determination. ``There's another Remnant who we believe would want very much to return, if he yet lives. The rest are certainly welcome to remain where they are, if they so choose.''

``Even with the earthquakes?'' Zack asked skeptically, voicing aloud what Riku had been wondering himself.

``Even so,'' Pagus replied with a decisive nod. ``We learned once to exist without magick; we can learn to exist without our Remnants as well.''

``Uh\textemdash wait,'' Hall piped up warily. ``Without magic?''

Pagus frowned, glancing amongst them again as if to ask what the joke was this time, but just as the qsiti opened his mouth to reply, a shrill of trumpets announced their arrival.

``Yamarn Plain,'' Pagus offered as Riku turned his eyes front again, realizing that the slow, steady incline they'd been climbing had sheared off all at once, low cliffs giving out onto a great, flat plain that stretched for miles, positively overflowing with Heartless.

Moving up through the ranks until he came even with the marquis, Riku stared down from the cliff's edge and flexed his hands, feeling the Keyblade thrum inside him. ``Man,'' he heard Ochs say, for once without an edge of laughter. ``That's a lot of Heartless.''

``And those aren't Shadows, either,'' Stiegler grumbled. ``What the fuck have they been eating?''

``Jhana, if I had to guess,'' David replied, mouth quirking briefly at the Sarge's unguarded speech. ``I was wondering why they seemed so quiet lately.''

``Jhana,'' Riku echoed, frowning. The Heartless below were humanoid but brutish, something like a cross between a man and an ape, or maybe a bear. Thick-shouldered, gangly-armed and short-necked, they were dark navy, bruise-violet and a sickly sort of black, though the ones carrying swords wore deep crimson hoods. All of them wore the Heartless symbol across their barrel chests, but there were clear differences in type; he just didn't know enough about the original model to guess what these might be capable of. ``Tell me about them.''

``Beastmen,'' a guard captain offered when David shot him a doubtful look and remained silent. ``They travel in packs, attack anything that moves. Little better than animals.''

Riku snorted. ``They may not be great thinkers, I'll give you that, but from where I'm standing, it looks like they're still social. And if that's carried over into their Heartless, then this is not going to be pest extermination, believe me.''

The captain sputtered, but David raised his hand, waving the man silent. ``The midsized ones. Those should be fighters,'' David explained, ``dangerous mostly in numbers. They're quite strong, but not very graceful and not very fast. The smaller ones are shamans\textemdash they'll hang back in support, but they fight quite fiercely when cornered. Don't mistake them for cowards.''

``Not a chance. And the ones in red?''

``Magi. Skilled in both combat and the Mystic Arts.''

``Not magic?'' Riku hazarded.

For some reason that made David flash a tiny little grin, laughter brightening his eyes. ``Thank Marian, no. That would make things interesting, wouldn't it?''

Okay\ldots so clearly something was getting lost in translation here, but there wasn't time to figure out what. If the trumpets hadn't been enough to give away their arrival, they'd definitely been spotted by now, and already the Heartless were massing together, gathering themselves for a charge.

``Got it,'' Riku said, and with a grin and three steps running start, he called, ``See you at the bottom!'' as he launched himself over the edge of the cliff, calling the Keyblade to him at the same time.

It was a little weird to be in freefall with empty hands, his arms stretched out and his fingers spread wide, for the Keyblade, still split in two, to be hovering just out of reach instead of sliding comfortably into his palm. It was worse to realize all at once that he had no idea how to control it like that, that he'd seen Sora do much the same but had never tried it himself. Always before when he'd summoned a second blade, it was to give it away, and this wasn't really the same thing. It was still his blade, just the one, only\ldots different.

He landed in a crouch when his feet hit the weedy grass below, but it wasn't that far of a drop for him these days, and he came up ready to fight. He only hesitated half a second, wondering if he should have thought this through, and then he was sprinting to meet the enemy, Way to Dawn circling him as the two blades spun in glittering arcs along the course of their orbit. Their whirling picked up speed with every step he took, the air around him humming, until they suddenly locked in place to either side of him, reversed their spins, and shot forward with a will of their own to plow into the ranks of the Heartless before him.

Where the whirling blades hit, they shredded everything in their path, ragged gouts of shadowflesh bannering up like smoke in the wake of freed hearts. For a moment Riku stood in the center of a cleared circle of absolute carnage as the Heartless flowed past him and closed ranks, until a bewildered fighter slipped through almost by accident. It didn't stay confused long; Heartless rarely did.

There wasn't time to worry about his empty hands or ready himself for a spell. He might not be as strong as Sephiroth or even Titus, but he wasn't exactly a weakling either, and long hours of sparring with the best fighters on any world meant he wasn't a stranger to being disarmed.

The first kick stunned the thing, and the second knocked it back, and he was just winding up for the one that ought to take it out when it stumbled back a little too far and Soul Eater took its head clean off.

``Nice one,'' he breathed, his sharp ears picking up the keening purr in Soul Eater's hum that meant the dark sword was feeling smug.

Zack hit the front lines just seconds later, Titus and Ochs hot on his heels, and once Schreiner waded in, Riku found himself able to push forward, making headway against the endless tide of Heartless. It left him feeling more than a little unbalanced to have nothing in his hands, to leave most of the work of fighting to the Keyblade, but it wasn't like that left him helpless. It just gave him more room to cast.

He figured on starting small\textemdash a Dark Firaga ought to do it\textemdash because he still didn't know what to make of that whole 'no magic' thing, and it made him a little nervous. He didn't seem to have any trouble gathering the power, at least\textemdash the darkness filled him up the moment he asked for it\textemdash but when it came time to release it, it just\ldots wouldn't go. It overflowed instead, leaching through his skin to envelop him in a shadowy haze, flickering wildly as he stared down at his empty hands in disbelief.

``What the\textemdash ''

``What are you doing?'' a harried, accented voice snapped at him, and he glanced up dumbly to meet David's eyes just as the man slapped a knife hilt into his palm, ignoring the lick of dark fire against his own skin. ``Focus through that!''

``What?''

``Through your\textemdash Marian bless\textemdash ''

Stepping between Riku and the Heartless surging toward them, David lifted his own sword before him, the flat of the blade braced against his other palm, gathering himself with a deep breath and\textemdash 

Acid. Great gouts of it spewing up from nowhere, eating through Heartless flesh like rain through spun sugar. How none of it managed to hit their allies, Riku couldn't begin to imagine, but it gave David time to whirl back to him, furious with worry, shouting, ``Through your weapon\textemdash you focus through your weapon! How do you not\textemdash ''

``Are you serious?'' Riku blurted out, because really, all that staff-swinging and wand-waving he'd seen Maleficent and Merlin do had always struck him as dead embarrassing.

He'd shocked David silent, though, because the man just stared at him, like maybe it was really sinking in that Riku had not one clue about the things people were just supposed to know here.

``Yes,'' David said simply, and Riku took a deep breath\textemdash and glanced past the marquis to find a line of Heartless Magi putting the finishing touch on some joint casting, light erupting like an explosion from at least a dozen swords.

Concentrating on throwing out the biggest Dark Shield he had in him, Riku drew back in all the power wreathing him now, calling more, and felt it flow out of him this time: through his palm, through metal that vibrated like a struck tuning fork, blued steel humming like it'd splinter in his hand.

The shield went up with a crack like a sail belling out, the slick black of an oil slick, a good thirty feet from end to end. Shocked himself at what he'd done, he felt his eyes go wide, stubbornness alone all that kept his jaw from dropping inelegantly to his chest. All the same, he didn't think it would hold\textemdash what hit the other side screamed like a fury, sent crackles of cold-steam hissing into the air as a rime of frost whitened the inner face of his shield, and darkness itself was already cold, dead cold. Ice and the Dark strained against each other, creaking, groaning, but it was the ice that gave out first, the Dark Shield rolling over the Heartless ranks behind it before it dissipated at last.

When he glanced sidelong at the marquis, he caught the man staring still, but that didn't last for long. Shaking himself, David said, ``We need to take out the Magi first.''

``On it,'' Riku said, diving immediately back into the fray, and realizing only belatedly that he hadn't handed back the marquis' knife.

Something told him David wasn't going to ask for it back just yet anyway.

Though Way to Dawn had pulled back when the shield went up, the twin swords came streaking out of their ready hover the instant he began to move, tearing into the Heartless like a pair of scythes. He heard David shout something at his back, but it wasn't aimed at him. It sounded like: ``For the glory of Athlum!'' actually.

And damned if the man's troops weren't actually following him, right into the midst of the Heartless, like that was glory enough to be fighting for.

Zack came up on his right, ducked Soul Eater with a laugh and asked, ``Where to, mini-Boss?''

``The mages,'' he called back, nodding dead ahead, and caught Zack lighting up with a grin that bared way too many sharp teeth. He wasn't even sure it was a grin, not in that body, but the gleam in Zack's eyes was the same as ever. ``And pass the word\textemdash if you have to do magic, focus it through your weapons.''

That got Zack's attention. ``Gaia\textemdash you mean it still works? How'd you\textemdash ''

``Don't ask,'' Riku groaned. ``We'll figure it out when we're\textemdash ''

If Zack had gone pale under all that fur, it certainly wasn't visible. Riku couldn't put his finger on what gave the man away, whether it was the widening of his eyes or the set of his ears\textemdash or maybe he was the one scaring ten kinds of hell out of Zack, because\textemdash 

``Hall!'' he heard Zack shout, with too much sovani growl to carry half as far as the man's own tenor would have, and it probably didn't help that Riku was yelling ``Sarge!'' right on top of him.

``We got it!'' he heard Stiegler yell back, like the man thought he'd been given orders, and when Riku raked the battlefield for sight of the pair, he nearly forgot why he'd been shouting in the first place.

Whatever the monster those two were squaring off against had been, it was huge, and if it had anything in common with the mutated scorpion it resembled, Riku didn't want to know how big they got in this world. Four of its arms could have passed for tentacles, and the tip of its tail rose a good twelve feet in the air\textemdash if that even was its tail. The glowing green eyes where the stinger should have been could have been decoys, like a moth's wing-spots, because the lower bit at the front of its trunk was definitely all teeth.

He watched with his heart in his mouth\textemdash still moving forward, throwing kicks and punches and swings of his borrowed knife mostly on autopilot\textemdash as Hall threw out a hand, rifle still slung across his back and chanting something they were too far away to hear. Not waiting for Hall to finish, Stiegler was already wading in, and damn it\textemdash he'd meant to make sure the Sarge was covering Hall, when he should have been worried that just this once, through no fault of his own, Hall wouldn't be covering Stiegler.

The big Heartless flinched back with a hiss as Stiegler slammed into it, the pincers on the ends of its four flailing arms snapping like jaws, but before Riku could snap off a spell in Hall's place\textemdash too far away for a Dark Firaga, and Stiegler too close for anything as messy as Sin Harvest\textemdash the whole thing went up in acid-green flame, screeching as it was engulfed.

Hall, grinning without a care, fisted his still-outstretched hand and lashed out at a Heartless that got too close, sending it reeling back into its fellows as he ducked aside from a warhammer's sweep. When he flicked open his fingers and gave the nearest Shaman a faceful of lightning, Riku turned back to Zack, dumbfounded.

``How the hell is he doing that?''

``Uh\ldots it's Hall?''

``Right. What was I thinking?'' Riku muttered, shaking his head.

They reached the Heartless Magi at the same time, Zack shattering lesser swords with relentless blows of his own, Way to Dawn scything through the pack while Riku threw off every spell he could think of into their midst. He almost missed it when one fell back, only to call for reinforcements\textemdash almost missed the heavy mace that came close to flattening him before a bolt of light whipped past him, the flare of magic briefly searing his retinas before it buried itself in one round golden eye. As the Heartless Magus dissolved in a burst of shadows, Riku glanced swiftly back, just in time to catch David's sword sweeping back down out of his casting stance to strike at the nearest Heartless.

He almost couldn't believe the guy was keeping up with them, but he didn't think Athlum had anything to worry about where her glory was concerned; apparently her marquis had that well in hand.

As the last of the Magi disintegrated, the Heartless around them began to fall back, whatever passed for self-preservation in things that lived only to consume beginning to make itself felt. Though the plain was still littered with Heartless, Riku paused to catch his breath, relaxing a little as he watched Athlum's forces spread out, turning to flank the now-disorganized army and bunching them up for the slaughter. Ordinary muscle and steel couldn't have done it, but whatever they were calling it on this world, these people had clearly made an art form of magic, and unless he missed his guess, half the officers' weapons carried enchantments. It might have been an uglier fight without their help, but he had to admit, these people could hold their own.

``Not bad,'' he heard at his back, and he turned with a grin, purposefully cocky.

``We get better.''

David only smiled, though his eyes were preoccupied. ``I'd look forward to seeing that if you were to continue on with us.''

``There's more, then?'' Zack asked as he joined them, the oversized sword he still carried at the ready for once looking properly-scaled for his size in a sovani's big hand.

``Indeed. If we carried the day here, we agreed to join the forces holding the Heroic Ramparts. If they break through that defense, Ghor will almost certainly fall, and Elysion after her. As for Nagapur\ldots '' David trailed off gravely, shaking his head, then seemed to recall himself with a start. ``My apologies. I forget these names are meaningless to you.''

That didn't sound like an accusation or a dig at their unlikely origins. It sounded like the marquis believed, finally, that they were exactly who they said they were, and only the fact that they didn't really have time was keeping the man from deluging them with questions. That was definitely going to make Riku's job easier\ldots it just wasn't his decision alone to make.

He glanced a question at Zack, not wanting to commit the SOLDIERs to risking their hearts for strangers, only to receive a ready nod in return, Zack's ears set at a jaunty angle as good as one of his usual grins.

``Looks like we're up for a geography lesson,'' Riku said as he turned back to the marquis, smiling wryly at the curious look they were given. ``When do we leave?''

``The sooner the better, I fear,'' David replied, glancing past them at the battlefield and readying himself to rejoin the fray. ``By all reports, this was only a fraction of their main force.''

``Lovely,'' Riku sighed, though he wasn't really surprised. He'd been pulled here pretty emphatically, after all; there had to have been a reason. ``Let's get this over with, then.''

He just hoped they'd catch a break on the next world, because if they kept running into Heartless like this, he'd have to start wondering if something wasn't going on, the kind of 'something' that'd have him headed right back out again the moment he reached home\textemdash and reinforcements.


\scenechange


Zack would say this for the Athlumian army: even in the face of Heartless, they were organized. They'd barely taken down the last of the stragglers before there were resupply chains being organized, the dead and wounded gathered up to make the slow trip back to the city while the rest of them carried on. Having been though it before on their adopted world, when he caught one of the captains looking furiously around for soldiers who neither reported for duty nor fetched up in the casualty train, he took the man aside before Riku had a chance to notice and quietly explained the situation.

Desertion happened, but when there were Heartless involved, it was better odds that there just wouldn't be a body to find.

``Oh man,'' Hall was saying as Zack rejoined the others, leaving the shaken captain to pass the word along. ``They had me worried with that 'no magic' thing. Who broke the universal translator, huh?''

``Yeah,'' Zack interrupted, looking Hall over intently, ``about that. How was it working for you?''

``Huh? It worked fine,'' Hall said with a shrug, looking lost. ``I just did what I always do. Why?''

``It's Hall,'' Riku said with a long-suffering sigh, echoing Zack's explanation from before.

Now Hall looked nervous, eyes flicking around the ring of consternated stares that had surrounded him. ``Uh\ldots guys? What?''

``I'm guessing that's what they meant when they were talking about Mystic Arts,'' Zack informed the others with a shrug. ``Apparently we're supposed to be channeling our\textemdash er, magic\textemdash through our weapons.''

Hall looked like he was on the verge of asking why when Giese shook his head with a grimace. ``Wait\ldots but wouldn't that still be magic?''

``Not exactly.''

Everybody turned as David came over to join them, both sides trading curious stares. The marquis didn't seem bothered by the attention\textemdash he wouldn't be, Zack supposed\textemdash looking at them with new eyes, not half as wary as before. He hadn't brought any of his generals with him this time, and that had to be a good sign.

He was in pretty good shape for a noble, Zack would say that for him. Despite the fact that he'd been hacking away at Heartless less than an hour ago, the guy looked almost as fresh as he had sitting pretty on a throne, and that was something Zack could respect wherever he found it. When the marquis got down to explanations, he didn't even sound out of breath.

``Long ago,'' David offered at their expectant looks, ``our ancestors practiced what I suppose you would think of as true magick. It was too powerful, though, too hard to contain\textemdash they nearly destroyed our world before it was decided that it was too dangerous to use. We turned to the Mystic Arts after that.''

``The weapon thing,'' Riku translated with a frown.

``Exactly. Focusing power through an object dulls its potency, but it also keeps that power in check,'' David said philosophically, his shrug as resigned as his smile. ``Of course, the knowledge of how to use magick\textemdash perhaps even the ability\textemdash has long been lost, so I suppose the point is moot.''

``Huh,'' Zack said, determinedly not looking at Hall. ``And if someone did happen to have that knack?''

``Then I suppose he'd be the first sorcerer in a thousand years.''

``Sounds dangerous,'' Zack offered, watching the marquis closely.

``Perhaps,'' David agreed with a faint little smile, only to turn to Riku, not Hall. ``But I'm more interested in what you did\textemdash the wall of darkness. How did you\ldots ?''

``That?'' Riku asked, looking startled himself, though maybe only because David didn't seem the least bit concerned about the element involved. ``Yeah, that surprised me too. I didn't think I'd put so much into it,'' Riku explained, hunching one shoulder sheepishly. ``Uh\ldots actually, I didn't know I had that much to put into it. Usually it's a lot less impressive.''

``Is it something you could teach?''

``I\ldots have no idea,'' Riku admitted, nonplused. ``Most of what I know about magic I just\ldots picked up on the way. I don't even really know how it works; no one actually taught me.''

It was long habit that kept Zack's eyes from narrowing at that little tidbit, but it was hard work that kept his ears from flattening down to his skull. Not that he was particularly surprised that Riku was smart enough to learn from what he saw. It was mostly that startled look, like the idea that someone should have taught him had never even occurred, that made Zack want to start knocking heads together.

``I see,'' David began, clearly intrigued. ``Well\textemdash ''

``Lord David,'' a woman's voice interrupted, and Zack glanced over to find General Honeywell giving an apologetic salute, fist to heart. ``My apologies, but we're ready to move.''

``Thank you, Emmy,'' David replied, turning back to Riku with a rueful smile. ``If you'll excuse me\textemdash ''

``Oh, hey,'' Riku protested with a start, reaching into his front pocket and\textemdash pulling out a knife?

Zack stared. Never mind that he hadn't thought Riku was that crazy\textemdash how had that even fit?

``Almost forgot,'' Riku said, holding out the blade, hilt-first. ``Thanks for the loan, by the way\textemdash and the demonstration.''

``Keep it,'' David replied with a smile, holding up his hand and shaking his head. ``I still can't believe you went into battle unarmed.''

``Uh\ldots I'm not exactly used to thinking of it as being unarmed,'' Riku said uncomfortably, though his little half-smirk was aimed at no one but himself. ``Still\textemdash thanks again.''

``My pleasure,'' David replied, leaving with a friendly nod as he followed his general back to the front ranks.

``You know,'' Hall mused aloud, eyeing Riku with a cocked head and a preoccupied smile, ``you do pack quite a punch, mini-Boss\ldots but I wonder if part of it isn't just this world.''

``How's that?'' Riku asked, nothing but keen interest in the quirk of his brows, his listening stance.

``Well, think about it. They couldn't use magic without dimming it down because it was so unstable. And then, like Pagus said\textemdash maybe they had those Remnant things after that to channel it for them\textemdash same thing. Whatever it is that actually fuels magic,'' Hall offered, grinning hugely as he warmed to his subject, ``maybe there's just more of it here. It's like\ldots imagine being on a world with a higher oxygen content and starting a fire. See what I mean?''

Clapping a huge hand on Hall's shoulder in the uneasy silence that followed, Titus rumbled, ``Never stop scaring us, Holly.''

Hall just laughed. ``Aw, c'mon\ldots what?''

``So,'' Stiegler said, shaking his head pityingly and ignoring Hall entirely. ``Weapons, huh?''

Having a pretty good idea where the Sarge was going with that, Zack grinned. ``Yeah, go on. Knock yourself out.''

Riku looked at him curiously for that, but Zack didn't explain and the orders to move out came soon after.

There was a marked difference in this march and the one previous, in that this time there wasn't anyone keeping watch over them, however polite the guard had been. Not that Pagus ignored them now that his lord was certain of them; the little guy stopped by now and then to ask how they were getting on, and even the marquis looked like he'd rather be marching alongside them, all the better to pick their brains, if he could just find five minutes to spare.

With the patent approval of the marquis and his generals to recommend them, they didn't worry too much about staying in strict formation. In fact, when Stiegler disappeared and Hall wandered off with Pagus to go break a few brains amongst the local mages, and Titus struck up a conversation with the exuberant General Blocter, no one gave them a second look. Well\textemdash not more than a second look. They were pretty high up there on the visibility scale, after all.

As for Zack, he stuck close by Riku's side, easily keeping pace with his longer legs. Energy unflagging despite all the magic he'd been burning earlier, Riku marched along with his head up and eyes open, curious about everything around him but not going out of his way to forge new connections like Zack had seen him do before. He hoped that meant they were already on the right track, trusting Riku's instincts to steer them the right way.

It wasn't lost on him that Riku was the center of a lot of attention, though, and somehow he didn't think it was just the obvious. They hadn't been trying to hide what they could do in that fight, any of them, and that was without figuring in the Keyblade, the first Remnant these people would have seen since the others vanished. Not that the Keyblade was actually a Remnant. And not that the locals knew that, most of them.

Most of the soldiers around them weren't looking at Zack, and they mostly weren't the wrong sort of looks\textemdash curious about the new sovani in their midst, not sizing him up as a potential obstacle or wondering what sort of meat shield he'd be. All the same, some of the sidelong glances thrown Riku's way put his hackles up, just a little. The hope and confusion, even the nervousness and wistful speculation\textemdash those just made sense, and though he filed them away in the back of his mind, they mostly didn't stand out. It was how avid some of those stares were, like they'd be all too happy to take the presence of a Remnant as some sort of sign\textemdash those were the ones that worried him, and he filed those looks away too, along with the faces behind them. Just in case. And if he made sure that Riku was never alone while they were here, well, he was just a cautious kind of guy.

He didn't even have to ask to know the others had had the same thought. All he had to do was watch the casual way Ochs and Giese pulled ahead of them, Schumann and Haxby flanking them to either side, a watchful circle pulling tight around their center.

The road they'd been following had begun to rise again not long after they'd begun their march, and Zack figured they'd reach the range of low mountains he could see ahead sometime before nightfall unless the road veered away again. There didn't seem to be many settlements out this way, and what wildlife he spotted was mostly on the wing\textemdash and he certainly hoped his eyes were playing tricks on him, or else the early birds in these parts were probably after the whole fisherman, not just the worm. He nudged Riku anyway when he caught sight of a pack of skull-faced hounds peering down at them from a nearby hill, Riku following his line of sight just before the beasts went scattering off as the army drew closer.

``Not much like home, huh?''

It wasn't until Riku grinned up at him that Zack realized he'd assumed 'home' would mean Gaia to the both of them.

``No, not much. It's interesting, though,'' Riku said with a shrug. ``I don't usually get much time to sight-see when I'm traveling. It's a nice change.''

``Except for the whole Heartless invasion thing, of course.''

``Actually? That's the part that makes me feel right at home.''

``Hm.'' He let that pass in silence for a mile or so before glancing sidelong again. ``So\ldots self-taught, huh? And here I thought you'd learned those moves from the master.''

``If you mean Sephiroth,'' Riku said with a snort, ``not exactly. I mean\ldots some of the actual spells, sure, but\ldots when it comes to the darkness, I don't think anyone exactly taught him, either. I think a lot of what we do is just\ldots instinctive. Of course, some things you are going to pick up really fast when someone like Seph is coming at you with a gigantically long sword.''

Zack wasn't the only one who laughed at that, having been in exactly that position before himself. Pretty much anyone who'd ever found themselves sparring with Sephiroth would say the same.

He would have let it go if Riku hadn't sobered at some memory or thought.

``What?'' he asked, his ears tilting off in uncertain directions as he cocked his head. It brought a ghost of Riku's smile back, at least. He supposed he could put up with the ear thing for that, if nothing else.

``Nothing. It's just\ldots a lot of what I do is stuff the fake Ansem knew, and anything he used, I guess I just\ldots remembered.''

Seeing Riku look so grim had him reaching out without thinking, settling his hand on Riku's shoulder. It made Riku glance up at him immediately, faint grimace set deliberately aside for a cocky grin, but Zack ignored that in favor of noticing that Riku wasn't sidling away, that some of the tension actually relaxed out of the muscles under his hand. So they were still good, then, in spite of everything.

``Like I said,'' Riku tried to bullshit him, shrugging the other shoulder with his chin held high. ``No big deal. All I need to do now is get possessed by something holy, and I'll be in pretty good shape.''

``Yeah, not on my watch,'' Zack promised, briefly tightening his grip on Riku's shoulder before letting him go. ``So don't go getting any ideas. You want strange new powers of Light, you'll have to get them the old-fashioned way like everybody else.''

``Look pitiful at Aeris until she cracks and gives in?'' Riku hazarded, smiling still.

``What? You know a faster way?'' Zack asked, just to hear Riku laugh, and somehow it didn't quite hurt to grin along.

It was hard to judge as the mountains started closing in around them, but Zack thought they were still an hour away from sundown when they called a halt for the night, smack in the middle of the long valley cutting through the Ivory Peaks. In no time at all, a proper camp had sprung up from nowhere, cookfires and traveling forgefires burning, wary sentries pacing out a disciplined circuit he took at first for a precaution against the Heartless until he got a good look at what was circling out there, hoping to make a meal of a straggler or three. The wyverns were one thing; those so-called demons looked like they might just live up to the name.

One by one, the guys who'd melted into the ranks came back from wherever they'd been, Hall first, with General Pagus in tow, the two of them still talking shop like a pair of old tenured professors.

``So it's the expression of your spells that has changed,'' the qsiti was thinking aloud, staring up at Hall in unabashed fascination, ``not the spells themselves.''

``It's the same thing with the Keyblade, I think,'' Hall said with an earnest nod, turning at once to Riku. ``Right?''

Zack had been keeping a pretty close watch, but he still couldn't make out what was so fascinating about a blank rockface that Riku had to shake himself to join the conversation.

``Uh\ldots what?''

``Hm,'' Pagus murmured, peering up at Riku curiously. ``Is there something the matter?''

``I\ldots not exactly,'' Riku said, shooting a distracted glance back at the chunk of rock he'd been staring at. The whole valley was riddled with low buttes and hills that sheared off without warning, but the one Riku had found had one flat side so smooth it almost looked polished. A pair of tall columns stood to either side of the rock, but there was no clue to their purpose, not even a hollow in the grass to show that anything else had ever stood here. ``This place just feels\ldots different.''

``Interesting,'' Pagus mused, a spark of excitement lighting his eyes. ``It appears you've found the former home of the Liafort\textemdash a Remnant once bound by the Gilles-Barre family.''

``Here?'' Riku asked, startled, looking around like Zack to spot where the Remnant might have stood.

``There,'' Pagus said with a quirk of a smile, nodding at the bare rock that had caught Riku's attention before. ``While it stood, the Liafort appeared as a shining work of art, inspiring all who saw it. Unfortunately, inspiration wasn't enough to counter certain changes in the political climate, and after these lands were annexed by Celapaleis, the family holdings fell into disrepair. Still\ldots that you can sense anything here is\ldots most unexpected.''

``Huh.'' Turning back to the rock wall with a frown, Riku stilled himself, breathed deep and held out his hand, and this time the Keyblade settled right into his palm, the two halves snapping together with a roiling flicker of shadows.

Zack was aware of the silence that rippled out around them, but while his ears were keeping track of every movement in any direction, his eyes were glued to Riku as the Keyblade was lifted, aimed.

Half expecting to see a Keyhole manifest or for a narrow beam of shadowlight to burst from the Keyblade on cue, he realized he'd been holding his breath only when he had to let it out, all at once. It was almost disappointing to see Riku shake his head, lowering his arm and releasing the Keyblade with a sigh of his own.

``It's not here,'' Riku said, turning back with an apologetic grimace. ``The door to wherever the Remnants are,'' he added for Pagus' benefit, though the thoughtful crease in his brows remained. ``I wouldn't say there's nothing, though. Just\ldots a lot of memories, I think. Makes me wish Kairi was here; she could probably do something with that.''

``It was worth a try,'' Pagus agreed with a sigh. ``I suppose we'll simply have to keep looking.''

``Count on it,'' Riku said with a firm nod, pretending not to notice as the soldiers around them went reluctantly back to their routines now that the show was over.

Stiegler was the last to find his way back, and if the hint of swagger in his stride wasn't enough, the Sarge's anticipatory little grin as he tossed something dark and compact at Riku would have clued Zack in that the man was up to something. ``Here you go,'' Stiegler said as Riku made a startled grab, examining what he'd caught with a puzzled look.

``Gloves?''

``Go on, try 'em on,'' Stiegler urged, grin stretching wide. ``I modeled them on Titus'.''

Surprised realization dawning instantly, Riku tugged on the black leather gloves: tough, flexible, their knuckles reinforced with a metal that gleamed with a bluish sheen as Riku flexed his fingers. Gathering himself visibly, he held out one hand, focused, and just that easily was surrounded by the shifting gloom of a Dark Shield, small enough to only cover a few people instead of that massive wall of black from before.

``Thought that might work,'' Stiegler said smugly as Riku let the shield drop. ``That and I didn't want to piss off the sword you've already got by giving it any competition.''

``Thank you,'' Riku said, so devoutly it was clear he didn't just mean for the gloves.

Stiegler laughed, waving Riku off. ``Yeah, yeah.''

``Had much practice fighting unarmed?'' Titus piped up, so nonchalant it had grins popping up on every side.

``I wouldn't embarrass myself totally in a bar fight,'' Riku said warily, clearly aware that something was up, ``but that's about all I can say.''

With a long, slow smile made that much more intimidating coming from such a height, Titus asked, ``Think you'd be up for learning more?''

It was hard not to do a startled double-take when Riku just\ldots lit up, eager and willing, and never mind that Titus had been three times Riku's size before the big guy grew a tail.

``Try me.''

Titus rumbled a low chuckle, but it was abundantly clear he was as pleased as could be.

They cleared a space, Titus pointing out the differences in balance as they loosened up, Riku bright-eyed and intent before they even got started. It was probably that look of undisguised, undivided attention that had Titus starting out slow, running Riku through a few basic moves instead of coming in hard and fast and crushing whatever cockiness might be there so they could get down to business. That was one difference between Riku and the average SOLDIER trainee; another was that he didn't chafe at the baby lessons, even though it was clear he was better than he'd claimed\textemdash which figured. Difference number three.

Titus in action was always good for a startled double-take, but it was even more surprising than ever to see that much mass moving with that much speed and grace. Though his balance couldn't be quite what he was used to, it seemed the big guy had already come to an accommodation with it, each lash of his tail and flare of its fins as confident and economical as if he'd been born in that oversized body. What should have looked ponderous was made predatory instead, and that faint little grin wasn't helping.

``Not many would engage a yama at close quarters like that.''

He'd heard someone come up on his right, but he'd been too preoccupied to greet whoever it was. At the sound of that deep voice with its hint of a growl, Zack glanced over to find the sovani general watching the practice match with interest.

``I believe it,'' he said, grinning a little as he glanced back at the sparring pair. ``But it takes guts at any distance when you're going up against Titus.''

``Hn. He seems quite skilled.''

``Oh, he is. Any of us who are worth anything at hand-to-hand have the big guy to thank,'' Zack agreed, watching with inexplicable pride as Riku dodged and blocked, meeting fists as big as his head without flinching.

Something made Torgal look over at him just then, ears pricking up stiffly in surprise, but when Zack swiveled a curious ear of his own in the other sovani's direction, Torgal shook his head brusquely and glanced away.

Zack was almost too distracted by the fact that he'd just had his first entire conversation with his ears to wonder what all that had been about.

Torgal didn't look inclined to elaborate, and it didn't seem like the best time to ask, considering that they were standing on the edge of a gathering crowd. General Blocter seemed especially enthused by Titus' mad skills, but Zack caught other yama looking on appreciatively, a few broad tails flicking in sympathy as they soaked up some of Titus' moves.

They were well into it now, Riku holding his own though Titus wasn't trying to outclass him, but an audience like the one they'd drawn couldn't be ignored forever. Zack almost expected Riku to freeze up or ice over as his eyes made a fast circuit of the crowd; what he wasn't expecting was for Riku to fall back a pace, grinning up at Titus and asking with a quirked brow if the big guy wanted to kick it up a notch.

He didn't know why that surprised him. It shouldn't have; Riku wasn't Cloud, didn't have the same kind of doubts in his own abilities, and he wasn't Sephiroth either, wary of the limelight and half-desperate to escape it. If anything, in this, Riku reminded him a little of himself: confident in his strength, not afraid to fall flat on his face and willing to learn from it after. Before the fiasco that had been Riku's introduction to the greater cosmos, he'd probably come off as just about insufferably cocky\textemdash Zack would bet on it, because he had too.

Now he could only grin as he watched Riku yelp and swiftly backpedal as Titus put some real speed into his swing. That had the crowd laughing, Blocter punching air\textemdash and Riku laughing right along with them, somehow ducking and sidling out of Titus' way every time, as fearless as he'd started out. But that was just it: fighting wasn't ever going to be Riku's problem. Give him a clear-cut enemy and something to protect, and he'd be the first to pick up a sword\textemdash or a Keyblade.

``You do realize,'' Torgal murmured over the cheers of the crowd, ``whatever its origins, what the boy carries is currently the sole Remnant in the world.''

Right. Because he'd been in danger of thinking the Heartless were their only problem.

``Yeah. We know. We're keeping an eye on things. I wouldn't worry too much, though,'' he added without looking at Torgal. ``You can't steal a Keyblade, and you wouldn't even want to try to steal that Keyblade.''

It was Torgal's continuing silence that made him realize there was another way of looking at all this, that the only reason he wasn't seeing it himself was because he'd known everything he needed to know about Riku from the company he kept.

``And if you think he's going to use it to set himself up as high king or something,'' he added, turning to meet shuttered gold eyes, ``I wouldn't worry about that, either. Riku's not much for politics, and we've got folks waiting for us back home. We weren't planning on overstaying our welcome.''

``Yet you must realize you would be welcome indeed,'' Torgal replied, carefully noncommittal.

``Not as welcome as we'll be once we get where we're going,'' Zack said, keeping his wistfulness in check. Even if it wouldn't be the homecoming he'd once hoped for, finally being home would be enough.

A particularly loud whoop from Blocter distracted him from the morose thoughts he was trying to shake, and he looked up to find that training had essentially devolved into roughhousing while he wasn't looking. One moment Riku was looking helplessly over his shoulder as if checking his line of escape, and in the next he was making a break for it\textemdash and though Zack had missed the look that must have passed between them, he didn't miss Stiegler leaning down just as Riku reached him, sticking out a hand that Riku stepped up into without missing a beat, ready for it when Stiegler came up from his crouch and launched him right into the air. Just like that, Riku was flying, twisting in midair like he'd grown wings himself, in a breath-stealing arc that landed him squarely astride Titus' massive shoulders.

Whereupon he promptly leaned forward and clapped both hands over Titus' eyes, holding on tight.

``What?'' Riku yelled back as the guys started laughing, pulling off a tone of wounded innocence not at all. ``I'm still using my hands, aren't I? What more do you want?''

Zack laughed too as Titus heaved a pitying sigh, shaking his head but refraining from plucking Riku down from there the way they all knew he could. ``It's always the little guys who think flying will help.''

``I will pay you to say that to Cloud. Or Sephiroth. Or both.''

Though Torgal was watching Zack, not the antics of the others, the set of the sovani's ears was amused. ``I understand,'' he said, more relaxed than before. ``I'm sure you must be missed.'' Then his look turned speculative. ``So\ldots there are sovani on other worlds?''

``Oh, man. No comment,'' Zack laughed uneasily, ruffling a hand through his hair. Fur. Mane. Gaia.

He understood what Riku had been muttering about earlier, though; First Contact really was a bitch.

Things quieted down after night fell, though listening to what was roaming around beyond the glow of the watchfires, Zack guessed 'quiet' was a relative term, was more than glad of the extra sentries pacing out their steady beats. The fire-shine made it hard to see the stars, but the few he could pick out were unfamiliar, as new as the skies over Leá Monde had been, and every other world they'd been to besides. He wondered at the distances that implied, that there were no fixed points to steer by, not one dim star above that even remotely resembled home.

Rolling over onto his side on his borrowed bedroll, he stared at the young face lying composed in sleep an arm's length away and wondered what Riku was navigating by, what the compass in the heart of a Keyblade master must feel like to let Riku pick their direction with such certainty out there in the dark. There was never any hesitation, and whatever the source of that pull, it was clearly something Riku trusted in without question. Riku would probably explain if he asked, if it was something that could be explained. It was just a little embarrassing to realize he didn't actually mind not knowing.

However Riku planned on getting them home, Zack trusted him for it.

Squirming a little to find a comfortable spot\textemdash and who knew having a second pair of arms would make sleeping rough that much more of an adventure?\textemdash Zack rolled back over onto his back and sighed. He hadn't needed as much sleep after making First Class, it was true, but a half day's march on top of a battle was something even he liked to wind down from, and this weird new body was just\textemdash 

``You okay?''

Glancing right again he found aqua eyes turned his way, paled-out by firelight but as alert as if they'd never been asleep.

Damn.

``Sorry. Didn't mean to keep you up\textemdash you should've said something earlier.''

``Don't worry about it,'' Riku said, hunching a shoulder. ``I couldn't sleep either.''

He hadn't expected that, though maybe he should have. It was just that Riku had looked so comfortable, like he didn't have a care in the world. ``Too many people, or not enough walls?''

``Too many Heartless,'' Riku muttered, mouth twisting wryly at his start. ``I don't know\ldots it may just be me, but\ldots this world didn't seem to be in this much danger when we first got here, and now we've taken on one army and we're on our way to meet a second. It just seems like things are moving a little fast\ldots or maybe the world itself didn't realize how bad things are. That kind of worries me too.''

``Think it has anything to do with the missing Remnants?''

``Maybe,'' Riku said thoughtfully, frowning as he puzzled that over. ``If it's used to having the Remnants as its first line of defense\ldots maybe it doesn't remember how to fight off an attack without them. It explains why it wanted us here so badly, anyway.''

``I think you mean 'you,''' Zack said with a fond snort.

``With this many Heartless? I mean 'us.'''

He managed to keep his laughter quiet, mostly breath, but he couldn't quite stifle the irritated growl as he tried automatically to roll over again and got a rock in the shoulder\textemdash the one that shouldn't be there.

``Can't sleep?'' Riku asked in knowing commiseration as he dug huffily around under his bedroll until the ground was smooth again.

Reminded that Riku had been in his shoes more than once, Zack heaved a sigh. ``Let's just say nothing's convinced me yet that these are an evolutionary gain,'' he grumbled, flailing his lower pair of arms a little before folding them again. At least that kept them out of the way.

The corners of Riku's mouth turned down as he watched, like there was laughter trapped behind that careful not-smile just dying to get out, but Riku took pity on him eventually, settling on a sympathetic smirk instead of a grin. ``Snake bits are worse,'' Riku offered sheepishly, nearly mumbling the words. ``I actually tied myself in a knot once.''

``You did not.''

``Oh, yeah. I totally did. Okay, I was distracted at the time, but\ldots ''

``Sephiroth?''

Riku's half-embarrassed grin was answer enough, and Zack was\ldots really trying hard not to picture that, which probably qualified him for some kind of sainthood. No doubt something that embodied self-denial and hopeless idiocy in equal measure, though he was pretty sure his particular brand of martyrdom wasn't going to be immortalized in glass in any church anywhere ever.

Well, okay. Maybe in the Chapel of Freya.

He also wasn't going to think too hard about the change in Riku's scent\textemdash something new, not\ldots anything he was already used to blocking out. Gaia, let him not be able to sniff out pheromones now. He wasn't sure he could take another boost in sensitivity.

``Yeah, well\ldots it helps if you can ground your senses. In a new body, I mean,'' Riku explained, hunching a shoulder. ``Once you get comfortable, you mostly forget the differences.''

``Comfortable, huh?'' Zack asked wryly, lying perfectly still in the closest thing to comfortable he'd yet found. Which wasn't all that close.

When Riku reached across the space between them, Zack didn't think anything of it until long, clever fingers threaded into his hair. He didn't quite start, staring back into a perfectly composed face and eyes that were one big question: Does this help, then? Uncertain, ready to spook, but above all friendly.

Sighing out a breath he hadn't been aware of holding, Zack let his eyes droop half-closed, turning his head into the skritching and rumbling a scratchy purr under his breath. It wasn't even the magic fingers that had him sounding like a drowsy housecat, although that good spot right at the base of his ears came close. It was suspecting that if Riku was this comfortable in the face of weird new bodies and crazy bartenders who liked to go around implying things, it must be because it was Zack he saw, not the stranger whose skin he was wearing\textemdash and that was more than Zack himself could say with any certainty at the moment. As long as one of them was sure of him, he guessed he could deal.

On the other hand, skritches this good probably ought to come with warning labels, because damned if he wasn't seeing things\textemdash another Riku, ghostly, sitting up on the other side of the real Riku and smirking in Zack's direction\textemdash right before the gentle massaging of one ear put him out like a light.


\scenechange


Torgal still wasn't certain he believed the strangers' tales\textemdash it wasn't sovani nature to be too trusting\textemdash but his lord believed, and there had been nothing duplicitous about the black sovani's scent. Nor could he deny that they'd been useful\textemdash courageous fighters, all of them, though their strength was surprising. Even the mitra amongst them had the strength of yama, and their yama was like nothing he'd ever seen. There had been times that morning that he wished Miss Irina had carried her point and joined them; he would have been very interested to know whether the Keyblade Remnant was truly the only one in their party, whether the unsettling glow in the soldiers' eyes had a very simple explanation.

The Third Committee had performed experiments like that; he'd seen the results, had fought against and alongside them, had nothing but respect for the abilities of those few he knew personally. He was simply\ldots not entirely easy with the idea that the same experiments might be happening elsewhere, not after seeing the damage it had done.

Admittedly, he had no proof that anyone who'd been fused to a Remnant had been anything like sane before the process\textemdash 

``Can't sleep?''

He started at the voice but couldn't be entirely chagrined that he'd allowed the approach unawares. He'd known the sound of those footsteps when they'd still been a wobbly, uncoordinated charge across a nursery floor, the determination that had won Athlum's independence wholly apparent even then.

``Thinking of our guests,'' he offered as he turned, inclining his head in the place of a more formal salute.

``You spoke with them earlier?'' David asked, though it was more assumption than question.

``With the sovani, yes. Zack. He seemed\ldots remarkably honest.''

``I've noticed this about them,'' David agreed wryly, smile quirking at the edges. ``It's interesting that he uses a family name\textemdash I didn't think you did that.''

``There are not so many sovani left in this world that it's difficult to distinguish between us,'' Torgal reminded, and though he'd tried for a humorous tone, David sobered regardless.

``No. I suppose not.''

They'd had this conversation before, that force of numbers meant little to a race as long-lived as sovani. They could have bred like mitra if they chose, overwhelmed the other races and reestablished their rule with ease; it was just that most sovani preferred to have nothing to do with outsiders, would rather ignore them than govern them.

``Do you believe them?'' David asked suddenly, catching Torgal's eyes with a level stare that gave away nothing of his own opinion, asking for Torgal's honest thoughts.

``I understand why you believe them,'' Torgal replied after a moment, ``and I believe that they believe their story,'' he added, which had his lord's brows arching in amusement. ``All the same, I prefer to withhold judgment without proof to their claims.''

``One of us probably ought to,'' David replied, letting out a sigh as relieved as it was wistful. ``I fear I'm not as unbiased in this matter as I should be.''

He hardly needed to explain himself; Torgal understood. ``If it helps, Zack assured me his lord possesses an astonishing lack of ambition,'' Torgal offered dryly, watching David's faint smile stretch into an honest grin.

``Now that I do believe,'' David said, which Torgal found surprising. ``Have you ever met anyone less impressed with rank?''

``One,'' Torgal said.

David smiled. ``Exactly.''

It wasn't lack of trust that made him swing close to their visitors' fire when he took one last turn around the camp, or not lack of trust entirely. He could believe in other worlds if he had to, in Remnants-that-weren't and in sovani who were as strange to him as those glowing-eyed mitra had to be to Lord David, however well the marquis hid it. It was something more foolish\textemdash the peppery-sharp scent of Zack's pride whenever conversation turned to his lord, how Zack shadowed the boy, deferred to him without rancor, asserted himself without hesitation\textemdash and was listened to, the balance between them never overturned. David might laugh to know Torgal saw a little of himself in Zack; Torgal had never been so unguardedly exuberant in his life, even as a kit.

Watching the two of them now from the edge of the shadows, he wondered what David would think if he claimed to see another in the silver head tucked trustingly against black, Zack having escaped his bedroll to curl up in a ridiculously-tight ball at Riku's side. That uncompromising bluntness, the bold willingness to fight, even the silver of the boy's hair\textemdash all too familiar, and all far too deeply missed.

Foolishness on top of foolishness, that; he knew how short mitra lives were, even those that didn't command armies. He had had decades to prepare.

Emma might have accepted that he would someday miss her, but she would have hated to be mourned.

She would also have teased her young likeness mercilessly, so it was perhaps fortunate for all concerned that their guests had only her daughter to deal with. Emma would have liked the boy, though, and for that reason alone Torgal found himself holding his tongue, not counseling the painfully young sovani currently purring in his sleep that mitra were better left alone.

If this Riku were anything like Emma in the slightest, no amount of warning could ever prepare one for the inevitable.


\scenechange


Jolted out of sleep to the sound of trumpets and the smell of coffee, Riku sat up so fast his head spun, every muscle coiling taut as he searched the controlled chaos of the camp for enemies, the Keyblade a heavy throb of willingness behind his ribs. ``Easy, there,'' someone said, warmly amused, and he blinked stupidly at the hand in front of his face until he realized it was connected to a scratched but serviceable tin mug, a mug that smelled of heaven.

``You're a godsend,'' Riku groaned, rational thought coming back online as startlement ebbed.

``Me or the coffee?'' Zack teased.

``Both,'' Riku paused just long enough to say before diving in.

It was clear he still wasn't really awake, though, because when the stupid thought hit him and made him frown, it actually took a moment before he realized Zack's smile had dimmed uneasily as soon as he started to scowl.

``What?'' Zack asked.

Riku shrugged. ``Godsend.''

``Huh?''

``Just wondering who the god of coffee is,'' he explained, shoulders hunching a little as he hid behind his mug. It wasn't that he couldn't fight within moments of waking. It was just that he shouldn't be allowed to think. ``Probably Hermes,'' he heard himself say after another sip.

Zack shook his head, but his smile had powered back up again, double-strength. ``You just keep drinking, mini-Boss. We'll cut you off when you start making sense.''

Snorting, Riku aimed a friendly kick at Zack's nearest boot, smirking when the man danced aside. At least he looked more relaxed today, the cheery bounce back in his stride as he wandered off to poke and prod everybody else awake, or at least into a better humor when it came to starting the day off with a dawn march. Apparently following instinct last night had been the right thing to do.

Reminded abruptly that Zack wasn't the only one he ought to be worrying about, he looked around for Titus and found the man lurking not far off, watching Riku from over the rim of his own yama-sized mug. He didn't look unduly traumatized\textemdash or Riku didn't think so, anyway\textemdash but he clearly had something on his mind. The question was what.

``Hey,'' Riku called, a tiny worm of guilt twisting in his stomach for leaving the man to his own devices. Traveling the worlds could be unsettling even when you weren't getting a full-body makeover. If Zack had been having trouble getting comfortable with his arms, how was Titus managing with that tail? ``Guess I should've asked before, but\ldots how are you holding up?''

``With the yama thing? It's fine,'' Titus said with a dismissive shrug.

``Uh-huh,'' Riku said skeptically.

Titus smiled. ``You're forgetting I was already a giant.''

``But not one with a tail.''

``Yeah, okay, that's new,'' Titus allowed with a chuckle. ``Thing is, when you're this big, you tend to second-guess your outsides anyway\textemdash seeing as the world's designed for you stripped-down models,'' he added, his own smirk widening at Riku's grin. ``That and folks look at you differently when they have to look this high up.''

That sobered him quickly enough. He'd only ever been glad of Titus' height and mass, grateful to have that kind of strength on their side. It hadn't occurred to him to really wonder what the average guy on the street might think, that the man might be intimidating to more than just the Heartless.

``Zack's a bit different,'' Titus said slowly, and for once Riku couldn't hear the slightest trace of a joke in that. ``He's the type that's always comfortable in his own skin, because he's always known exactly who he is. I can't say I blame him if having his outsides changed is messing with his idea of what's inside,'' Titus rumbled, tapping the side of his own skull with one thick, blunt finger. ``Just\ldots try to cut him some slack, huh? He's usually got his head screwed on better than this.''

Riku frowned up at Titus for a moment then shook his head. ``Uh\ldots are we pretending you guys didn't hear me telling Zack about the whole Fake Ansem thing?'' he asked dubiously. ``Because believe me, I am the last person who'd give anybody crap for being weirded out over being in the wrong body. I probably know every trick there is for making that feel normal, though, so\ldots it's fine. It's not like we're going to be here forever. But thanks for the reminder,'' he added, hunching an awkward shoulder at Titus' puzzled look. ``The thing is, when I look at you guys, I still see Zack and Titus\textemdash I forget that maybe you don't.''

He didn't know quite what to make of the long, silent stare of growing amusement Titus was treating him to, and that made him nervous. He did get that he wasn't known across twenty worlds for his tact; he just couldn't figure out what he'd said to stick his foot in it this time.

``Right,'' Titus said after a moment, knocking back the rest of his coffee like he actually thought it would hide that grin. ``Anyway, don't worry about me. You just go right on mother-chocoboing Zack. Gaia knows it's time someone did.''

He knew he was gaping like an idiot, but getting control over his jaw again in no way implied he had control over his mouth. ``I\textemdash huh? I'm not\textemdash it's not\textemdash what?''

Titus laughed at him. That wasn't even a surprise. Riku would have laughed too.

``Come on,'' the big guy said over Riku's sputtering. ``Let's get something to eat and get ready to move.''

``Yeah, whatever,'' Riku muttered, heaving himself to his feet.

Probably all SOLDIERs were crazy. It'd explain a lot. Like how Titus had managed to miss who exactly was wearing the feathers around here.

Mother chocobo. Yeah, right.


\scenechange


They made good time through the Ivory Peaks, following the line of the valley and a nearly-straight road tramped smooth by generations of travelers and the occasional army. Though he didn't have much experience with infantry himself, Zack couldn't fault the stamina of the Athlumian troops: anyone willing to march from one battle to the next\textemdash in a full kit, no less\textemdash got his respect, hands down. The funny thing was, it'd been so long since he'd been on anything with an engine, that was actually starting to feel normal.

Though they were all keeping a wary eye out for Heartless, the one bit of real excitement they had that morning was when a wounded demon came staggering right into their front ranks, half-blind and flailing its massive talons at anything that moved. Whatever it'd tangled with before, it was something equally big and mean; the thing's tough hide was a patchwork of gaping claw-marks and ragged, rough holes where teeth had sunk deep. A big yama mercenary led the charge to take it down, which was definitely impressive to watch. Zack was just a little more interested in knowing what had gotten hold of the beast in the first place and whether it was still around.

``That looks like the work of a wyvern,'' the marquis offered, examining the corpse afterwards. The man looked troubled, though, scanning the sky with a preoccupied frown. ``Strange. They prefer raptors; I've never seen one attack a demon before.''

It wasn't even a surprise anymore to see Riku step forward and sniff the thing, wrinkling his nose like he'd caught a whiff of something fouler than the reek of blood and animal musk. ``It smells like Heartless.''

``Heartless wyverns?'' Zack hazarded, just to make sure they were on the same page.

``Yeah. But I'm thinking these are going to be bigger than the kind we've seen before,'' Riku warned, splaying a hand over a set of deep gouges dug into the demon's haunches, the furrows as wide as the gaps between his spread fingers. ``Like\ldots about ten times as big.''

``Well, that sounds like fun.'' Only not really. Pretty much the opposite, in fact.

Glancing back and forth between them, David arched a brow and asked, ``Is there anything the Heartless won't possess?''

Riku stiffened, but when he turned back to face them, he met the marquis' eyes without flinching. ``It's not\ldots really possession,'' Riku explained, ``most of the time, anyway. They don't move in and take over; they're just the darkness that's left behind after a heart's been consumed. You can't just\ldots exorcise them, or cast them out, or whatever it is you do here\textemdash it's not that simple.''

``But they'll take wyverns as handily as mitra or yama\textemdash or Jhana\ldots correct?''

``Yeah,'' Riku said slowly, ``to a point. I mean\ldots they'll eat pretty much anything, but\ldots from all I've seen, you don't get Heartless without a certain amount of intelligence. At least it doesn't always carry over\textemdash most of them aren't nearly as smart as they are hungry.''

``And the others?''

``The stronger the heart, the stronger the Heartless. The really strong ones\ldots some of those would almost pass for human.''

David looked like he was tempted to ask about the ones that wouldn't pass, but something in Riku's expression made him stop, visibly biting back the question though his eyes were lit with curiosity. ``I see. Then it's lucky we have the Guilds with us.''

Zack twitched an ear back, wondering if it meant he'd been hanging out on the wrong worlds that his first thought was: 'Assassins or Thieves?' ``Uh\ldots Guilds?''

``Hunters and mercenaries,'' David explained with a faint smile. ``A few rare monsters are all in a day's contract for them\ldots and we currently hold every contract they would sell us.''

That explained all the guys out of uniform\textemdash and it sure beat the farmers and bakers with more patriotism than training he'd been worried they'd have to protect. ``And here I was thinking those were volunteers.''

The quirk of the marquis' mouth was friendly, but no less proud for all of that. ``They are. They're the ones who wouldn't sell.''

``Go Athlum,'' Zack said with a grin, which made David laugh, startled but not offended.

The weird part was how his vision flickered, just for a moment, like he was seeing double again. It was just a little too specific\textemdash not the whole army; just the marquis\textemdash monochrome and transparent but perfectly sharp.

Ghost David sighed, murmured: ``Rush.'' And then it was gone.

He kept the spooked uncertainty off his face with an effort, thanked countless past-midnight conversations with Sephiroth for the fact that he was good at it, good enough to fool a man who could actually read sovani expressions if David's unfailing accuracy in deciphering Zack's was anything to go by. And maybe that wasn't the best strategy he'd ever come up with\textemdash maybe he ought to be asking if seeing ghosts of the living was just some kind of sovani thing that came with the body\textemdash only he didn't think so. Not with Riku shooting him one fast, puzzled glance, there and gone, the same look he got when he smelled something just fascinating.

Two guesses what that was, and the first didn't count.

He figured Riku would corner him once they got moving again, ask what sort of magic he'd been tapping into back there and why hadn't it required some flashy moves and his sword. He waited a good five miles, in fact, before he realized Riku wasn't going to say a word, at least until Zack's constant glances in his direction earned him a puzzled smile and a patient, ``What?''

``So, uh\ldots back there,'' Zack began, only to watch as Riku's face cleared all at once.

``Oh, yeah. Sorry,'' Riku said without a hitch in his stride. ``It's just that sometimes you smell really strongly of the Light. It's interesting,'' he added with a sheepish little shrug. ``Does it bother you?''

``No\textemdash it's not that,'' he began, only to run out of words when he realized just how creepy 'I think that freaky city made me something-pathic' would sound. Still\ldots the Light, huh? That was pretty much the opposite of what he'd been expecting, and he didn't mind admitting that hearing it made a world of panic drop right off his shoulders.

He was spared having to grope for words to explain something he barely understood himself when Ochs' whistle and Stiegler's admiring curse caught their attention and redirected it towards the mouth of the valley, just ahead. Barring their way was what looked like a small private army, hundreds of troops at least, and though their weapons remained sheathed and grounded, they looked like they'd be trouble if they decided to fight. At this distance, Zack could just make out the device here and there of crossed swords bordered by silver wings, but the heraldry and the silver and grey of their armor and livery meant nothing to him. They did make quite a picture in all that gleaming scale and polished plate, but he wasn't going to bank on the color scheme making them the good guys until they were properly introduced.

Completely understandable preference for charcoals and black aside.

The commander that stepped forward from the other side was a sovani, armored nearly from head to toe, though Zack could see that his fur started out a sort of reddish-brown at his ears and faded to cream around his nose and mouth. Zack thought there might be a hint of stiffness in the sovani commander's ears, not so much unwilling as uncertain, but they relaxed as David left the protection of his men without hesitation to meet the sovani halfway.

``Caedmon,'' David greeted him warmly. ``It's good to see you.''

``And you as well,'' Caedmon replied, inclining his head in a respectful nod between equals. ``Though you would have seen us much sooner but for a regrettable delay. Athlum yet stands?'' he asked, glancing past David at the Athlumian army and seeming relieved at what he saw.

``She does,'' David replied, and there it was again: that hint of pride\textemdash in his men, his city, not himself\textemdash that had men lining up to fight for him and half the mercenaries in the city throwing in their lot for free. ``We were on our way to join the defenders at the Heroic Ramparts.''

``Of course,'' Caedmon replied with a not-half-bad attempt at a mitra smile, as if he'd expected nothing else. He sobered almost instantly, his voice grave when he said, ``You should know\ldots Nagapur has fallen.''

``What?'' David demanded over the staid commotion that spread at his back, soldiers shifting uneasily as the word was passed back through the ranks.

``None of the other scouts returned,'' Caedmon said heavily, ``so I elected to go and see for myself. By the time I arrived, there were neither enemies nor defenders to be found. Nagapur stands empty of all but ghosts.''

``Fuck,'' Riku breathed, and Zack agreed wholeheartedly. If the Heartless had already taken an entire city\textemdash 

``Then the Heroic Ramparts cannot be allowed to fall,'' David said firmly, squaring himself up just perceptibly though his spine had already been stiff and straight before.

``Agreed,'' Caedmon said with a short, sharp nod, green eyes weighing. ``With your leave, the Falcons would fight alongside Athlum. In place of vanished friends,'' he added when David seemed to hesitate.

``Then you're doubly welcome,'' David replied, offering his hand to seal the deal. ``Will you walk with me a ways?''

``It would be my pleasure,'' Caedmon said, catching the eyes of his captains and giving the order to fall in with the Athlumians.

``I wonder what all that was about,'' Hall mused aloud as they got moving again. ``I mean\textemdash Caedmon. That's the guy the bartender told us about, right?''

``Yeah,'' Zack said, though one of his ears insisted on flicking uncertainly back. ``I guess these must be the Silver Falcons. So why do I get the feeling they're not usually on such friendly terms with the marquis, there?''

``We're not on unfriendly terms with them,'' a voice piped up from somewhere around Zack's knees, and he jerked his eyes down to meet Pagus' amused smile with an embarrassed huff, purely instinctive. ``Though they have made enemies amongst the other lords, Athlum has always maintained a neutral stance where the Falcons are concerned.''

``Why's that?'' Zack asked. ``I mean, how'd they tick off the other lords in the first place? What do they do?''

``They fight,'' Pagus said mildly, ``regardless of borders or allegiance. Purportedly against injustice, though where politics are involved, one can see how opposing sides may have opposing definitions of the term. They've also been instrumental in holding back the Jhana hordes and have more than once come to the aid of towns beset by disaster.''

``Those sound like some pretty noble goals,'' Zack said, waiting to hear the catch.

``Indeed,'' Pagus replied, not disputing it, ``so long as you don't have a stake in convincing them to choose sides. Historically, the Falcons have always maintained a neutral position. By throwing in their lot with Athlum\ldots ''

``They're making trouble for your lord,'' Riku guessed, rousing himself from his own thoughts with an effort.

``Possibly,'' Pagus said cautiously. ``They are, technically, allies of\ldots an ally who all of Congress owe debts of gratitude to. The irregularity may simply be overlooked in light of that.''

Zack would have liked to ask about this mysterious ally, strongly suspecting it'd turn out to be a name they'd all heard, but Riku's quiet snort stopped him even as he drew breath.

``I wouldn't worry about it too much,'' Riku said, dry and humorless. ``If the Heartless have already taken this Nagapur place, no one's going to be questioning where three hundred more swords came from.''

``Well,'' Pagus said, ``it's true that we had hoped to pin those creatures on more than one front, but\textemdash ''

``However many people were in that city,'' Riku overrode him grimly, ``that's how many new Heartless we're facing now.''

Faltering in mid-bound, Pagus stared, his thin hide paling to a sickly shade of green.

``I don't suppose we could march any faster?'' Riku asked, his quiet, even voice making the back of Zack's neck prickle, his fur bristling down the length of his spine.

``I'll find out,'' Pagus said and bounded away without another word, weaving determinedly through the troops standing between him and the marquis.

``So,'' Zack said in the silence that followed, ``what are we looking at, here? Is this place gong to go under if we don't make it in time?''

``I don't know,'' Riku said with a faint headshake, staring dead ahead. ``I've seen worlds die before, but only from ground zero. I don't know how much warning there was further away from the door. I don't think it's been opened yet, but\ldots I don't think it'll be much longer.''

He didn't ask if Riku had recovered enough yet to take them back out into the black again if he had to. If he had to, Riku would; he knew that the way he knew there wasn't a sword heavy enough that Cloud wouldn't find a way to swing it. Instead he said, ``We can go on ahead if it comes to it. We can travel a lot faster than an army.''

Riku nodded once, letting out a long, slow breath of mingled relief and resolve. ``If we have to,'' he said, sounding a little easier now that he knew he had options. ``But only if we have to. An army might actually come in handy.''

``And the world not even ending yet,'' Zack said, shaking his head mock-pityingly. ``I guess we'll have to show you what SOLDIERs First Class can do.''

``If you're trying to impress me,'' Riku deadpanned, ``it's already working.''

``Yeah?'' Zack asked, reaching out to scruffle Riku's hair. ``Well, just you wait.''

He got an eyeroll for that\textemdash or, more likely, for the abuse done to Riku's hair, though a quick headshake had the fine strands settling instantly back into place. Zack couldn't say he minded, not with Riku looking like he was trying to out-serious Sephiroth, and Seph not even here to see how close he was to losing his title. In fact, he was going to count every instance of Riku looking like an actual teenager as a victory. Not least because he was starting to forget that fact himself.

The truth was, Riku was way too young to be this far from home, trying to stop a world from collapsing\ldots but then again, who wasn't too young for that?

The high spires of Castle Ghor were in sight on the horizon when a tall figure in silver plate dropped back through the ranks to join them, green eyes weighing each of them curiously from beneath an ornate, open-faced helm. Caedmon seemed especially interested in Riku, and it was clear David had been chatty from the sovani's greeting.

``I've been warned not to be surprised that you fight with a Remnant.''

``I should probably carry a sign,'' Riku said wryly, not bothering to deny it.

Zack had to laugh. ``Yeah, as weapons of surprise go, that one's a doozy.''

Now Caedmon was staring at him, equally friendly but equally fascinated.

``I've also been warned not to be surprised if your customs are not our own.''

Oh, ouch. Ruffling a sheepish hand through his\textemdash well, he was going to call it hair\textemdash Zack shrugged. ``Yeah, uh\ldots I guess I don't make a very good sovani.''

Caedmon's scowl was instant, his ears flicking sharply back. ``And who told you that?''

``It's not like that,'' Riku jumped in while Zack was still staring, taken aback. ``Everyone's been great. It's just that we're from\ldots really far away, and Zack here was raised by mitra.''

``You make it sound like I was raised by wolves,'' Zack complained, giving Riku the eyes until Riku thumped him.

``You were raised by us,'' Titus corrected him with a grin.

``Yeah, you're right,'' Zack said, nodding thoughtfully. ``Wolves would've been less embarrassing.''

They had Caedmon laughing by then, all that stiff, offended pride drained away. ``My apologies, then. We sovani tend to hold ourselves apart from the other races. It's rare to see such a close-knit group.''

``What about you?'' Riku asked. ``The Silver Falcons are yours, right?''

``After a fashion,'' Caedmon replied, something wistful in his tone. ``I am their current leader, true, but in practice, we usually travel in far smaller groups, or often alone. The last time we all gathered together in one place was when we fought the Conqueror's troops at Harphlus Pass.''

``You fought the Conqueror?'' Riku asked, latching onto that little tidbit like his instincts were telling him he was on to something here.

And Zack couldn't say he was wrong, not with Caedmon's ghost fading in on Zack's left, marching in steady lockstep with its living counterpart, the sadness that wasn't making it to Caedmon's face showing up starkly on its own.

``We helped to rout his armies,'' Caedmon replied modestly, ``though I myself continued on with Rush to Undelwalt.''

``Undelwalt,'' Riku echoed, and gods it was weird, watching the ears of Caedmon and his ghost twitch in time at the intensity of Riku's tone. ``What's in Undelwalt?''

``The God Emperor, for one,'' Caedmon replied, like he didn't quite know where to begin, though he didn't seem surprised when Riku considered that for about half a minute then shook his head. ``I suppose you mean the portal to the Sacred Lands, then, beneath the palace.''

``Portal. Wait\textemdash Sacred Lands?''

``Elysion\textemdash the Remnant Elysion, not the city it flew over\textemdash was the birthplace of the Remnants, or so it's said. We were told,'' Caedmon said slowly\textemdash his ghost murmured: ``Lies"\textemdash "that the Remnant Elysion held the Sacred Lands, the place souls traveled to after death. We found nothing of the sort once we reached that place, I'm afraid; only a maze, and the Conqueror's machinery.''

Riku didn't seem to hear him, staring at Caedmon but right through him. ``Gaia, that's it. Elysion. Undelwalt.''

``You lost me,'' Zack admitted.

``Undelwalt, Zack\textemdash Underworld. Look\textemdash don't ask, but\ldots these things carry over. I need to talk to David. Just\textemdash I'll be right back,'' Riku said, nearly vibrating with sudden excitement, pausing only long enough to clap a reassuring hand around Zack's upper arm before darting into the midst of the soldiers around them. There wasn't time to tell him to wait up, take someone with him, but Giese was on Riku's trail before Zack could call after him, the man slipping effortlessly through the crowd.

``Should I ask?'' Caedmon wondered aloud, bemused.

``You can if you want,'' Zack replied with a shrug, ``but I don't know what to tell you myself.'' And not because he couldn't guess; he just wasn't sure how much the marquis had actually told the man, how much it was safe to hint at without knowing how Caedmon would react. Then again, if he'd seen that machine Pagus had told them about, the one the Conqueror had tried to use against this world, then he'd seen how everything had ended. And if that were the case\ldots  ``So, we've been hearing a lot about this Rush guy since we got here. Friend of yours?''

``You don't often find a mitra so comfortable around sovani,'' Caedmon said, that wistful tone back full-force, ``but yes\ldots he was a good friend.''

``He was a Remnant,'' Caedmon's ghost said dully, as if that explained everything, and Zack wasn't even surprised. It had to be the worst-kept secret in the world, or else it was just Riku's not-so-spooky powers in action, whatever it was that made people want to spill their guts whenever he was around. He thought he understood where Riku was coming from with the actually-spooky powers, though, because that wasn't the sort of knowledge you wanted to just steal from someone on the sly: the fact that Caedmon truly believed this Rush guy was only friends with him because he wasn't human enough to share the rest of his race's prejudice.

He didn't know what to say to that, and it wasn't like he could unlearn it. He couldn't even bring it up when he wasn't supposed to know it in the first place. All he could do was shrug, say, ``Sometimes people surprise you,'' and hope like anything that was true.


\scenechange


Riku couldn't believe he hadn't seen it before. He'd been thinking it himself just a few worlds back: that some things, like Hel, were universal\textemdash they even went by the same name more times than he was entirely comfortable thinking about. The sad thing was, he'd been to the Elysian fields; a slight difference in pronunciation shouldn't have thrown him like it had.

Not that he really expected to be able to reach a literal Afterworld from the Sacred Lands, though he'd seen his fair share of those, too. In fact, he was more encouraged to have Caedmon's reassurance that he wouldn't. The Sacred Lands might very well lead to a resting-place for souls\ldots only he was willing to bet that the souls in this case wouldn't be human, never had been. He was absolutely certain he'd find the crossing-point between the two worlds there, the mortal and the Remnant; the only question was how he was actually going to get to the so-called Sacred Lands now that all the Remnants had vanished.

Well. Except his own, of course. The fact that it was first and foremost a Keyblade was what had him sprinting after David, spilling the craziest plan he'd yet come up with into the marquis' lap.

The hope that dawned on the man's too-controlled face was almost painful to see, but at least he wasn't alone in thinking it would work.

``I\textemdash yes, of course\textemdash but we can't afford a delay, even for this,'' David warned, though it sounded like the hardest thing he'd ever had to say. ``Once our business at the Heroic Ramparts is finished\ldots that will have to be soon enough.''

``Right,'' Riku agreed, ``because it's going to be a moot point otherwise. But can you\textemdash ''

``I'll send a company back to Athlum right away,'' David promised, a faint little smile escaping to match Riku's own. ``Elysion should be safe enough for the time being, and it's far closer than Undelwalt. But there are plenty of others with the talent to bind a Remnant,'' David added, his curious tone not entirely masking his caution, secrets the man had no intention of sharing\textemdash and that Riku had no intention of prying into. ``Why would you need Miss Irina's help in particular?''

``Because she's not going to be binding this one,'' Riku said with a smirk. ``And anyway, Way to Dawn likes her. I don't think we could work together with anyone else.''

Not anyone who hadn't grown up with a Remnant, who still thought of him as her brother, in fact. But more than that\ldots he'd thought Irina was like Kairi at first, but the more he thought about it, the easier it was to see her with a Keyblade of her own in hand, swinging away. She had the guts for it, that was for sure, and probably a more open heart than Riku himself could lay claim to. If there was anyone who could help him unlock the Remnant world, it was her.

He'd noticed Giese arriving with him, a lean, dark shadow that had settled in unobtrusively on his right, but he'd been too preoccupied to really think about it until they were dropping back again, Giese strolling along beside him with an amiable smile and both hands on the hilts of his shortswords. Which wasn't obvious at all.

``You know, I don't think the Athlumian army is going to abduct me,'' Riku offered, amused.

``Oh, yeah\textemdash the army's fine,'' Giese agreed sagely. ``It's individuals I don't trust.''

``Let me guess\ldots ''

``All of them,'' they said in unison, Riku hard-pressed not to laugh out loud.

``This is so weird,'' Riku said, shaking his head.

``Yeah? What's that?''

Riku hesitated, wondering suddenly if he was overstepping himself, or assuming too much, or\textemdash he didn't know. He knew Giese as a light and fast fighter, ferocious with those twin swords of his, that he had a Junon accent and would vote in favor of pit-roasting giant Damascus-shelled crabs if the subject ever came up again. What he didn't know was how the guy would react to Riku saying, ``You guys. The honor guard treatment. I mean, I know you've got your reasons, but\textemdash ''

Giese startled him silent with a laugh, saying, ``Hold on, I need a moment. Flashbacks,'' he added with a rueful grin, resting his fingertips theatrically at his temple.

``Sephiroth?''

``Oh, man, yeah. Used to doing everything himself, totally convinced that looking after him was a wasted effort, baffled by the notion of delegating\ldots ''

``I delegate,'' Riku protested reflexively, then felt his face go hot an instant later as he realized what that sounded like.

Giese laughed outright, not unkindly. ``No, you let Zack bully you into sharing. And yeah, that's worth a flashback, too. Thing is\ldots you may be our ride home, but we wouldn't be following you the rest of the time just because of who you look like. We listen to what you've got to say because you know the Heartless better than we do\textemdash and you've got a good head on your shoulders,'' he added with a grin. ``And if you haven't figured it out yet, we're not too fussed about age around here. We were taking orders from Sephiroth when he was seventeen, and then we were taking orders from Zack. It's no big deal.''

``But I'm not\textemdash ''

``In SOLDIER,'' Giese cut in neatly, smiling like he knew that wasn't even Riku's argument. ``So? Zack listens to you, and we listen to Zack. And before you go assuming that's proof we're all crazy\textemdash ''

``Zack is the least of the reasons why I assume you're all crazy.''

``Well, there you go,'' Giese said with a grin. ``Clearly you fit right in.''

He wasn't sure he wanted to know\textemdash he was squirming with embarrassment already\textemdash but he asked anyway. ``And how do you figure that?''

Giese shrugged. ``Hey, you're the one crazy enough to stick with us. What else are we supposed to think?''

Riku's answer to that was deferred as they got their first real look at Ghor: the toppled buildings, the holed stonework and battered walls, the tents that lined the pock-marked streets. At first he thought they'd come too late, that the Heartless had already been and gone, until he realized those tents weren't just built around the rubble; they incorporated it, well-entrenched. Whatever had happened to this city in the past, it had been decades, not days ago, and he got the feeling its current scarcity of people had more to do with the fighting taking place elsewhere than from any current disaster.

``I wonder how far we are from the Ramparts?'' Riku asked of no one in particular and turned in surprise when he got an answer.

``Not far,'' said General Honeywell, regarding them soberly, one hand resting forgotten on the hilt of her sword. ``We'll march past Ghor before we stop for the night; we should be there before noon tomorrow. The forward scouts are already coming back, though. It doesn't look good.'' She said it as a statement of fact, and if the reports she'd gotten had scared her, the worst that made it to her face was a vague sort of worry.

``What about the troops already there?'' Zack asked. ``How are they holding up?''

``We still hold the Ramparts, but only just. At the moment, the enemy are concentrated on the Plain of Luhang between the Ramparts and Nagapur, but we won't be able to hold them there much longer. Their ranks, as you warned, are swelling,'' she added, glancing at Riku.

He nodded, suddenly aware of the eyes and ears all around. No matter how sick he felt at hearing that, this wasn't the time to let it show. ``What have they said about the Heartless? Are they mostly Jhana or what?''

``The Jhana seem to comprise the majority of their forces, but there have been more and more sightings of a different type: man-shaped, with crooked antennae, all black. Both small and large.''

``Shadows and Neoshadows,'' Riku said, that sick feeling growing. ``They're a pain, but they're small fry.'' Just regular people, but he didn't say that. Some folks got weird about it, torturing themselves with wondering if this one or that had been someone they knew. That never ended well. ``Just\ldots if you get any reports of colossal Heartless, you need to let us know.''

Emmy stared. ``Colossal.''

``Yeah. Believe me,'' he said with a lopsided smile, ``you can't miss it.''


\scenechange


By the time they reached the place they'd camp the night, Riku was positively fretting. It might not have been obvious to anyone else\textemdash he wasn't constantly after the generals for fresh intelligence or pushing ahead to the foremost ranks\textemdash but Zack could tell by how quiet he got, the noticeable pause before he answered each time someone tried to grab his attention. Though they didn't stop until dusk, it was clear that even that much of a delay was killing him; left to his own devices, he would have pressed on through the night and done his best to take out whatever he could of the enemy before he simply dropped from exhaustion.

Lucky for Riku, he just happened to be surrounded by twelve guys who'd sit on him if he tried.

``Hey, c'mon. Take a load off,'' Zack urged, tugging Riku down to settle beside him on the grass. ``You do realize the whole point of stopping early is to get there rested, right?''

``Yeah, I know,'' Riku muttered, not that Zack had expected anything else. ``It's just\ldots I can smell them from here.''

``Those creatures?'' asked Caedmon, who'd been coaxed into joining them earlier after seeing to his own men. Ears pricked curiously, he glanced to Zack as if waiting to hear the joke. ``Even I can't smell them at this distance; we must be hours away.''

``That's what worries me,'' Riku muttered, half to himself. A poke in the side from Zack reminded him of his surroundings, and he nailed on a cocky smile, straightening where he sat. ``Anyway, I just have a nose for those things. You guys still have me beat at everything else.''

``Fascinating.'' It'd taken a little time, but Caedmon had finally relaxed enough to get comfortable, leaning back on one hand with the lower pair resting relaxed on his thighs, his legs folded tailor-fashion. With the helm off, he looked much less formal, his lean face infinitely more expressive than Torgal's cautious reserve. Paler cream than the fur on his face, his short-cropped hair had been flattened before, but it was beginning to spike and fluff in the face of absent finger-combing, and that made him look younger still. ``Is it something to do with your Remnant?''

``Not exactly,'' Riku said after a moment's thought. ``It's because of my affinities. I got pretty strong in one element, and it kind of did a number on my senses.''

Caedmon frowned, perplexed. ``Forgive me\ldots I've heard of a weapon being strong in an element, but a person? You wouldn't happen to be\ldots ?''

Zack knew what he was thinking, even with trying his hardest not to see those too-candid ghosts people dragged around with them.

Riku just smirked, having clearly worked the same thing out on his own. ``Who, me? One hundred percent mitra, thanks.'' He sounded so proud of it, Zack just knew he had to be thinking of the days when at least part of his strength had been Heartless.

``I see. And you?'' Caedmon asked, glancing at each of them in turn\textemdash or, more precisely, at their eyes. ``I'd heard there were experiments to fuse people with Remnants, but\ldots ''

``Whoa\ldots you can do that?'' Hall asked, eyes round and avid.

Stiegler snorted. ``Down, boy.''

``What? I'm just curious\textemdash ''

Zack sighed, casting a wounded look in Caedmon's direction. ``You see what you've unleashed?''

``You have my deepest condolences,'' Caedmon replied solemnly, green eyes glittering with laughter. ``So\ldots not Remnants, then.''

``No,'' Zack admitted, mostly because the guy was just so polite. ``I guess you could say we're a different kind of experiment.''

``Just not where I can hear you,'' Riku said shortly as his scent went sharp and hot: angry, protective. ``I hate that word,'' he added in a softer voice, embarrassed at his own outburst but no less fierce.

``All right,'' Zack said mildly, like his gut wasn't knotting up at how familiar that was. Reaching out to scruffle Riku's hair, he found his hand curving to the back of Riku's neck instead, giving him a light, friendly shake that felt as instinctively sovani as his cajoling grin, mostly eyes and ears. ``What about poster children for awesomeness?''

Riku broke with a laugh, shaking his head without shaking off Zack's hand. ``Is that even a word?''

``Pretty sure, yeah. Spell-check's never kicked it out on any of my reports, anyway.''

Caedmon blinked at them. ``Spell check?''

They were saved having to explain that one by the arrival of David, who settled down on Caedmon's right like there couldn't have been any possible confusion as to where he'd fetch up, much to the sovani's surprise. ``I think facing the Conqueror was actually easier,'' the marquis announced without preamble. ``At least then we had six months to prepare.'' He definitely looked frazzled, though he'd hidden it well until then. Now Zack could see the dark circles under his eyes, the lines of tension that never quite left his mouth, the bright, brittle stare of a man who suspects all his preparations might still come to nothing.

``Marching on such short notice is never easy,'' Caedmon offered hesitantly. ``That you've come so far in such good order is impressive.''

Though David looked both startled and pleased at the compliment, his sigh was still dissatisfied. ``I'm more concerned with what we'll find at the end of this march, to be honest.''

``Well,'' Riku offered, which reminded Zack all at once that it was probably about time to let him go. ``The trouble with Heartless is that most people just plain don't hit hard enough to take them out with ordinary weapons. Having yama on your side, though\textemdash that evens the odds some.''

``Blocter will be so pleased,'' David said with a faint smile, though his eyes were just about devouring Riku where he sat.

``Thing is,'' Riku continued, ``I'm betting a lot of your weapons aren't ordinary. Even the types of Heartless that aren't particularly weak to m-Mystic Arts,'' he caught himself quickly, ``will go down faster under an enchanted blade. But your casters are still probably going to be your best asset. Hammer them with spells and just keep at it. Just watch out for the solid black ones with the antennae\textemdash those things can dive right into the ground, and unless you've got some Earth spells you don't mind setting off under your own feet, you won't be able to get at them until they pop back out again.''

``Clearly we have our work cut out for us,'' David said ruefully, though he looked more hopeful than before.

``Count on it,'' Riku said firmly, ``but don't let them get to you.''

``Oh?''

``Against Athlum, the Silver Falcons, and these guys?'' Riku asked with a smirk, jerking his head in Zack's direction. ``The Heartless don't stand a chance.''

When the marquis wandered away a little later, Caedmon followed him, the two talking quietly of old campaigns, mutual friends. One by one the campfires were banked to a dull glow as the sentries settled in for their watch, soldiers turning into bedrolls though there was more than one pair of wakeful eyes staring up at the stars. Even Ochs tossed and turned a bit until Hall threatened to Sleep him and Ochs threw something at his head, complaining about rocks, damn it. Catching Ochs' projectile out of the air, Hall electrified it, pitched it back with a grin, and nearly started a friendly brawl until Stiegler growled at them all to settle the fuck down before he put them all down for a little nap.

Glancing over at Riku, who'd bunked down beside him again, he met stifled laughter with a grin of his own, momentarily distracted from the coming day. ``Consummate,'' he murmured, almost inaudibly, ``professionals.'' Which won him a totally undignified snort from Riku and a half-hearted snarl from Stiegler before Riku shook his head and closed his eyes, folding his hands neatly over his stomach with a huge grin still plastered on his face.

A job well done if he did say so himself.

Pillowing his head on one arm, he watched Riku slowly drift off and tried his best to follow that very good example, without migrating that way in the night, this time. Though he'd been lucky enough to wake before Riku, he didn't exactly want to catch a repeat of the look Titus had given him that morning\textemdash amused, assessing, and unexpectedly sympathetic, like he'd figured out from Zack's panic face that he really hadn't meant to do that.

Not that he'd never sleepwalked into someone's bed before. It was just that he'd been five at the time.

At least it wouldn't be much longer now. They had one more march ahead of them, one more fight\textemdash or so he hoped\textemdash and then they could get down to the business of closing this world, moving on to the next. He'd get his old body back, and Riku would stop smelling like adrenaline, and worry, and so much pent-up frustration and aggression Zack wanted to wrap all four arms around him until he stopped vibrating under his skin and tell him to breathe already. He knew from experience that the waiting was the worst part of any fight. By tomorrow they'd be in it, not working themselves up over possibilities. They'd see what the enemy had to bring to the table, and they'd counter it. Simple.

The only thing he had to worry about was Riku, never truly disarmed but still unarmed, new to it, used to the familiar protection of a sword. He'd done all right for himself on the plains outside Athlum, but Zack still couldn't say he liked it much. So maybe he'd just stick close for this one, not that he wouldn't have anyway. He'd have done the same for Sephiroth\textemdash though really, trying to picture Sephiroth without Masamune was like trying to imagine Riku without the Keyblade; it just didn't work\textemdash and that wasn't being overcautious or overprotective or over-anything. That was just the way things were. They were SOLDIERs; they looked out for their own, even the ones who didn't have mako shining out of them. Riku would just have to get used to it.

He didn't realize he'd been glaring stubbornly into the dark until the slow, amused shake of a ghostly head made him blink. Sitting between their bedrolls, knees bent as he leaned back on his hands, Riku's double watched him with a fond half-smirk, one brow arching at Zack's start of surprise. At first he was at a loss to explain the panicked thump of his heart against his ribs until he realized it was more guilt than nerves. He'd already inadvertently dragged one painful moment of true confession out of the real Riku, but Riku had at least been able to choose that one. If Riku's double started babbling secrets at him now\textemdash 

Smirk widening into an actual smile, the ghost double shifted, reaching out with an insubstantial hand that carded through Zack's hair with a light, cool touch, barely-felt but still soothing. Part of him wanted to be startled by that, but it was hard to keep his eyes open in the face of that hypnotic stroking. Wait, he wanted to protest groggily, not the ears, but the smirk was back, long fingers trailing up to smooth a thumb over the soft-furred back from base to tip, and before he could force his leaden limbs to move, the world slipped away, and that friendly touch with it.


\scenechange


Seeing the high, sturdy walls of the Heroic Ramparts on the horizon at last, Riku had to force himself to hold to the same steady pace, every part of him wanting to sprint ahead if only to have it all over with. He could see why the defenders had chosen this place to make a stand: the line of fortifications extended for miles, forming a bottleneck at the narrowest part of a river too wide to ford elsewhere. The only problem he could see was that it was meant to be held from the other side\textemdash Nagapur's first line of defense\textemdash when they already knew Nagapur had fallen.

Taking a deep breath, he flexed his hands in his new gloves, telling himself to wait, stay calm. He didn't only have the SOLDIERs to think about this time, and now more than ever, he couldn't afford to go off half-cocked. They'd be fine, though. Anything anyone had for weaponry that could be enchanted had been enchanted while they traveled; formations had been rearranged to make sure their casters would be fiercely guarded; and he had to believe that they'd arrived in time, because the world hadn't ended yet\textemdash though that might be a close thing.

General Honeywell had just gone silent beside him, her sharp eyes narrowed on the battlements as she lifted a hand against the sun.

``Look there\textemdash are they fighting?''

``Yeah,'' Zack replied without missing a beat, one fast glance and SOLDIER-sharp eyes telling him everything he needed to know about the commotion on the walls.

``Then the Ramparts have been breached,'' Emmy warned, running ahead to meet David.

``I think that's bad,'' Riku offered, his heart leaping into his throat.

``I think you're right,'' Zack agreed. ``You ready?''

``As I'll ever be,'' Riku said, and then they were racing to the head of the pack, the trumpets sounding out something complicated that he hoped like hell was open gates.

There were Jhana Heartless on the walls, glimpsed more clearly as they closed the gap: Fighters mostly, the occasional Shaman, but not one Magus. Those were probably down below, because not all the magic he saw going up was friendly. Every scream made him grit his teeth in sympathy, knowing he couldn't cast blind, shouldn't try portaling ahead, because that was a stupid amount of energy to burn when his legs worked just fine. Another fast glance at the wall had him scowling, questioning his eyes, only that was definitely not a Jhana he saw clawing some poor bastard to shreds. Another type of beastman, maybe\textemdash this world was just seriously blessed in the monster department\textemdash with a face like a hyena and a grin like a Bomb.

``Gates!'' he heard David shouting at his back, sharp and urgent. ``Open the gates!''

He got why Emmy had been so worried at seeing the fighting on the walls when the portcullis went up and the big doors swung open. Over the chaos in the field beyond he saw another set of walls, a paved courtyard beyond that, what looked like another set of walls on the far side. And from the number of Heartless he could see, the Ramparts hadn't just been breached; they'd been overrun.

He hesitated half a heartbeat before calling Way to Dawn in the middle of that crush, but the pressure against his ribs from the inside was almost a living thing, the Keyblade straining to be loosed, and they'd been through too much for him not to trust it now. It wasn't so much a summoning as a loosening of control that called the Keyblade to him, and it flared into form already moving, circling just overhead with an eager hum.

It was madness just inside the gates, the defenders grimly holding their own, the Heartless throwing themselves with suicidal fury against that point of weakness. Though he would have liked to throw off a spell to blow through that clot of attackers, there were too many soldiers interspersed with the enemy, and the darkness just wasn't that precise\textemdash or maybe that was just him. Instead he plowed into the front ranks with fists and feet, thanking the Keyblade and the Dark that he wasn't limited to ordinary strength, because these weren't Shadows.

And then some of them were.

He jumped out of the way half on instinct, seeing the ripple of darkness that eased under his feet out of the corner of his eye at best. The claws that swiped at his legs missed, but the warhammer sweeping towards his skull would have hit if a broad, heavy blade hadn't deflected it at the last instant. Growling loud enough Riku could hear him over the din of battle, Zack pushed the Shaman back, pressing forward with teeth bared, ears ominously flat.

He was seriously going to have to learn to fine-tune his magic better, because aiming a Dark Firaga at a Shadow was just ridiculous, but the damned thing slicked itself right back down into the ground before Riku could thump it properly by hand.

``Damn it,'' he muttered, irritated and out of sorts, only mollified when they made it past the bottleneck at the gates and Way to Dawn circled down to join the fray, cleaving through dark bodies and eeling between startled soldiers without touching a one. At least the only friendly fire he had to worry about was his own.

He noticed the difference as the other SOLDIERs came through after him, how quickly the battle turned once the Heartless were pushed back from the gates, the Athlumian troops and the Silver Falcons hot on their heels. Spells flew over his head thick and fast, some that he recognized but many that he didn't, picking off the Heartless swarming over the battlements and clearing a path to make room for the troops still outside the walls. The defenders inside the gates were beginning to form up as well now that some of the pressure was off, and in the fleeting glimpses he got between throwing punches and a Dark Shield or two, Riku was relieved to see that things didn't look nearly as bad as they had at first in all the chaos. There were way too many Heartless, yes, but there were also more defenders, enough to pin the Heartless between them now that they'd regrouped.

Surprised, Riku realized as the soldiers started to regroup, gaining ground as scattered pockets of fighters became solid walls of swords and spears once more. They'd been surprised somehow\textemdash by the slipperiness of Shadows, Riku didn't doubt\textemdash but not completely overwhelmed. That was good to know; he'd been expecting at least two armies to be manning these walls, and the thought of having that many new Heartless to fight was enough to turn even his stomach.

He didn't think it was his imagination that Zack was shadowing him more closely than usual, but he couldn't exactly complain. It was Zack who kept the worst of the Heartless off him when he was bracing himself to cast, who stepped in like they'd practiced the move when the Neoshadow he hadn't seen behind two hulking Magi nearly ripped him wide open. It was embarrassing and more than a little frustrating, but he just felt so hobbled\textemdash not by his own empty hands, but because he wasn't used to fighting in the middle of so many friendly targets. He nearly always fought alone\textemdash he was used to it\textemdash and trying to be so careful of everyone around him was just\ldots maddening.

And did that sound familiar? Why, yes it did.

``Oh my god,'' he yelled over his shoulder, lighting up with something like relief as he saw the giant knot of Heartless milling uncertainly before him, bunching together as they were flanked and pinned. ``Zack! I totally get Sephiroth now!''

He was starting to get the showy spellcasting thing, too, because there was something deeply satisfying about throwing both hands out, like he could launch his Dark Firaga into the midst of that cluster of targets just that much faster if he physically helped it along.

As the shreds of those Heartless were still drifting into the air in the wake of a cloud of hearts, Zack caught up to him, grinning, cocking his head and perking one ear in Riku's direction. ``So?'' he asked. ``You want to hug it out?''

Riku laughed, feeling inexplicably lighter in the face of Zack's own good humor. He might not be holding his own right now, but Zack didn't seem to mind picking up the slack while he was figuring it out.

``Are you kidding? I'm going to own it.''

``That's our mini-Boss,'' Zack said, rueful and proud at once, lifting his sword in a jaunty salute before they dove back into the fight.

When he heard Stiegler bawling out orders somewhere off to his right, he didn't think anything of it at first, not until he realized the Sarge had found the ragtag odds and ends of several decimated companies, decided they looked lonely, and had taken them in hand. He was putting Hall to work, too, buying his rattled, unaugmented troops some elbow room until he had them ready to advance again, sweeping in to herd a pack of Heartless into the waiting arms of a phalanx of yama spearmen.

``That's more like it!'' Stiegler boomed out with a laugh, grinning from ear to ear. ``Now let's send these bastards packing\textemdash form up! Move!''

They took back the first section of the Ramparts quickly after that, bunching up their targets where they could, leaving the stubbornly solitary Heartless to the heavy hitters like the SOLDIERs and the yama, or a few well-placed Arts. Taking the next gate slowed them down at first, but they had the advantage of the high ground this time, the casters on the walls picking their targets while Hall kept them covered with that magic-proof Ward he'd learned in Leá Monde. There seemed to be more yama amongst the defenders in the wide, boxy courtyard, but that might have been Riku's imagination, or maybe the yama were just better at holding their own. He wasn't going to think about that\textemdash how many lives might have been lost to tip the numbers that way\textemdash but then he caught sight of an old yama in red and grey, his still-powerful body striped with scars, grimly swinging an oversized axe even as his honor guard was going down around him, overwhelmed by a crush of Fighters.

``The Duke!'' David shouted at his back. ``To the Duke!''

It was Titus who reached the old man first, Blocter hot on his heels, and if Riku had thought yama were impressive fighters before, he hadn't seen them angry.

He didn't wait to see the court fully cleared, charging up the cracked stone steps to the battlements, Way to Dawn weaving in and out of the soldiers on the walls right along with him and ripping through the few stray Heartless that remained as they passed. It wasn't lost on him that no one was in any hurry to haul open the gates just below, and if that meant they'd reached the limit of the Ramparts' defenses, then beyond this line must be\textemdash 

Heartless. Thousands upon thousands, worse than he'd seen massing in the Great Maw while Sora was still asleep, worse even than what he'd seen on his own world when it was breaking apart. He hadn't seen this many Heartless since he'd shut himself on the wrong side of the door to darkness, and the only thing that kept his heart behind his ribs and not somewhere in the vicinity of his boots was the fact that what he was seeing was just another army. Parts of it would have been pretty impressive solo, that went without saying, but nothing on the plain below was blotting out the sky or cracking the world open like an egg, and he'd be damned if he panicked without better reason than being a little outnumbered.

Which maybe meant he'd been hanging out with the Restoration Committee too much, but these things happened.

Footsteps slowing halfway down the length of the walls, Riku dragged to a halt, staring out at that sea of black without blinking. There were whole companies of Jhana, milling without mingling, as if even without hearts they were still keeping the notion of tribes alive and well. The dog-faced things were less picky, slinking around solo or forming packs that dissolved just as quickly, all of them a uniform carbon-black as anonymous as a Shadow\textemdash and there were plenty of those. There were wyverns too, massive compared to what he was used to, and worse.

``Tell me those aren't dragons,'' Zack muttered on his left, not even bothering to lean out of the way when Soul Eater came close enough to have clipped his ear if he'd flinched.

``Okay. Those aren't dragons.''

``Seriously?''

Riku laughed, quiet and shaky, so he swallowed it, quick. Dragons or not\textemdash and there were only two of them, though two were probably enough\textemdash he just couldn't stop scanning the hills, feeling his gut twist and tighten at what he wasn't seeing. ``Wasn't there a Duke of Ghor?''

``Yeah,'' Zack agreed, hunching a shoulder as they were joined by Titus and Hall, a David who'd paled at the sight of the army below but who moved with the same determination, eyes electric. ``I think it's that old yama Titus just hauled out of the fire. Why?''

``Some of these soldiers are probably his. So where are the rest?'' Riku asked, leaning both hands on the ancient stone walls as if leaning out just a few inches more would somehow change what he saw. ``Elysion's close-by, right? Even if no one made it from Nagapur, shouldn't there be\ldots more?''

``There are,'' David assured him, coming up quick to join him. ``Caedmon's scouts brought the word. They were forced to retreat, but we'll have reinforcements to the north and east of here if we can break them out.''

``Yeah, but first we have to break us out,'' Zack reminded, shaking his head at the crush below. ``Also, dragons.''

``Zack has this phobia,'' Titus offered, amused.

``It's not a phobia. All I'm saying is, when dragons show up, it's a bad omen, okay?''

``There's dragons in Nibelheim,'' Riku reminded, wondering what the problem was. It wasn't like Zack had never seen one before\textemdash 

``Uh-huh. And Zack here's dragon-bait,'' Hall explained with a grin. ``Seriously, you can't keep them off him. So the one time he goes home with Strife for Solstice\textemdash ''

``Look, can we never bring that up again? Also, if you've jinxed me, you're taking care of the dragons.''

``If they don't spit acid, I'll take care of the dragons,'' Riku said decisively, turning in the same breath to David. ``They don't spit acid, do they? Because that usually sucks.''

The marquis looked like he really wanted to smile but didn't want to encourage them. ``No acid,'' David said with suspect solemnity. ``These breathe darkness.''

``I think I can handle that,'' Riku said with a perfectly straight face, looking out over the plain beyond. ``And I think I can buy us enough room to break out. I just need to be roughly there,'' he said, pointing to a spot right in the thick of the nearest Jhana tribe. ``Alone.''

Zack's ears flattened instantly, but all the man said was, ``Portal?''

``Too much power,'' Riku replied, shaking his head. ``I don't want to waste it on that.''

``Okay\ldots how, then?''

Zack was probably strong enough, but there was no way Riku would ask it of him, not with Zack so uncomfortable in his new body. If Riku fucked up, it'd be his own clumsiness to blame, but he'd bet Zack wouldn't see it that way.

He turned to Titus instead.

``I don't suppose I could change your mind about the usefulness of flying?''

``Always the little guys,'' Titus rumbled, shaking his head. ``You want to do this now?''

``The sooner the better,'' Riku agreed, stepping closer as Titus rolled his shoulders, crouching down and making a stirrup of his hands. ``And hey\textemdash if Hall's right about the magic around here\ldots the further you send me, the better.''

``You got it,'' Titus said, and though there wasn't room for Riku to take a running start, it was clear in the instant Titus heaved him into the air that Riku didn't need one.

The sheer force of Titus' boost had him tucking up instinctively, his legs curling under him though he managed to force them straight at the last instant, giving him just that much more momentum. That sense of weightless velocity should have left him feeling disoriented, out of control, but finding that perfect balance of tension and loose readiness had become second nature, nearly instinct. Sparring with Sora had taught him to fall, and living on the islands had taught him to dive, but it was Sephiroth's particular brand of crazy that had taught him to fly, made gravity only the burden he let it be.

There was time to look down and choose his landing, to decide just how his body would turn to get his feet under him, time to open himself to the darkness and draw in every scrap of power he could until it thrummed under his skin, eager, hungry. He saw the first hovering wyvern notice him and fold its wings into a dive\textemdash saw the bolt of light that exploded in its face, making it pull up in midair, shedding dark streamers like blood\textemdash saw the Keyblade spiraling down and down, ready to tear him a path if need be.

Fire exploding across the ground in a widening circle just moments before he landed nearly shocked him out of the spell he was focusing. That was definitely not the Keyblade, but the power smelled familiar\textemdash smelled like Hall\textemdash so he ignored it, touching down on scorched earth emptied abruptly of distractions and letting the darkness tear out of him unchecked.

It wasn't quite like the last-ditch attack he'd pulled off once before, with his whole heart behind it. It wasn't his heart that fueled this one; it was his darkness, a solid wall of heavy shadow that blossomed out around him to slam into the Heartless with crushing force, the acrid smell of hearts torn free rising even over the musty-cold scent of the power he'd raised. He couldn't see anything in all that black, and as an icy shockwave buffeted him from all sides as the dark spiral widened, he dropped to one knee just to stay upright, his fingers digging into the dirt as he listened for the ominous crack of magic on stone. If he'd put too much force into that, hadn't landed quite clear enough of the walls at his back\ldots 

Time slowed along with the breath that kept faltering in his chest, each moment stretching to a minor eternity as his pulse drummed in his ears. Before worry could spike into panic\textemdash because the spell should have faded by now, run out of steam; even darkness like his couldn't power it forever\textemdash the impenetrable shadows around him burst apart at the seams, thick tendrils whirling away as if storm-snatched, dissolving even as he winced his eyes closed against the noonday sun.

He wrenched them open again almost as soon as he'd closed them, the world spinning around him when he didn't have a horizon to fix his gaze upon. Even then, things were wobbly, and though there wasn't a Heartless left within a stone's throw of him\textemdash and he could throw pretty far these days\textemdash he cursed the numbness of his fingers as he fumbled for an ether. He'd burned too much magic again, and though the darkness was already rushing back in to fill the empty hole inside him where all that power usually coiled, that wasn't quite the same as getting back the magic he'd used to focus it. He was just lucky he hadn't knocked himself out again in the meantime\ldots and that Zack wasn't close enough to see the way his hands were shaking.

The first ether got him on his feet, and the second made him feel like he'd actually be able to stay there without falling over again anytime soon. He would have felt better about the whole thing with a sword in hand, but already the Keyblade was spiraling in closer, circling him with a low, vicious hum: protective and eager, impatient to fight.

Time to work at keeping all the ground they'd just won.

Riku took a deep breath, gathered himself, and broke into a run.


\scenechange


Stuck on the walls, Zack had watched with his heart in his throat as Riku threw himself right into the middle of an army of Heartless, and if the image of Riku in midair\textemdash all easy grace and something Zack could only put down to trust\textemdash was going to stay with him for a long time, so would the breath-stealing uncertainty of the next few moments. With his own eyes stupidly fixed on Riku, it was the marquis who noticed the Wyvern Heartless first, who fired off a spell that winged as straight and true as an arrow to check the thing in mid-dive. He'd seen Hall winding himself up for a long-distance cast even as Riku was twisting in mid-flight, curling his legs under him like a cat\textemdash and there were too many Heartless on the ground; Riku would come down in a ring of swords and claws and teeth, too damn far away for them to reach him in time\textemdash 

And then there was fire, blue-white at the center, burning so hot it seared the Heartless away in instants, blew through its fuel in one ravenous gulp and flickered out almost in the same breath. Riku fell through a shimmer of freed hearts, coming down on empty ground and landing without a wobble, light as you please, with a good six feet of elbow room in any direction.

Seconds later he was just gone, swallowed up by a multi-armed spiral of black that barreled out like the floodwaters of a dam breaking, devouring everything in its path and doubling its reach by the second. Some of the Heartless seemed confused, lingering uncertainly until that roiling tide swept them under and kept rolling; some tried to run and weren't quick enough. Zack noticed the Shadows diving into the ground, but he didn't know if that saved them or not. He couldn't see anything inside that wall of darkness, couldn't tell if Riku was holding his own or whether any of the Heartless would prove to be immune. He couldn't even be sure the spell was working until the first few hearts jerkily broke the surface, spinning drunkenly in the air as if tugged at by heavy winds.

He let that distract him even as the darkness drew closer, and closer, until he wondered in the very back of his mind whether someone ought to order a retreat from the walls before it was too late.

The nearest edge of that boiling wall of darkness was so close he could have reached down off the wall and dipped a hand into the black when it finally burst apart, tearing into ragged shreds that melted away before his very eyes. All that was left behind was a stretch of cleared field as wide as the parade ground back home, and though he checked the churned earth for Shadows, there was nothing to see but grass bent perfectly flat, a scattering of weapons and armor left behind without bodies to carry them, and Riku, down on one knee but still in one piece.

``Come on,'' he heard himself say, all his attention fixed on that lone figure climbing slowly to his feet, knocking back two potions in quick succession\textemdash only knowing Riku, those were ethers, and two meant he'd stretched himself way too thin. ``We've got our opening; let's make this count.''

He didn't wait for the gate to be hauled open or to hear who was coming with him. He just went straight over the wall, landing with barely a huff and making a beeline straight for Riku on the first stride.

And of course he ended up playing catch-up, because Riku staying put when there wasn't a stout length of rope involved was clearly not happening on this or any other world.

``Didn't we talk about this?'' he prodded as he drew even, halfheartedly swiping at a streak of bruise-violet that careened just a little too close. He didn't think Soul Eater actually had it in for him or anything, but damned if the crazy sword hadn't just buzzed him. And now it sounded smug, like it was laughing at him.

Riku tossed a fast glance his way, arching a brow. ``About what?''

``The joys of sharing!''

``Don't be greedy, Zack,'' Riku shot back, so primly it would have been hilarious if Zack hadn't been checking him over for signs of exhaustion. ``There's more than enough to go around.''

He had to admit, Riku looked mostly all right. There was a faint tension around his eyes, a symptom of the headache that usually followed from nearly emptying yourself of magic, but his eyes were sharp and clear, and there wasn't a trace of hesitation in his stride. He was just as quick to throw off another spell, and though that didn't exactly prove anything, it was a point in favor of Riku actually being in pretty good shape and not just more proof that he was a tough little bastard.

``Fine,'' he said over the blare of trumpets at his back, the roar of an army out for blood. ``Since you're embracing your inner Sephiroth and all.''

``You are seriously obsessed with hugging, you know.''

``Have you counted my arms? Lately?''

When Riku hit the front ranks of the swiftly-recovering Heartless, he was still laughing under his breath, all fists and jabby elbows and one unstoppable grin.

Zack was going to count that as a victory too.


\scenechange


Standing on the crest of a rise in the northern hills, Allan glared down the slope with narrowed eyes, watching as the creatures that had overrun the Plain of Luhang and taken Nagapur paused in their dogged search for them and turned, retreating back the way they'd come on some invisible signal. Good news for the fools at his back; the healers had needed more time, and now it seemed as if they might get it. He just didn't understand why those creatures had given up their pursuit, and that troubled him, his ears flattening down in annoyance as he watched those nightmarish Jhana shamble away.

``Sir,'' a young mitra called excitedly, waving him over when he reluctantly turned. Six months ago, he would have destroyed this rabble for daring to appropriate a name that should rightly be lost to history by now; instead he found himself leading the Steel Syndicate once more. ``Sir, you have to see this! It's the Ramparts,'' the boy added, thrusting a pair of field glasses at him\textemdash as if sovani eyes weren't far superior. ``The defenders\ldots they've broken out!''

From this new vantage, he could see the snaking walls of the Heroic Ramparts, though the great, empty swath where part of the dark horde had once stood pricked his ears up straight in amazement. Somewhere inside the walls, the tide had clearly turned, and now the defenders had regrouped, boiling out of the gates and taking the fight to those creatures once more. Some fool even felt confident enough to raise a standard, as if two hands could be spared against those things.

When the wind caught the banner and tugged it out straight, Allan scowled, his ears pulling back. Even sovani eyes couldn't distinguish much more than color at this distance, but that flag, black and red\textemdash 

``It's Athlum!'' the mitra exclaimed, peering through the glasses Allan had waved away. ``Athlum stands!''

Allan huffed. If Athlum had joined the fight, then Torgal would be down there as well. In the thick of things, as always.

``It's about time,'' Allan growled, his hands itching for his swords. ``Prepare to move out. We're joining the defenders.''

``Yes, sir!''

``Hmph.'' Torgal had best appreciate the sacrifice he'd made; as if he'd wanted the obedience of a pack of short-lived idealists. ``And where are you going?'' he snapped at a man trying to jump into formation though he wobbled on his feet, naked mitra face ashen from blood loss. ``Stay here and guard the wounded!''

``I\ldots yes, sir!''

Allan huffed an irritable sigh. How these fools had survived before he'd taken them in hand, he had no idea.


\scenechange


It was the awed ``Fuck me,'' that caught Nora's attention: not that Loki running his mouth was any kind of surprise, but the fact that he actually sounded impressed was worth paying attention to. Rolling the arm she'd just had bandaged\textemdash those sneaky little bastards' claws hurt\textemdash she nodded grudging thanks at the nervous Academy healer and went to join the former bandit at the cliff's edge.

One glance at the foot of the Ramparts had her cursing as well, wide-eyed as she watched the front ranks of those creatures get swallowed up by a hungry black cloud. She might have worried it was some new attack by those monsters, except that they were scrambling to get away from it, turning to run and getting swallowed up before they made it five steps. Whatever it was, it was friendly, or close enough; it was just that she'd never seen anything like it.

``Haruko!'' she yelled without tearing her eyes away from the cloud. ``Get over here and take a look at this!''

Though it'd be fair to say that there was no love lost between Nora and her sisters and the Academy, when the Academy forces had been overrun, the Ladies of the Bloody Alice had stepped in and kept them from getting their asses handed to them. Nora knew Haruko didn't like her; Nora had been Third Committee before she'd been promoted to glorified experiment, and Haruko was a good little girl who'd made it all the way to Director by playing it safe. All the same, Haruko didn't drag her feet when Nora called, and there was nothing but polite curiosity on her face\textemdash at least until she got a look at what was going on down below.

``Oh, my,'' Haruko breathed, staring avidly with her lips genteelly parted instead of gaping inelegantly the way Nora suspected she'd done.

Stuffing down the urge to rearrange that pretty face\textemdash now wasn't the time, and fuck, wouldn't Rush have given her hell?\textemdash Nora jerked her chin towards that swiftly-growing cloud of lightless black. ``Not one of yours, then?''

``No,'' Haruko said wistfully. ``I have no idea what that is.''

Well, fuck.

``Hey, it's taking out the monsters. Who cares where it's from?'' Loki offered with a shrug, casting a nervous glance at Haruko from the corner of his eye. His own smarts and Rush's endorsement had kept him from the gallows so far, but he never forgot that there was still a price on his head, and Haruko had the authority to have him arrested on the spot.

``The enemy of our enemy is not always our friend,'' Haruko replied mildly without looking at either of them.

``Yeah, whatever,'' Nora huffed. ``Look. It's been fun, and if you people want to stay up here all nice and cozy, we won't stop\textemdash ''

``Oh, fuck me twice.''

Just like that, the dark cloud blew away, leaving nothing but an empty field and some guy just now climbing to his feet, apparently the sole survivor. Which meant he was probably the one who'd set off that flashy Art in the first place. Which meant\textemdash 

She blinked hard at the first flicker of sun off metal, straining her eyes because they had to be playing tricks on her. Only there it was again\textemdash a second flash, a second sword, both of them spinning through the air in lazy\textemdash circles, fuck, they were circling that guy, not thrown but flying under their own power, like\textemdash 

``A Remnant,'' Loki ground out, his voice curiously flat. ``They've got a Remnant down there.''

They looked at each other at the same time, neither of them breathing, the same strained hope staring back.

Whirling on Haruko, Nora snarled, ``You get your people ready. Now. We're going back down.''

Haruko might have been Rush's friend\textemdash the kid had no taste whatsoever; just look at Loki\textemdash but she wasn't one of them. She hadn't been there at the end, didn't know, couldn't know, or Nora would have to kill her, just to be on the safe side. She didn't argue, though, just nodded once and hurried away. Probably itching to get her hands on that Remnant so she could pick up her studies where she'd left off.

``It's probably not him,'' Loki offered reluctantly, a little too casually, like he was already bracing for disappointment.

``So? If he's got a Remnant, maybe he's got answers.''

He'd better have some answers for her. She didn't intend to rest until she'd gotten one that satisfied her, and anybody who had a problem with that had better get the hell out of her way.


\scenechange


They'd been making pretty good headway until the dragon spotted them\textemdash or rather, until the dragon spotted him. Zack had all of three seconds to notice a pair of great, golden eyes the size of cart wheels fixing on him and him alone, and then the oversized lizard was barreling toward him like a runaway freight train, crushing other Heartless in its haste to get to him.

``Hall's a dead man,'' he muttered under his breath, and whether Riku managed to hear that over the clamor of battle or whether the thunderous approach of ten tons of scale and muscle had caught his attention, at least Zack had the satisfaction of seeing him look solemnly impressed.

Of course Riku took that as his cue to go running to meet the thing, but Zack had hardly been expecting anything else.

One thing for sure: Riku was no fool. He let the thing rush past him and went for its legs with a Dark Firaga from behind.

Shrieking its fury, the dragon whipped around, its long, heavy tail crashing against friend and foe alike and sending men and monsters flying. Zack managed to jump that sinuous lash, coming down right on top of the thing and jumping again as an enormous head came jerking up, peering back over its shoulder and half-spread wings in affront. Yeah, he'd pissed it off, and now it was turning again, Riku forgotten, everything in its dim little mind forgotten but Flatten Zack.

He could work with that.

He saw Riku roll under the thing's stomach to escape the next lash of that tail, saw the Keyblade dive after him and the dragon rear up with a scream as the twin swords dug ragged gouges into its belly armor. When its forepaws hit the ground once more, it hunkered down low, wings flared as it stretched its neck out straight and cracked its jaws wide on a deafening roar.

Darkness, he remembered the marquis saying. It breathes darkness.

He had time to throw up Ashley's Demonscale Ward before the black flames reached him, time to feel someone hit him with that Regen spell Hall was so fond of\textemdash only that Ward only blocked about half of what he was hit with, and Regen worked slow, and he already had a Limit burning through him before he felt the first crackle of healing sink into his skin.

Charging that still-open mouth, he swept his blade up, around, focused all that power inside him and let it all go, a howling stream of braided lighting that shot right down the beast's gullet in the tightest beam he'd ever managed.

The Heartless went wild, rearing up again to tear at its throat with scrabbling claws, mouth gaping open silently as it whipped its head up taut. Zack winced himself when he saw the Keyblade slam hard into the thing's skull, staggering the beast even as the blades rebounded and caught themselves in midair, instantly going back to their predatory circling, probing for weak spots. Already there were dark motes rising from the thing\textemdash not quite dead, but it had to be in pretty bad shape inside\textemdash but he wasn't going to assume it was down for the count until it up and disappeared. Being taken out by some Heartless' dying last move was not the way he wanted to go.

It was Hall who hit him with the Curaga\textemdash twice\textemdash but it was Riku who skidded to a stop at his side, looking him over frantically and then glaring up at him narrow-eyed, like he was about to get one of his own lectures handed back to him verbatim. The only thing that spared him was the dragon dropping to all fours again and lunging towards them, baring fangs as long as Zack's arms in a mouth seared ash-grey on the inside.

A Heartless that size should have been harder to stop, but it never quite worked up the momentum for a full charge. Instead there was Hall tangling its legs with a whiplike Scourge, Schreiner swinging that axe of his like a warhammer as it stumbled and the Sarge taking its other leg out from under it as it passed, Titus standing ready when it went down hard, jumping right up onto its muzzle as it snapped closed and driving a yama-sized lance right through its skull as it slid to a listing stop. When it burst into a mile of shredding shadows under him, Titus let himself fall, landing on his feet with easy grace and turning back with a faint little grin.

``You and your dragons,'' he called, and Zack, torn between laughing and growling, flailed three unoccupied arms with a mighty shrug.

``That isn't even my fault!''

``Heads up,'' Hall warned before he would warm to the subject, nodding at the closest Heartless, which were beginning to sidle closer now that the dragon was out of the way. Zack nodded back, taking a firmer grip on his sword\textemdash 

\textemdash and froze, the fur on the back of his neck bristling uneasily as he watched Riku slowly still, staring out across the battlefield with an uneasy, distant frown.

``What?'' he asked, more sharply than he'd meant to, except that a Riku focused anywhere but on the here and now made his insides knot up tight.

``There's something weird,'' Riku said, cocking his head like he was listening to something. ``It's like\textemdash ''

He got the warning half a second before everybody else did just from the way Riku's eyes went huge, horrified but with an awful lack of surprise that made Zack's throat close with a growl he didn't quite voice. There wasn't time anyway; mere instants after Riku fell silent, every Heartless on the battlefield tried to converge on them at once, and he was suddenly too busy trying to make each swing and parry count to worry about how he was going to keep the universe from disappointing Riku so often he just got used to it.

Caedmon reached them as the first wave hit, and just seeing the way he handled those double halberds double-handed, he thought he understood what good four arms were after all. And that was before he saw Torgal cut a path to his lord with a sword in each hand like some kind of grey-furred whirlwind of doom.

He hadn't realized the marquis was so close, though Caedmon's presence should have given it away, if not the acid geysers going up on every side, eating through the Heartless and leaving nothing behind but a few dark stains. It was a nice trick, that last bit; he was definitely with Riku when it came to fighting in the middle of that stuff, and having your boots melt right off your feet was seriously not his idea of a good time.

A weird sort of stillness on his right made him glance over uncertainly, and he nearly missed a block when he realized Riku was standing poised but stationary, his hands outlined in shadows with the magic still unfocused, eyes scanning the battlefield as if looking for something in particular. ``Riku!'' he yelled, even though he could tell the Keyblade was working overtime, circling Riku so fast it was hard to see.

``Zack,'' Riku called back without looking at him, fingers flexing even as his shoulders went that much tighter. ``The Heartless\textemdash there's someone controlling them!''

Controlling them. Shit.

When a familiar burst of darkness leapt from the ground just yards away, he knew even before it settled that it would form a portal, high and narrow, like the tall windows in the gallery walk in the castle back home.


\scenechange


Riku had known there was something odd going on almost from his first glance over the Ramparts' walls. That many Heartless in one place, massed that quickly: that just didn't happen, not until a world was on shakier ground than this one\textemdash not without help. They'd seemed a little too organized, but he'd let himself put it down to paranoia, at least until the dragon went down.

He'd felt it then, not a spoken command but a push through the darkness itself, focusing all those hungry minds and firing them with a single purpose. It was how Ansem had commanded the Heartless\textemdash the fake Ansem, anyway\textemdash and he'd done it through Riku often enough that he recognized the echo of it now, even when it wasn't aimed at him, could sense it through the dark even though he wasn't Heartless himself. He'd been close enough to never forget.

It was almost a relief when the dark portal he'd been half-expecting for days finally burst skyward, and if it was ten times flashier than it really needed to be, he'd long since accepted that most people who turned to the darkness had no sense of proportion. Part of him wanted to attack while the creator of that portal was still in transit, meet whatever came through with the Keyblade already in mid-swing. It was caution and uncertainty that made him hesitate, wanting a clear shot and a better idea of what they were dealing with, but what stopped him from attacking the moment the stranger stepped through wasn't anything like prudence.

It was that the stranger smelled, just the tiniest bit, like Sephiroth.

The man was tall, human\textemdash mitra, if he was a native, which Riku somehow doubted he was\textemdash his dark hair grown out a little longer than the military cut of his heavy overcoat and well-worn boots would suggest. He might have been Zack's age or a little older, and though he didn't look the least bit uncomfortable in the midst of a battle peppered with magic and the occasional dragon, Riku got the feeling he came from a more tech-heavy world than the last few they'd visited.

Looking the man over narrowly, Riku decided he didn't really bear any resemblance to Sephiroth at all apart from two things: his scent, alien-sharp, without a hint of the now-familiar prickle of mako beneath, and his eyes: cool grey, nearly metallic, pupils slit in a way he'd only seen in one other human face.

``So,'' the man said, stepping away from the portal and lifting a hand with a casual wave, eyes fixed on Riku as the Heartless around them fell back. ``I take it you're what's been closing these worlds. Aren't we a little out of your jurisdiction, boy? Or did you think no one would notice you expanding your territory?''

``Yeah\ldots so I have no idea what you're talking about, but this has nothing to do with territory. I was invited.''

``By these?'' the man asked with an ironically arched brow, glancing at Caedmon, David, Torgal.

``By this world,'' Riku shot back, not caring at the moment who might hear and what conclusions they might draw from it. The oversized portal still bleeding clots of darkness into the air\textemdash and just how strong was this guy to still be powering that thing?\textemdash was going to inspire questions enough, mysterious Fourth Committee or not. He might as well come clean with the rest of it while he was at it; at this point it could hardly hurt.

Grey eyes narrowed, long pupils slitting hair-fine. ``There are no Cetra here.''

Riku snorted though his stomach did a slow roll inside him. How did this guy know anything about the Cetra? And why did he smell like that, his scent acrid and unnatural and familiar as home? ``Keyblade master. Heard of it?''

Abruptly the stranger smiled. ``I'd heard tales of one, it's true. But I thought he was traveling with two friends, not a private guard. Perhaps you're not as impressive as the stories led me to believe.''

Yeah, and he was falling for that one. Right. Like he hadn't pulled his head out of his ass where Sora was concerned ages ago.

``Riku,'' David said suddenly at his back, his voice urgent.

The stranger's smile widened. ``Though I haven't given you much to impress me with, have I?''

``That talisman\textemdash ''

Talisman? Riku's eyes jerked down, puzzled. He hadn't exactly been paying attention to the guy's jewelry, but now that David mentioned it, the crystal that hung around the man's neck was glowing an eerie green under the gloved fingers wrapped around it.

``Perhaps all you need is a bigger dragon.''

It was hard to see exactly what happened next through the flash of light that accompanied it. He thought he saw the guy yank hard on that pendant, snapping the thin chain it hung from to pitch it off into the mob of Heartless that surrounded them. He knew he saw the still-open portal drop amidst a flurry of purposeful motion, which meant that bastard had probably just escaped. It was everything in between that was a muddled mess, because that glowing crystal didn't stay small and contained for long\textemdash not even for as long as it took for it to hit the ground.

One moment there was a flash of glittering gold flying through the air, and in the next instant the ground was shuddering with the impact of something massive, something that stretched sinuously up to a colossal height, towering over the field below. Armored in plates so thick the entire creature looked like a stone golem come to life, the carbon-black dragon spread four spiny wings that glowed blue at the tips, the light growing as the thing threw back its head and roared.

``Marion save us,'' David breathed in the ringing silence that followed. ``It's the Gwayn.''

``The what?''

``Nagapur's Great Remnant. But it's\ldots it's Heartless now, isn't it?''

Riku stared. ``Yeah.''

He couldn't remember now whether David had actually come right out and asked, but he had an answer for the marquis' question now. As far as he was concerned, this world's Remnants probably counted as a fifth race, because whatever the Gwayn had been before, it'd had a heart strong enough to awe even in its absence, and that was good enough for Riku.

Something niggled in the back of his mind\textemdash something about Way to Dawn, Soul Eater, the grafted Keyblade\textemdash but there wasn't time to examine the vague feeling that he was missing the obvious. He'd fought enough dragons to know that a really deep inhale meant you were in really deep trouble, and that your best bet was to get close enough in that it couldn't flame you while keeping far enough away that it couldn't stomp you flat. Only that was flesh-and-blood dragons, and when the Gwayn let loose with a bellowing shriek, it wasn't fire but the unearthly blue light from its wings that seared the air, raw power that lashed the earth and left nothing but charred ruin behind. One sizzling crack, and twenty men were just gone, and those snaking blue whips were falling all over the battlefield, everywhere Riku looked.

Magic exploded against the Gwayn's armor from every side as he watched, but it didn't seem to have any effect; even Hall was giving the thing a nervous look, chewing his lower lip with his hand still outstretched, like he'd already thrown the strongest spell in his arsenal and didn't quite know what to follow it up with. Even Titus wasn't putting a dent in those heavy plates; the thing was just too big.

``What were you saying about colossal Heartless?'' Zack asked distractedly as they edged reluctantly back, not quite willing to retreat but not quite sure where to begin.

``Uh\ldots this is different.''

``Yeah, I thought it might\textemdash fucking Gaia\textemdash ''

He felt the breath whoosh out of him as Zack tackled him bodily, three arms hauling him close to a hard chest while the fourth kept its grip on the hilt of Zack's sword. Even as his body went loose, moving with Zack instead of fighting him, his thoughts blanked out as he realized their hasty tuck and roll wouldn't be fast enough, that nothing was faster than those arcing blue lights without a Haste spell to give it wings. It was that same unthinking panic that had him reaching out instinctively, scrabbling for Zack and the darkness at the same time and falling through, pulling Zack with him\textemdash 

\textemdash and falling back out again, still tucked to Zack's chest as they rolled over and up and\ldots found themselves just a little ways off from where they'd started, far enough to have dodged that searing attack by simple virtue of not being there when it landed.

``What the\textemdash ''

Riku shook his head in answer, but it wasn't because he didn't realize what he'd done. That was one of Sephiroth's tricks\textemdash a short-range teleport without the use of a dark portal\textemdash but it was one Riku had never quite gotten the hang of for all his trying. He could still remember that first conversation they'd had about the spell, Sephiroth congratulating him for blocking a blow from behind and Riku teasing him that he'd been too predictable, made it too easy.

``What would you have done in my place?'' Sephiroth had asked, amused, and\textemdash 

``I would have come in over you and landed on your head.''

Oh. That\ldots actually sounded like a plan.

``Riku?''

Only when he tried it, the darkness he touched felt weak, stretched thin, the distance to the top of that monster too great for the limits of the spell.

``Riku.''

He shook his head again, tightening his jaw. Those blue bolts had stopped falling, but already the Gwayn's bony wings were beginning to flare up again at their tips, a sure sign that it was powering up for another go. As if that wasn't bad enough, all across the plain the trumpets were blaring out a new pattern, one that sounded a lot like Retreat. Decimated, in shocked disarray, the soldiers were pulling back on every front while the Heartless hounded them with mindless determination. Those things didn't care if the Gwayn took them out along with their prey. They only cared that there was a feast to be had right now.

``There's got to be a way,'' he ground out, flinching as a panicked soldier began to scream in a cracking voice nearby, almost instantly cut off. There had to be a way for him to get at that thing, or why was he even here?

He couldn't let it fire off another volley. He just couldn't.

He took one step, another, gathering himself to run.

And then the Keyblade was just there, twin streaks of light and dark, coming at him so fast he lifted his hands without thinking, palms out, grabbing on hard when a hilt smacked into each hand.

Like being stuck in an elevator dropping too fast, the pit of his stomach went briefly cold and weightless as a ripple of some unfamiliar power flowed down through his arms and into his bones, his feet leaving the ground an instant later. He didn't rise far, only a few feet, but it was enough to make him clench his hands on the Keyblade's hilts until his knuckles sang, his eyes wide as he stared down at the empty air beneath his feet.

``Uh\ldots Riku?''

He jerked his eyes up, met Zack's startled stare. He had no idea what his own face looked like, but whatever Zack saw, it softened the man's eyes until there was nothing but raw belief staring back at him.

Whatever the Keyblade had in mind\ldots he could do this. He could.

``Okay,'' Riku said. ``Go.''

There seemed to be no interval between willingness and execution. One moment he was trying to draw Zack's own steadiness around him like armor, and in the next his feet were touching down on the marble-hard back plates of the Gwayn, like the darkness had drawn him in and spit him out again in the space of a breath. Part of him wanted to reel at the sudden translocation, but he forced himself into a sprint instead, the Keyblade thrumming in his hands. He didn't think it was his imagination that there was a crack in the jointed plates just ahead, a ragged starburst of paler gray against ungleaming black, and he hit that spot with all the force he could muster, cautiously encouraged when he heard the thing shriek in response.

He might have worried at that weak point even longer, but already the Remnant was twisting beneath him, trying to throw him off, and with a snap he could feel in the center of his chest\textemdash 

\textemdash he was higher up, perched on a wing-spar as the wind whipped his hair into his face. Fighting blind was nothing new to him, and he'd already seen what he needed to see: the gap in the plates just below where wing joint met shoulder armor. Flipping off the bony spar he'd faded in on, he tucked his legs in close and rolled in midair, leading with both blades when he landed.

He felt the crack all the way up to his shoulders, but his hands remained tight on the hilts when they should have numbed instantly, and it took him a startled moment to realize it wasn't his bones that had broken. One wing of the Gwayn's four drooped over heavily to one side as he glanced warily up, and already the glaring points of blue at that bony pinion's tips were stuttering, fading out. The wind gusted again while he was still staring, and he blinked\textemdash 

\textemdash found himself crouched along the arch of the Remnant's neck, and he pushed himself up, feeling suddenly that he needed to hurry, and as it shook its head like a horse and his feet lost their purchase, he felt the Keyblade lift him up again and realized he was wreathed in shadows and\textemdash 

\textemdash light, glaring across the bone-sharp fan of three wings, shining out of eyes wider than he was tall, and in the instant he realized he was standing square in the center of the thing's muzzle, he felt the unmistakable tug of\textemdash 

\textemdash Go higher.

Only there wasn't anything higher, just open air.

\textemdash Trust us.

He took a deep breath, closed his eyes, and opened himself to the urgency humming through him in voices he almost recognized.

As the shadows lifted him up one final time, he had the strangest sense of his own flesh and blood melting into darkness, into a cool, comforting glow, both of them twining around him so tightly, the fear of losing himself never quite materialized. All sense of Riku and Way to Dawn as separate creatures faded. There was one mind and one drive, their irreplaceable heart and their incomparable sharpness in perfect accord.

They fell like a stone as the three became one, but when the Gwayn tried to snap them out of the air, they were already elsewhere, the soul-sword keening its mockery as it sheared through dark armor, the dawn sword sighing, biting deep. They flickered, all stinging quicksilver feints and shattering lunges to attack, fading out and reappearing too fast to follow. The Gwayn raged, but having cut themselves free of all mortal limits\textemdash consumed our wielder\textemdash you see the danger?\textemdash they were only as weak as their heart.

The Gwayn was in ribbons when it finally gave up its death-scream, darkening the sky as its shadowflesh tore apart in ragged clots and smoky banners. They were the only ones high enough to see the heart that burst from the black, shining like a small moon as it rose and shimmered out, leaving them alone in the upper air.

The struggle that followed was brief. Possessiveness, restraint, amusement tinged with acceptance roiled between them\textemdash and Soul Eater gave in with a mutter, letting the Keyblade wrap around him once more and letting his soul drift free. When they fell again they were Riku and Way to Dawn once more, and Riku was glad of the distinction. Like it or not, the Keyblade had better control than he did at the moment and kept him from breaking his fool neck when they faded one last time to an easy landing on solid ground.

Sagging, exhausted, he dropped to one knee, dimly aware of turning the two blades loose and watching them lift slowly into the air, as if they were as drained as he was. He knew the Heartless were surging back, that someone was standing practically over him\textemdash Zack, his heart told him, which was when he realized his eyes were closed\textemdash but he just couldn't work up the urgency to push himself back to his feet. He listened instead to the deep hum of a wide, heavy sword cutting swift strokes through the air, the low, ominous growl of an angry sovani, and concentrated on breathing, staying upright. Healing magic settled over him like a cool net of cobwebs\textemdash it smelled like Hall\textemdash and he blinked his eyes open dazedly just as Ochs yelled, ``Shadows! Blackout at twelve o'clock!''

Riku stared, trying to get his feet under him and feeling his legs give out before he'd gotten even halfway there. That was\textemdash he'd never even seen that many Shadows in one place, like an oil slick speeding over the ground, heading right for them. He had no magic left in him, wouldn't have enough power for the one truly ground-clearing spell he knew for at least a week, and once those things came up out of the ground, it'd be like being buried under an avalanche in reverse.

When the first tremor hit, it made him grateful he was already down; he didn't have as far to fall. Only the ground beneath him more or less stayed put\textemdash he felt the shivering through the dirt, but no worse than from standing too close to a busy freeway. It was only where the Heartless were that the ground was shifting, the scuffed-bare skin of the earth writhing as if rocks were grinding away just beneath, chewing the Heartless up in granite teeth and spitting out stolen hearts.

It was probably a bad sign that hearing Hall chanting in Ancient Kildean was becoming so common he didn't even hear it anymore, but he did notice the man's cheerful whoop as something thrust an arm through the dirt and started clawing its way to the surface.

``All right! I wasn't sure that'd work!''

``What did you do?'' Zack demanded, sword dipping forgotten in the brief lull that followed.

``Oh, uh\ldots I kind of summoned a Dao,'' Hall said with a shrug, peering sidelong at Zack with a hopeful little grin. ``It's an earth elemental. I mean\ldots it doesn't look like the drawing in the grimoire, but\ldots you know\ldots ''

It was sort of sovani-shaped\textemdash it had the ears, anyway, and the catlike, streamlined body\textemdash but it was hollowed out in the middle, and it only had two arms. The long, reptilian tail almost made up for that. Almost. It seemed to be made out of sandstone and red clay, with claws of sharpened quartz, and it did not like the Heartless at all. Of course, if it was an earth spirit, connected to the planet, that made all the sense in the world.

Closing his eyes again on the sight of Hall beaming like a proud papa, he listened to the silvery call of the trumpets\textemdash new ones, to the north and east\textemdash sounding a charge, and slipped gratefully under to the realization that reinforcements had arrived.


\scenechange


Zack's first clue that everything was not entirely as it should be was the Keyblade fading from sight, leaving ghost trails of darkness and a hissing white glow that curled like smoke into nothing. ``Riku!'' he heard Hall shout, and Zack was already swooping down to catch the body that sagged into his arms even as he turned. Gaia. He'd known Riku was pushing himself too hard, burning too much magic too fast; the fact that Riku hadn't been popping ethers the moment he touched down should have been a giant red flag that he was too wiped to think of it himself.

``Shit,'' Zack muttered, propping Riku against his side with two hands and frantically scanning the battlefield. There were still too many Heartless, even with Hall's Dao ripping through anything that came too close, and they all seemed bent on converging roughly on top of them. ``Can you\textemdash ''

He'd wanted to ask Hall to take Riku and get the hell out of there, but Hall turned at Stiegler's shout just in time to slow a charge headed their way with a well-placed Graviga, and there were so many Jhana between them and the relative safety of the Ramparts, Zack pushed the thought of retreat resolutely from his mind. Against odds like that, it was safer to fight, and just because he hadn't picked his ground didn't mean he wouldn't defend it with everything he had.

Easing Riku down gently, he rose to his feet, planting himself and waiting for the Heartless to come.

There were so many he could actually feel the chill coming off them, and they pressed him so close he thought more than once that he'd be buried under their sheer numbers. Claws slid off the thick padding of his fur, sometimes biting flesh-deep, and once or twice a sword or a warhammer came uncomfortably close, parried at the last moment. Muscle and sinew burned as he wrung every scrap of speed from his body he could, pulling no punches and striking with all the force he could muster. At times he could barely see through the tattered curtain of rent shadowflesh and the flicker of freed hearts, but he kept fighting, giving not one inch of ground. As long as he had Hall at his back, he could stand, and as long as they had Riku between them, they weren't budging.

All the same, there were a lot of Heartless, and even Hall had to run out of magic eventually.

He saw the first stray spark out of the corner of his eye, a flicker of deep red that licked the air like it'd caught some invisible tinder, racing to discover the limits of what it could devour. Arcing over the heads of the Heartless in a wide circle, it hissed and sputtered, dragging a long banner of flame behind it that lowered as the first spark was joined by a second, a third\textemdash 

And then everything was fire. A huge, howling wall of it that spun like a slow cyclone flecked with black ash, the flames so deep Zack couldn't spot a break in their fury. The space the three of them occupied seemed to be the eye of the storm, and though the heat was enough to bake the air desert-dry, the flames didn't touch them, like they'd been warded from the worst of it. Maybe they even had; he wouldn't put it past Hall to know a spell for that, too.

When the conflagration ebbed, the flames sinking into the earth, they were smack in the middle of a great ring of empty space, in the midst of a battlefield now peppered with ice and fire and thunder. ``Holy,'' he heard Hall breathe, unabashedly impressed, which argued against that being one of his.

So did the ``Nice shot, Director,'' coming from a smirking woman with a warhammer propped easily on one shoulder though she looked like the weight alone should be dragging her over to one side. The badly-scarred man on her left was looking at her incredulously, like he couldn't believe how calm she sounded, or else couldn't believe she was handing out compliments in the first place.

``Are you unharmed?'' asked a woman in a short, white lab coat, her dark eyes flicking down to Riku with a worried frown. ``Was he\textemdash '' Her frown deepened, puzzled. ``We thought the Remnant had consumed him.''

Wait. Consumed?

``Uh\ldots I don't think the Keyblade does that. Exactly,'' he amended with a shrug, remembering all at once that at least half of this particular Keyblade was pretty much famous for it.

``It's a Remnant,'' the woman\textemdash the Director?\textemdash said sternly, like a professor determined to drive home a lesson. ``There's always a risk.''

One of Zack's ears flicked back as a commotion rose behind him, running feet and David's startled: ``Haruko?'' The Director glanced past Zack briefly, but her eyes returned to Riku with grave determination, her hands lifting in that familiar pattern, like she held an invisible sphere between them.

``Haruko!'' David snapped, anger and worry tightening his voice. ``Cease at once!''

Apparently a director outranked a marquis, but Zack didn't plan on waiting around to see how that would play out. Even as the weird blue light was flaring up in rings and ribbons around the woman's poised hands, the Keyblade was exploding out of nowhere, whirling in dizzying patterns of blatant threat, its light boiling off like cold-steam, darkness snapping like hungry flames. That Zack was standing right in the center of its defensive display didn't worry him a bit.

When he took a warning step forward, bringing his own sword up at the ready, and the Keyblade advanced with him\ldots he guessed that didn't worry him either.

``Don't even think it, lady,'' he growled as the paired blades wheeled around him in a tight, furious coil. ``This one's spoken for.''

Dark eyes widened as Haruko's stare traveled from the Keyblade to the bright blue ringing her hands, her gaze snapping to Riku in something like shock. She'd maybe figured out that this particular Remnant wasn't bound, but if all that meant to her was that it was free to all comers\textemdash 

When she dropped her hands all at once, she was smiling with a trace of something Zack couldn't quite interpret: amused, like she knew a secret everyone else thought her ignorant of, and oddly grateful, like she'd just gotten good news when she'd lost hope of any news at all.

``Of course,'' she said, inclining her head with the dignity of a duchess at the very least, and promptly turned her back, walking unhurriedly away.

``Well, that made fuck-all sense,'' the scarred man grumbled, glaring at his companion when she elbowed him in the side.

``Nora,'' David greeted the woman warmly. ``And Loki, I see.''

``Can you pretend you didn't?'' the man muttered, not quite looking at the marquis and missing David's swiftly-hidden smile.

``You've been holding out on us,'' Nora accused, eyes narrowed. ``Where'd you get the Remnant, and who the hell are these guys?''

``It's a long story,'' David warned.

Nora scoffed. ``So? Let's wrap this shit up, then. And don't even think about ducking out on us.''

``I wouldn't dream of it,'' David promised, more fondly than Zack would have expected.

Nora just glared like he'd personally insulted her and jerked her chin up sharply. ``Right. See you in fifteen, marquis; don't be late.''

``Doesn't ask for much, does she?'' Loki muttered as Nora stalked away, but he followed with a shrug, axe in hand, his light step at odds with his resigned tone.

As overconfident as her ultimatum had been, when it came to the final outcome, Zack was with Nora one hundred percent of the way. Losing wasn't even an option, not anymore.

If the reinforcements pouring onto the battlefield and the rallying of the troops they were relieving were any indication, this battle was already won.


\scenechange


Torgal was beset by Jhana Heartless on every side when he felt a space open up suddenly at his back, one that was just as suddenly filled by whirling blades and a long-familiar scent.

``It took you long enough,'' Allan huffed, as if Torgal had been the one to come to him\textemdash which, he had to admit, was one interpretation of the facts. Trust Allan to see it as the only interpretation.

``We were unavoidably detained,'' Torgal explained dryly, not surprised in the least by Allan's unimpressed sniff.

``And yet you found time to pick up another mitra with a strange Remnant,'' Allan grumbled between fending off a sword-thrust meant for Torgal's side and shredding an Imp that got too close. ``Is your lord starting a collection?''

``It's doubtful. This one has a sovani lieutenant.''

That shut Allan up for all of two seconds. ``Hmph. At least he shows good taste.''

``So does his lieutenant.''

Though he'd kept his voice perfectly uninflected, he and Allan had known each other for two centuries; there was no possible way Allan could mistake his meaning.

``Lugh wept,'' Allan snarled and spent the next ten minutes cursing, of which Torgal only caught about half. The words ``shameless'' and ``Caedmon'' and ``idiots'' figured prominently, though the name ``Emma'' never once touched his tongue.

Torgal was very careful to keep his back to Allan so as not to shock his old friend with his grin.


\scenechange


When Titus saw Zack coming his way with a too-familiar body cradled in his upper pair of arms, he didn't even try to contain the icy dread that pooled in his gut. A heartbeat later, he was gusting out a sigh of relief; Zack's step was too light and too relaxed for there to be anything permanently wrong, and Hall, tagging along at Zack's side, wasn't lighting the air up Curaga-green. So that was two points in favor of another lecture on the evils of playing hero, just as soon as Riku woke up enough to ignore the whole speech properly.

``He okay?'' Titus asked anyway as Zack drew near. It was strange seeing Riku that quiet, his lanky form utterly lax and his head tucked to Zack's shoulder, way too pale in all that black. The Riku he knew was always moving, sharp eyes and sharper mind never still for long.

``He just hit burn-out,'' Zack assured him, in a tone that promised Riku would be hearing about that as well, in great detail. ``We got a few ethers in him, but he's still going to be out for a while. Thought we'd take him back to the Ramparts just in case.''

Titus nodded. He thought they'd gotten all of the Heartless in this area, but that didn't mean there weren't other pockets elsewhere, maybe even nearby. Better to be safe than sorry.

``Have you seen Giese and Haxby?'' Zack asked worriedly, shifting Riku unconsciously closer. ``I've run into the others, but\textemdash ''

``They're fine,'' Titus promised, keeping his eyes on Zack's but not missing the careful way Zack cradled what he held, the protective splay of his hands. ``They were guarding the healers, so you'll probably meet them back at the walls.''

``Good,'' Zack said, his relief echoed by Hall, both of them looking like a weight had just dropped off their shoulders. ``Uh\textemdash if you see the marquis\textemdash ''

``I'll tell him where to find you.''

``Thanks, big guy,'' Zack said with a sovani grin, and maybe Riku had a point\textemdash even if it didn't look a thing like Zack's usual beaming smile, it was still Zack all the way through.

All the same, that low curl of dread in the pit of his stomach didn't entirely leave him as he watched Zack carry Riku off the field. Maybe it was just Zack's nature to set his heart on the impossible, and somehow he just never learned. It'd be one thing if he were just bringing home a new boyfriend to Cloud and Aeris; they'd probably understand. Hell, they might even reward him. Only Riku already had someone, wasn't actually from their world for all their forgetting of that fact, was way too smart about everything else to be so clueless when it came to Zack. Maybe Riku just figured it was Sephiroth Zack was really seeing\ldots and that was another can of worms Titus was in no hurry to see opened.

Even if Sephiroth didn't kill them all outright for desertion before sanity kicked back in\textemdash and he could read between the lines just fine; he knew exactly what worried Riku most about their homecoming\textemdash what Sephiroth might do to Zack for putting the moves on someone Sephiroth considered his didn't bear thinking about.

So maybe he'd better have that talk with Zack after all. Soon. Probably. Unless Riku confused him all over again and put him back at square one.

For someone who didn't exactly look to be in the market for a new boyfriend, Riku seemed pretty attached to the one he'd picked up without noticing, and that was a fact.


\scenechange


Waking was a slow process, Riku's awareness of the world coming back in increments: the bedroll under him discovered by a twist of his shoulders, the rough blanket thrown over him by the twitch of a foot. The uncoordinated flailing of one arm dragged his fingertips across seamed, dusty stone, not dirt and grass, and the dim, friendly shadows when he forced his eyes open told him he was in a tent long before the canvas stretched overhead made sense to his half-asleep brain.

He thought he made some sort of noise then, not quite a grumble or a groan, but he might have dreamed that. Or maybe he hadn't\textemdash someone ducked through the tent flap instants later as if summoned, and he blinked in sleepy confusion until Zack's darker-than-usual face came clear.

Right. Sovani. He remembered that bit.

``How are you feeling?'' Zack asked, easing in the rest of the way once he realized Riku was awake and tracking him properly, crouching down at his side.

``Like I've been beaten with rocks,'' Riku replied frankly, struggling up into a sitting position all the same. The steadying hand at his back helped. ``Are we back at the Ramparts? Is everybody okay?''

``Everyone's fine\textemdash which is more than you can say. What happened, anyway?'' Zack asked, cocking his head. ``Did you hit some new Limit or something?''

``Not exactly,'' Riku said, rubbing the back of his neck and wincing at the tightness there. He didn't know how long he'd been out, but things were still a little fuzzy. All he really remembered was the Keyblade\textemdash and Soul Eater; the two had been separate but connected since they first entered this world\textemdash and him, joining together. Becoming one. ``That\ldots oh, man,'' he breathed, going still as it really sank in. ``I think I just pulled off a Trinity Limit with my own Keyblade.'' And then he was grinning fit to break his face. ``Sora's going to freak.''

``I might join him,'' Zack muttered, but he was smiling all the same. ``So\ldots Trinity Limit? I'm guessing that's a Limit that takes three\ldots er, people?''

``People,'' Riku agreed with a firm nod, ``exactly. It can't just be any three, though; you have to have a pretty strong connection. I've been able to do it with Sora and Kairi before, but\ldots it wasn't anything like this.''

``Folks were saying it looked like you got consumed by your Remnant,'' Zack offered, noncommittal.

``Yeah, I remember them warning me about that. Soul Eater and the Keyblade, I mean. Obviously they gave me back,'' he said with a shrug. ``Why? What did I look like?''

``Well, you were pretty hard to see, actually\textemdash you were moving pretty fast. But\ldots I thought you still looked like you, actually. Just maybe not flesh-and-blood you. I couldn't quite tell if you were metal or magic like that. Maybe a little of both.''

``Huh.'' So that feeling he'd had of melting into Way to Dawn\textemdash from the sound of it, he literally had. ``If it's any consolation, I don't think I'm going to be able to do that anywhere else,'' he offered, reading the stiffness of Zack's ears and the tight worry buried in the back of his eyes with an ease that only dimly struck him as strange. ``I mean, the Keyblade's\ldots it's always alive, and\ldots you know. Aware.'' And at least half of it was damned possessive, which was never not going to leave him torn between laughter and sheer gratitude. ``But\ldots well, it's usually the Keyblade. Singular.''

``So\ldots no more weird transformations?''

Riku grinned. ``Sorry, Zack. Can't promise you that. But if I hit any weird new Limits, I'll try and let you know in advance.''

``Good plan,'' Zack agreed, relaxing minutely and finally easing himself down from his ready crouch to sit cross-legged at Riku's knee. ``So\ldots Sora and Kairi, huh? You've never done one of those trinity things with Sephiroth?''

Trying and failing to think of a single thing that could convince Sephiroth to fight alongside any of Riku's friends, even now that they were all mostly on good terms with each other, Riku shook his head. ``Uh\ldots no. In fact, my brain hurts now.''

Zack snorted.

``No, really. That's just\ldots wrong.'' Not least of which because Mickey was the only one he could even see going for it, and that\textemdash right. He was never going to be able to look Mickey in the face again. ``Uh\ldots maybe you all have to have the same kind of connection?''

Zack was kindly trying not to laugh at Riku's attempts to not go cross-eyed at the very thought\textemdash at least until Riku balled up a fist and smacked him on the shoulder, whereupon Zack lost it quite spectacularly, falling over sideways and holding on to his stomach.

``I hate you for putting that in my head,'' Riku informed him, only for Zack to hold up a random hand, like the man was begging him to stop. ``Oh, yeah. Laugh now. But if there's a way to break your brain, I will find it, and Aeris will take pictures.''

He got a strange sort of hooting sound for that, but Zack did eventually get himself back under control, wiping at his eyes as he sat up, still leaning back on one hand. ``Oh, man. So who were you thinking about, then?''

``Not telling,'' Riku muttered, rolling his eyes. ``Bad enough only one of us is traumatized.''

``Aw, c'mon.''

``No way.''

``Is he cute?''

``He's a mouse!'' he blurted out, not because the species thing really bothered him, but\textemdash it was Mickey. It was like asking him if he thought Aeris was pretty. ``Oh\ldots okay, that was sneaky,'' he grumbled when he realized what he'd given away, casting Zack a reproachful glare.

Zack looked so much like a smug feline, Riku was half surprised the man didn't trill at him. It was weirdly adorable.

``Hey, you're the one who thinks I don't have a poker face.''

``I'll bear that in mind.''

Zack laughed at him, again\textemdash or was it still?\textemdash and reached out to scruffle his hair.

For reasons Riku didn't even want to examine, he sat there and took it as Zack's teasing grin settled into a contented little smile.

``You know we're going to have to push even harder to get home now,'' Riku offered as the silence stretched, warm and comfortable, between them.

``Because of that guy with the portal?'' Zack asked, leaning back again.

``Yeah. Did\ldots he smell familiar to you, too?''

Zack frowned. ``You know\ldots this is going to sound crazy\textemdash I mean, it's been years, so maybe my nose is playing tricks on me, but\textemdash ''

``He smelled like Sephiroth,'' Riku said flatly, stopping Zack's rambling in its tracks. ``Not the way you guys do\textemdash I didn't smell any mako on him\textemdash but\ldots there's that\ldots other thing that makes Sephiroth different.''

``Jenova,'' Zack offered, a faint line etching itself between his brows. ``You think maybe Hojo tried to make another version of Sephiroth, one without the mako?''

``I don't know. Maybe. Have you ever seen him before?''

``No, but that doesn't mean anything,'' Zack admitted with a shrug. ``Most of Hojo's projects were top secret, one way or the other. I don't think even the king knew everything that guy got up to.''

``Great. Because there's another possibility, you know. I mean\ldots I don't know that much about the Jenova Project myself; Sephiroth doesn't like to talk about it much.''

``I don't blame him,'' Zack said, and though Riku looked at him sharply, there was nothing but honest empathy in Zack's eyes, a worry and acceptance Sephiroth must have depended on like the air itself. No matter how everything else played out, Riku could be nothing but relieved to be taking this man back home where he was so desperately needed.

``Right. Well, from what I understand, Jenova isn't from your world. She crashed there.''

``You mean like an actual alien?'' Zack asked, incredulous, sitting bolt upright.

Riku shrugged. ``Either that or someone got a summon very badly wrong. The thing is\ldots what if, wherever she's from, there's more like her?''

Zack opened his mouth, closed it again. ``Shit.''

``Yeah. We really need to get home, Zack. Fast.''

``All right,'' Zack said, ``I hear you.'' And hopefully that meant he wouldn't give Riku too much grief if he pushed himself a little harder to get them all back there. ``But first we've got to deal with this planet, right? So you'd better get some rest,'' he added, taking Riku's shoulder briefly before climbing to his feet. ``I'll let you know when we're ready to move.''

``Yeah,'' Riku said, ``okay.''

It was all the eloquence he could muster as he finally put a name to the totally inappropriate warmth that lit in the pit of his stomach at Zack's touch.


\scenechange


The march from the Heroic Ramparts to the city of Elysion took a week all told, and that was after two solid days of convalescence, camped out on the Plain of Luhang while the healers went to work and companies slowly formed up again, too few stragglers coming in from the hills. It didn't feel much like a victory, but Zack knew that sometimes battles didn't. Those two days were quiet, and the only good thing other than the welcome dearth of Heartless was that nobody was in too big of a hurry to quiz Riku on what he'd done to that oversized Heartless. David kept Rush's crazy friends in check, Haruko stalled the rest of the Academy with the skill of a diplomat, and the rest of the army kept their heads down and their mouths shut, too grateful to be alive to look a gift chocobo in the mouth.

Riku slept all of the rest of that first night and partway through the next morning, and nobody gave Zack any grief for standing guard the entire time. They saved that for after Riku woke up. If he heard one more 'wark' hidden in a badly-faked cough, a few comedians of his acquaintance were going to wake up dyed yellow with feathers stuck in their hair\ldots but maybe he'd wait until he figured out why the ``mama chocobo'' routine was making Riku blush, too.

As for their uninvited visitor from the day of the battle, they heard not one peep on that front either, but Zack quietly made the rounds, filling everyone in and collecting what theories and half-remembered bits of overheard conversations he could. It didn't help that Hojo had been a close-mouthed bastard, unlike the king's apprentices. If the SOLDIER Project had been Xehanort's baby, random strangers in coffee shops could probably have recited back its whole history to them verbatim.

Gaia, that guy loved to talk.

Hojo, though? That was a different story.

Though there were rarely any dead in need of transport after a battle with the Heartless, there were always plenty of wounded. Some things even Curaga couldn't fix, or at least not all at once, and the casualty train had the entire combined army for an honor guard as they made their slow way back to Ghor. That would be the last stop for some\textemdash the old duke and his men, the wounded who'd never recover enough to limp their tired way home\textemdash though Athlum and the Academy forces planned to continue on to Elysion together.

The Silver Falcons left them at Ghor as well, splitting up to go back to the assignments they'd briefly abandoned, promising to keep a sharp eye out for Heartless in case they began to mass again. This world was still unlocked, after all, though Zack doubted it would be for long now that Riku was recovered enough to start worrying over it again.

``So? Where's your next stop?'' Zack asked Caedmon that last afternoon in Ghor, standing in the shadows at the edge of a ruined courtyard and grinning openly as yet another of Riku's hand-to-hand lessons ended in laughter and underhanded trickery. Underhanded trickery Riku was actually learning from.

Titus was a genius.

``Nagapur, actually,'' Caedmon replied, smiling a little at Zack's dumbfounded look. ``There wasn't time for too thorough a search, but I've heard that there were secret passages out of the city. I know it's foolish to hope for survivors, but if any did, they may not realize it's safe to return.''

``Oh, man. Good luck,'' Zack offered, trying not to shudder. Having wandered around one abandoned city recently, the idea of taking a stroll around another just gave him the creeps.

He was about to explain as much to Caedmon's curious ear-tilt when a peal of laughter distracted him. Glancing out at the courtyard, lit up by the early summer sun striking off the pale, cracked stone, he found Riku getting a hair-scruffling from Titus of all people, who frankly looked like an alien anthropologist putting theory into practice, patting almost dubiously at the top of Riku's head. Riku didn't seem to mind\textemdash it looked like that was why he was laughing, in fact\textemdash and Zack told himself firmly that it was utterly ridiculous to feel wistful over someone else not only pulling off his trademark move but getting Riku to laugh like that in the process.

``You should tell him,'' Caedmon said out of the blue\textemdash and it most certainly was a surprise, because Zack had no idea what Caedmon was talking about. Or how he'd known. Maybe it was the pheromones. Oh Gaia, he hoped it was the pheromones that had given him away, because if he'd been so obvious even near-strangers were picking up on his completely pathetic crush, it was probably about time for Titus to break him in half or something. The big guy had practically promised, after all; there was no way he'd let Zack down like that.

``Yeah, uh\ldots not a good idea,'' he muttered back, glancing over with a rueful shrug. ``He's already got somebody. My best friend, actually.''

Ears drooping a little in commiseration, Caedmon solemnly offered, ``I'm sorry.''

``It's fine. We're fine,'' he added with something like a smile. ``I'm just glad they've got each other\ldots you know?''

``Yes,'' Caedmon said, and somehow Zack just knew he was thinking about Rush, and David, the two of them together. ``I do indeed.''

The quiet, reflective sigh of Caedmon's ghost\textemdash still sad but not half as alone now that David had been working on the man\textemdash said it all.


\scenechange


Irina had been waiting in Elysion for days by the time the Athlumian army finally arrived, and with it David and Riku. She'd had time to explore the Academy, watching her father puttering with his experiments as he tried to distract himself from the waiting, and she pretended not to notice the runners that came and went, bringing news of Nagapur she wasn't supposed to know about. Her mother had been in Nagapur just before the city was cut off, combing through the castle library for half-forgotten texts. For all anyone knew, she'd been there when the city had fallen.

She couldn't think about that now, or anything but the cryptic message Riku had passed along through David: if he had a key that could unlock any door, could she show him the door when she couldn't see it herself?

After days of haunting the Temple of the Ark, empty now of its Remnant but as clear a marker as a trail of stones in the woods, she was all that convinced that she could. She couldn't feel the other Remnants yet, but with Riku's strength to boost her own, she would. And if there was a way to bring her brother home, she'd find it.

It was the thunderous roar of the crowds below that alerted her to the fact that the waiting was over. Running out into the bright sunlight of the Assembly Plaza, she peered over the edge of the terrace to see a long line of soldiers filing up the snaking streets in perfect parade rank, the banners of Athlum and the Academy unfurled side by side. Unlike the last army to march through Elysion, Athlum was being hailed as a welcome guest, the forces of the Academy as returning heroes.

She hoped there wouldn't be speeches. As much as she understood the necessity of politics, she could hardly contain herself from running down to meet them and kidnapping Riku at knifepoint if necessary. She had the distinct impression he'd make it look good for her if it meant he got to skip the speeches too.

She needn't have worried. It wasn't long at all before she saw the bright gold of David's hair in the crowd, coming up the last few steeply-angled streets below the Plaza. He had Emmy with him, and Pagus, and Riku with the black sovani she'd never yet seen five steps from his side, and that yama that made even hulking Zuido look delicate.

``Irina?'' she heard at her back and turned with a smile as her father touched her shoulder. His eyes were shadowed with worry, but he kept his expression hopeful as he asked, ``Are you ready?''

She nodded, her throat too tight to speak. While there might be nothing she could do to help her mother\textemdash and she didn't believe that for an instant, but one thing at a time\textemdash her brother was coming back today if she had to go and fetch him herself.

She met them in the temple itself, pretending not to notice that David looked paler than usual, practically thrumming with nervous anticipation. If she wanted her brother back, what David wanted was just as simple and just as deeply felt, and she had to resist the urge to mortify them both with a hug of support. A purely sisterly hug, because her embarrassing crush on the marquis had lasted exactly as long as it had taken her to realize that Rush was completely gone on the man, and that the feeling was mutual.

``Miss Irina?'' David asked\textemdash and practically siblings or not, she was never going to get tired of hearing him call her that.

``I'm ready,'' she said and turned to Riku.

Smiling reassuringly, Riku came to meet her at the steps that had once led down to the platform of the Ark Remnant, what had once been the only known method of traveling to the Sacred Lands. She'd heard the reports of what he'd done the week before\textemdash the official reports, not the rumors flying thick and fast through the city below\textemdash but he looked the same as he had when she first met him, like he'd never been consumed, or like his Remnant had been careful enough with him to keep him whole, even without a binding to compel it. The confidence in his step remained unbroken, and there was no hesitation in him when he held out his hand, calling his Remnant to him.

She could feel its satisfaction humming through the air when it appeared, its joy in being called and its sheer contentment as it settled into Riku's hand, both blades snapping together once more to form a whole. It was letting her feel all that, she was sure of it, but that didn't make it any less real. Wherever its wielder was, that was exactly where the Keyblade wanted most to be, and it was that, that sense of home freely given, that she needed to reach for now.

``So,'' Riku said, his voice soft in the hush of the temple. ``Straight overhead, huh?'' He arched a brow, one side of his mouth quirking up at the corner, and before nervousness could flood back in and paralyze her, she found herself smiling confidently back.

``That's right,'' she said. So what if the Remnant Elysion was gone? Maybe she just couldn't see it. Maybe she didn't even need it, just a place to focus and enough will to make it happen.

``Put your hands on mine,'' Riku suggested, hefting the Keyblade up between them, the tips of the paired blades pointing straight up at the round hole in the temple's roof where the Ark's power used to flow when it sent its passengers to the Sacred Lands.

Riku's hands were warm under hers as she mirrored his grip on the blade, waiting for his nod before she let her own power flow between them.

The blue light that rose from her skin hissed faintly as it formed into its familiar sphere, only to collapse, drawn suddenly into long spirals that wound up the length of the Keyblade and down both her arms and Riku's. Far from worried, Riku closed his eyes, centering himself visibly, and as the shifting ribbons of Irina's power reached the twinned points of Riku's Keyblade, a thick bolt of mingled shadows and light shot straight up into the heavens, its core the brilliant blue of Irina's magick.

Squeezing her own eyes closed as the glow became a glare, she gripped Riku's hands more tightly, nearly praying as she reached out with everything she had. Please, she tried to send, straining hard after that snap of connection that said Remnants to her, only this time trying to anchor, not to bind. Please. Come back to us. Come home.

There was\ldots something: a click like a key turning in a lock, only she didn't hear it with her ears. All she knew for certain in that very moment was that the sense of emptiness that had nagged at her for half a year had just been suddenly filled, the lonely places in the back of her mind overflowing with a low, wordless hum as joyous at the renewed connection as Riku's Keyblade had been to be called. They were there again\textemdash the Remnants, close enough she could almost reach out and touch, and something\textemdash 

Something was coming.

When her eyes snapped open, she found Riku had done the same, alarm the twin of her own staring back from wide eyes. They really ought to be running now, but before the panicked thought could quite make it all the way down to her feet, Riku had torn his hands loose from under hers, the Keyblade instantly vanishing as he scooped her up like she weighed nothing at all and bolted for the stairs.

He was almost too late even so. Over his shoulder, she saw a column of blinding white touch down, wider than the eyehole set into the roof, or what was left of the roof after ancient stone was boiled away to nothing. Eyes winced shut against the light, she only felt the four arms that came around them both and pulled, yanking Riku off his feet, sending all three of them tumbling down in a dizzying roll that left her breathless but unflattened. It was the black sovani\textemdash Zack\textemdash who climbed off of them with a sheepish grin, hauling them back to their feet with a hand held out to each. She tried to thank him\textemdash she had no clue what she actually said, but she hoped it was appropriately grateful\textemdash but she couldn't take her eyes off that hollow in the floor where she'd stood just moments ago, at the light roaring down from the heavens that cut out with one final burst that nearly blinded her.

Peeling her eyes open and blinking hard against the dark spots that danced in her vision, she stared and felt her breath go still in her chest.

Where there'd been bare, polished stone before, the sunken disk of the Ark Remnant now gleamed like new, previously-hidden glyphs along its edges glowing white-hot, only just beginning to fade as the power that had animated it began to ebb away. Though she couldn't drag her eyes up to check, she knew with a certainty that left her shaken that if she were to look into the heavens right now, she'd find the skies over Elysion occupied once more, the delicate, spiraling cloud of the Elysion Remnant floating serenely overhead. There might be others elsewhere; she neither knew nor cared.

Braced down on one knee in the center of the Ark, her brother was staring up at her with a dawning smile of incredulous joy.

``Rush,'' she breathed tremulously, and as fast as Riku had moved before, Rush was faster, blurring green at the edges as he raced up the steps and nearly tackled her with a hug.

``Sis!'' he said into her hair, and she decided with a squeaking laugh that she didn't really need air in her lungs if it meant Rush was there to squish the stuffing out of her. He let up only a little when she squeezed him fiercely back, and only because their father distracted him by wrapping them both up in a hug, his grizzled head bent to rest against both of theirs.

``Son,'' he said, voice choked with relief. ``Welcome home.''

``Dad,'' Rush said, and Irina was not going to hear the gratitude in his voice, like he'd actually wondered for even one instant whether their father still considered him a son. The only one who hadn't known all along that Rush was a Remnant was Rush himself, and he was theirs, her brother and John Sykes' son, and that wasn't ever going to change.

It was right about then that he noticed David standing off to the side, watching them with a warm, wistful look on his face, like he would have toppled thrones for a hug of his own but was trying to do the noble thing and not intrude. Like the way Rush lit up incandescent at the sight of him wasn't practically an engraved invitation.

``Dave!''

She sort of expected her brother to make a lunge for the poor man\textemdash Rush wasn't exactly shy\textemdash until she caught that flicker of doubt in his eyes for a second time, like he was no longer quite certain of his welcome.

``Rush\ldots ''

That was as far as David got before Emmy pushed him, and Dad dragged him over the rest of the way, and Irina made room with a contented sigh as Rush tried to hug all three of them at the same time. David only stiffened for an instant\textemdash surprised, not unwilling\textemdash before he relaxed with a soft huff of laughter and gave as good as he got.

That was all she remembered of the next few minutes before Rush lifted his head, looked around curiously, and asked, ``Where's Mom?''

It was awful how quiet everything got after that, and though David looked like he was steeling himself to spare the others the unpleasant duty of explaining, even Irina wasn't expecting the gentle cough from the entrance to the temple, one with the faintest hint of a growl underneath.

``Rush?''

She didn't care how stupid it was; there were already tears streaking her cheeks before she even turned and saw her mother standing by the doorway with both hands pressed to her mouth, Caedmon a self-effacing shadow at Marina's back, all but devouring Rush with eyes gone warm and soft.

The next few hours were a blur of Loki cursing at them and Nora thumping Rush soundly for disappearing in the first place, Haruko's soft congratulations on his return and Blocter nearly flattening the lot of them with his enthusiastic hugs. Even Allan stopped by to insult Rush in person, which Torgal assured them meant he secretly cared.

``Uh, yeah, we've met,'' Rush reminded him, which Torgal seemed to find amusing.

It was early evening before Rush managed to sneak away long enough to track down Riku, with Irina tagging along since she didn't intend to let her idiot brother out of her sight unless it was to turn him over to David. Which wasn't anything she wanted to think about too closely, because eww, and also embarrassing. All the same, her plan sounded like a good one, and she was sticking to it.

She supposed it wasn't all that surprising that Riku and his friends had made themselves at home in the nearest bar, soldiers being soldiers. They'd commandeered the second floor of the Heavenly Terrace, pushing tables up close so they could all sit together, and she was struck all at once by how much like a family they looked, content in each others' presence and perfectly at home, even this far away from home.

They shuffled over amiably enough when Rush and Irina joined him, but she noticed that Zack didn't give up his spot on Riku's right hand, and that nobody seemed to expect him to.

``So, hey,'' Rush said, sticking out a hand with an enormous grin, perfectly sincere. ``Sorry I didn't say so earlier, but thanks.''

``No problem,'' Riku replied, clasping Rush's hand with a bemused little smile and an arched brow that reminded Irina oddly of David. ``I didn't do much, though; you can thank your sister that it worked.''

``You freed Elysion, though,'' Rush said with a shrug, even as he was tossing Irina yet another grateful smile. ``If you hadn't turned her loose\textemdash ''

``Wait,'' Riku said, frowning. ``You lost me. I know the Remnant world was locked, but\textemdash ''

``Huh,'' Rush said thoughtfully, like the pieces of a puzzle were just beginning to fit. ``I guess that might have been it. Things look sort of\ldots different over there,'' he explained, hunching a shoulder with a sheepish smile. ``Or maybe that was just me. All I know is that we were stuck while Elysion was all chained up like that, but once you busted her out, we could hear Sis calling us back. So, well, since the door was open and all\ldots ''

``Here you are,'' Riku summed up with a smile.

``Yup,'' Rush said, grinning again. ``So like I said\textemdash thanks. For a while there, we didn't think we'd ever find a way back out. Even when that guy came through that weird portal thing\textemdash ''

``He was there?'' Zack demanded, ears perking up stiff and straight.

``Yeah. And he brought these creatures with him\textemdash the older Remnants called them Heartless. I guess you saw them here too, huh?''

``A few,'' the big yama said wryly, shaking his head.

``Right. Well, they took the Gwayn totally by surprise, and I don't know where that guy got the tablet from, but\textemdash ''

``Someone had a tablet?'' it was Irina's turn to interrupt, staring at Rush incredulously. ``Like the one Mom made?''

``Yeah,'' Rush said heavily. ``That guy turned the Gwayn into a talisman, just like Mom did with Cyclops,'' he said, touching the crystal hung around his neck as if to reassure himself it was still there\textemdash or to reassure Cyclops after bringing the subject up at all.

``Wait,'' the black sovani growled, eyeing Rush warily. ``There's a Remnant in that thing?''

``Hey, don't worry,'' Rush said quickly, ``Cyclops is cool. I've had him for a while now, and he didn't want to get left behind\textemdash no monsters to fight over there,'' he explained with a shrug. ``He says it's boring.''

One of Zack's ears twitched, but all he said was, ``I guess it would be.''

``Never mind that,'' Riku broke in impatiently. ``That guy\textemdash the one that took out the Gwayn. Can you tell us anything more about him? His name, what he was?''

``Huh. So you didn't think he was a mitra either,'' Rush said, eyeing Riku speculatively. ``The Conqueror said that too.''

``The Conqueror?'' one of the other soldiers asked; she hadn't caught his name. ``Wasn't that guy bad news?''

``He's\ldots complicated,'' Rush said after a moment of gnawing his lower lip, shrugging helplessly at the skeptical looks he was getting. ``It's like\ldots as bad as it was when we couldn't get back here, I guess it was just as bad before, when they couldn't get back home. Like\ldots if Elysion was locked shut before you came, she was locked open before then, only it was a one-way street. They could come here, but then they couldn't go back. Now that there's options, the Conqueror is actually kind of mellow. In a\ldots grumpy\ldots broodingly homicidal kind of way,'' Rush finished with a cough.

Riku and his guard glanced at each other, but it was the big yama who spoke for them all with a shrug. ``Sounds like Sephiroth at budget time.''

``Yeah? Well, he's the reason we only lost the Gwayn,'' Rush said, trying to smile though his mouth kept twisting unhappily, dwelling on the losses taken by both their worlds. ``The Conqueror blew those Heartless things to smithereens, and the guy that brought them didn't stick around to be next. I wish I did know more about him,'' Rush added, a thread of hot anger running through his voice, ``but the Conqueror couldn't tell me much. Just that he wasn't fully mitra and that he didn't feel\ldots alone. Inside his head.''

``Okay, that's creepy,'' Zack announced. Riku only looked thoughtful.

``Not alone, huh?'' He quirked a wry half-smile that didn't quite reach eyes gone solemn and tight. ``Thanks. That actually tells me a lot.''

Irina hoped he'd share. If there was someone out there who could capture a Remnant like the Gwayn, then it was up to her to keep her brother safe.


\scenechange


The trip back to Athlum took days more, and though the sense of urgency was different, Riku still felt the press of time. If there was someone out there capable of controlling the Heartless\textemdash someone infected with the Jenova virus, who hadn't been lucky enough to burn her out with his own innate darkness\textemdash then he couldn't afford to drag his feet. Radiant Garden needed its defenders\textemdash King Mickey needed to be warned\textemdash and Sephiroth\ldots Sephiroth needed to hear from him what was sure to be coming, before it became an unpleasant surprise.

Assuming he could look Sephiroth in the eye again, considering he'd gone and developed a thing for the man's best friend.

He did get that Gaia wasn't Destiny Island. Two people hooking up with a third wasn't even all that weird there, and two guys together? That was nothing. Under any normal circumstance\textemdash normal for Gaia, anyway\textemdash Riku falling for Zack could conceivably go a long way toward making everybody happy. Only Sephiroth wasn't normal, even now, and Riku would have to be a complete asshole to take Sephiroth enough for granted to forget that fact.

And anyway\ldots Zack\textemdash who didn't have Riku's cultural hangups or an ounce of shame in his entire body\textemdash was pretty obviously not interested, or he'd have said something by now\ldots right?

Which was why Riku had ducked out on the man pretty much the moment they got back to Castle Athlum, claiming he was looking for the Keyhole but in reality to get his head on straight.

It was taking a bit longer than he'd thought.

Following no particular path and wandering where his feet led him, he took a long corridor where the air smelled fresher and found himself walking out into a walled garden, filled with ornamental trees and a riot of flowers, and a wide, quiet fountain that gave back shards of sunlight when the breeze ruffled the glassy stillness of the water. Taking a seat on its edge, he breathed out a long, slow sigh. It was pretty ridiculous to be hung up on something like this when he had more important things to be worrying about. He just had to focus on the things that really mattered, like getting everybody back safe, and not dying, and spreading the word before they were up to their necks in Heartless and Jenova-spawn. Where there was one, after all, there were bound to be more. Sephiroth's relentless territorialism aside.

He was pretty sure that particular personality trait could be laid squarely at the feet of the Dark, because part of Riku was\ldots actually pretty convinced that trait was a desirable one that ought to be rewarded as often as possible. And if that wasn't his own darkness talking, he really didn't want to know.

The scuff of a boot on stone made him look up, but while he'd been expecting Zack, he wasn't entirely disappointed to see Rush wandering in instead. The fact that he was disappointed when he'd all but fled the man was just more proof that he was an idiot who needed to stop worrying about things he had no hope of changing. Once they got back to Radiant Garden\textemdash that would be an excellent time to start worrying. Until then? Not so much.

Having a distraction like Rush come along out of nowhere clearly meant the universe agreed.

``Hey,'' Rush greeted as he ambled over and dropped down beside Riku, grinning like he didn't have a care in the world. ``I heard you were looking for that Keyhole thing. Any luck finding it?''

``Not yet,'' Riku admitted, feeling a twinge of guilt because he hadn't exactly been looking. ``What about you? Settling in okay?''

``Oh, yeah. Dave's been great,'' Rush said with an easy shrug, though the way his eyes slid away while his cheeks heated up made Riku bite the inside of his cheek to keep from smirking outright. ``He's pretty good at keeping secrets under wraps,'' Rush added, eyes flicking back to Riku as his expression went less gooey and more earnest. ``Even when they're not really secrets anymore.''

``That's good to know.'' Because while it was anyone's guess whether worlds this far out would actually remember them after they left, if they did, at least the damage he might have caused by clueing them in to the existence of other worlds might still be mitigated.

``So, uh\ldots I finally got the whole story out of Dave about what happened at the Ramparts, by the way.''

``You mean the Gwayn,'' Riku said levelly, having wondered when this would come up. ``I'm sorry about that. Were you two friends?''

Rush stared at him for a long moment, apparently lost for words, before shaking his head with a faintly incredulous laugh. ``Man. I keep forgetting you're not from around here and expecting it to wear off.''

``Huh?''

Rush's grin was lopsided, self-deprecating. ``You're really not bugged by the Remnant thing, are you?''

Oh. So that was it.

Riku shrugged. ``One of my best friends is a talking mouse. Who happens to be a king. And a Keyblade master. You're going to have to try a lot harder if you want to weird me out.''

Rush's startled laugh still held a touch of surprise, but he seemed to relax at last.

``As for the Remnant thing\ldots if the Gwayn had a heart to steal, I don't need more convincing than that. People are people,'' Riku added, in case it needed saying. ``The packaging doesn't matter.''

He felt the click of connection in the same instant a brilliant flash flared at his back, and he nearly fell off the edge of the fountain and right into it as he was whirling to investigate. Rush had jumped to his feet as well, and the two of them leaned over, peering into the unruffled depths of the fountain at a heavy gold ring resting innocuously at the bottom, shining too brightly to be lit by the sun alone. Even if it didn't look like a Keyhole, Riku only needed one guess to know exactly what that particular glow meant.

``Oh, man,'' Rush groaned, oddly embarrassed. ``I didn't know Dave still had that.''

``What is it?''

``Uh\ldots it's an old-fashioned betrothal band,'' Rush explained, rubbing the back of his neck without meeting Riku's eyes. ``I picked it up on the Southwestern Road, and\ldots yeah. I don't know what it's doing here, though.''

He was reaching to pluck it out of the water when Riku stopped him with a hand on his wrist.

``Can you leave it there for a bit?'' Riku asked. ``It might be weird if I have to close this world while you're wearing it.''

If he'd thought Rush had been red before, it was nothing compared to now. ``Aw, c'mon. It's not\textemdash ''

``Isn't it?'' Riku drawled, not bothering to hide his smirk this time.

``I mean he can't\textemdash ''

``You sure about that?''

``Rrr!''

Riku laughed. ``Now you sound like Zack.''

``Okay, fine\textemdash let's talk about your sovani, then,'' Rush shot back with a grin. ``Fair's fair.''

``Uh\ldots he's not my sovani,'' Riku hedged.

``Do I need to quote you?''

You sure about that?

``Don't bother,'' Riku said with a wry smile that made Rush frown, confused. ``He's not interested.''

``Uh\ldots I may be from the middle of nowhere, but trust me, I know when a sovani's interested. And we're not going to talk about how.''

``Fair enough,'' Riku allowed, amused. ``But you're still wrong. I just happen to look a lot like his best friend\textemdash who just happens to be my boyfriend, because clearly our lives weren't complicated enough.''

Rush still looked puzzled, but more like he thought Riku still wasn't getting it than because he was wondering why Riku was dating his own twin. ``Yeah, but\ldots he's a sovani.''

Riku arched a brow. ``So?''

``So he's not going to care who you look like. I mean\textemdash sovani eyes are pretty amazing, sure, but they still think with their noses. So unless you both smell the same too\ldots '' Now he was starting to look a little freaked out, and Riku jumped to reassure him.

``Not even close.''

``Well, there you go then. Unless\ldots does it bug you that he's got a thing for your\ldots ?''

``Not\ldots like you'd expect,'' Riku admitted, startled to realize it was true. In fact, it hadn't bothered him since the moment he'd realized Sephiroth would just turn creepy stalker guy on him if Riku tried to do the noble idiot thing and leave. ``Me and Seph have been through a lot, and I'm not saying they haven't too, but\ldots Sephiroth's not the kind of guy who just trades up when something new comes along. If you let him catch you,'' he said with a shrug, ``he is definitely going to keep you.''

Stuffing his hands in his pockets, Rush hunched a shoulder with a smile, saying, ``Then it sounds like none of you have anything to lose. I mean, unless you were planning on beating yourself up for getting too lucky. It's the thing to do, I hear,'' he added with a sheepish little grin, like he had practical experience in the matter.

Suddenly the whole conversation seemed so familiar Riku found himself staring, dumbfounded.

``Oh, you have got to be kidding me,'' he muttered aloud. ``Since when did they start making Princes of Heart?''

``Huh?''

``Never mind.'' And thank Gaia he'd never had to try to kidnap this one; it would definitely not have been worth the headache. ``Just\ldots I'd better find Zack.''

``Good idea,'' Rush said with suspect innocence, completely failing to stifle a smirk.

``Not one word,'' Riku warned, aiming a glare at Rush that glanced right off that impenetrable grin.

Never mind the fact that Zack wasn't actually a sovani, didn't actually think with his nose, and that Rush had still misread the entire situation.

It still gave him something to think about as he went looking for the man, ready at last to start making their way back home once more.


\scenechange


Whatever had been bugging Riku earlier, Zack was more than relieved to see that it had been fixed, even if he still didn't know what it had been. It'd been enough to see Riku coming to find him with the lightness back in his stride, a faint little grin tugging at the corners of his mouth. Even stepping through the dark portal Riku had raised and finding himself back in his own familiar body wasn't quite as satisfying as seeing the determined focus returning to Riku's eyes, the shuttered look of preoccupied worry thoroughly banished.

So that was one he owed to Athlum. The rest he owed to the jokers around them.

``I'm just saying,'' Giese was insisting doggedly, ``when someone tells you your earth elemental bears an uncanny resemblance to the Remnants of the Apocalypse\textemdash ''

``Yeah, that was weird,'' Hall agreed, blithely unconcerned. ``I mean, the Dao Pagus summoned just looked like one of those raptor things.''

``That's all you, Holly,'' Titus rumbled, shaking his head. Though the big guy wasn't ostentatious about it, Zack could tell he was glad to be back in his own body as well.

And as for Riku, even the long hike through the darkness didn't seem to have dented his spirits any. He was actually smiling as he slowed, cocking his head and listening to something only he could hear.

``This is it,'' Riku said, holding up a hand without calling up a portal just yet. ``We ready?''

``Always,'' Zack promised amidst a chorus of agreement, and Riku nodded once, grinning as he pulled open a rift in the dark, waiting this time without fretting as Stiegler went through first.

When the Sarge's offended growl reached them\textemdash "What the fuck is that supposed to be?"\textemdash Zack found himself stifling a laugh, trading glances with Riku and nearly thrumming with anticipation.

``Not quite like it says on the recruitment poster, is it?'' Zack offered, unslinging his sword and waiting his turn, always the last out but one.

Riku only shrugged, smiling back, and said, ``I wouldn't trade it for the world.''


end

Posted 3-27-2011