\renewcommand{\pfbreakdisplay}{%
\ding{167}\quad\ding{167}\quad\ding{167}}

They came out of the dark portal fast but cautious, Titus' clipped warning of ``We've got Heartless'' stretching every nerve taut. Zack didn't give him any trouble about who was going to be the last man out this time, and Riku didn't automatically try to shrug off the hand that settled at his elbow before he was even all the way through the portal. He just let the portal drop and stood, swaying a little but trusting Zack to keep him on his feet, and took one half-exhausted look at the chaos spreading out from the open square they'd been spit out into as the SOLDIERs formed up around him.

Funnily enough, though the cobbled streets around them were teeming with hungry black shapes, screaming townsfolk and liveried soldiers falling hopelessly back, what he saw was enough to loosen the cold knot of trepidation in his chest.

``It's fine,'' he muttered, shaking his head hard, as if that'd help. ``Small fry. This world's still got some time. Just\textemdash ''

``We're on it,'' Titus said, nodding at him\textemdash or no, probably at Zack, who nodded back. And didn't let go of his arm.

He hated the feeling of being useless, watching others wade into the fight without him, but he knew himself well enough to know that he'd fall flat on his face if he tried to play hero at the moment. This place had been closer to Ivalice than Ivalice had been to their starting point, but maybe giving himself less than a day to recover before dragging them all out again hadn't been the best idea after all. When he'd heard 'Heartless,' his first, dismayed thought had been: I can't. Not that he couldn't fight, because if he absolutely had to, he probably could. Probably. But if it turned out this world was on its last gasp, there was no way he could have taken them through the dark pathways a second time, not so soon, or held them all together through the planet's dissolution. Finding out he wouldn't have to try made him want to slump with relief.

He forced himself to stand tall instead, took deep breaths and waited for his insides to stop roiling, his head to stop spinning. It felt a little like it did when he overtaxed himself magically, but it wasn't anything so simple. He used his darkness to open the portals and his light to keep the darkness at arm's length, but the actual work of traveling, of pulling twelve guys after him over a distance that could technically be measured in light years and keeping them in one piece inside that careful pocket of not-quite-dark\ldots that was his heart, not his magic at work, and there was no elixir for that kind of strain.

If these guys hadn't been SOLDIERs, he couldn't have done it. He'd have had to go back for help, enlisted Sora, Sephiroth, even the King, or they'd never had survived the first time they'd come out into a fight. And if these guys' hearts weren't as strong as they were\ldots 

He didn't let himself shudder until he'd tugged his arm loose from Zack's steadying grip, and he made a show of summoning his Keyblade to hand to cover it. ``Who'd have thought we'd miss Leá Monde?''

Zack didn't look too terribly convinced that Riku wasn't going to die on the spot, but the guy smiled anyway, shaking his head. ``Sorry, mini-Boss. The zombies liked you, not the rest of us. Me, I'll take the Heartless any day.''

``Picky.''

Zack laughed. ``Not to hear Seph talk. Ready to earn our welcome here?''

``Always,'' Riku said, wondering with a faint grin whether Zack knew just how right he was.

The other SOLDIERs hadn't stayed put, but they hadn't gone far. He could see Titus dead ahead, hammering Gargoyles to shreds with his fists, Stiegler cutting a swath through a pack of Neoshadows that had overrun the broad, straight avenue to their right, Hall covering the man's back and letting fly with spells and the occasional bullet. A Large Body sat down heavily at the edge of the square then exploded in wisps of darkness as Giese finished carving it up with his shortswords; Riku didn't notice the woman crouched behind the guy until she lifted her head, picked up the child she'd been sheltering with her body\textemdash and made a dash for the middle of the square, for them, not the dubious shelter of the shops and houses around them.

Nor was she the only one. As the SOLDIERs let them slip through, more civilians flocked to their center, huddling together in a tight knot of panic and hope in what might be the one truly safe place in the entire city. There wasn't time to examine the unsettling mix of nerves and uncertainty that woke in him. There were Heartless to take care of, reinforcements spilling in down side streets and up out of the cobbles practically at their feet, and he still wasn't in top form.

And as he rushed to meet them, he realized that maybe it didn't matter this time that he wasn't at his best, because he didn't meet the front line alone. There was another blade right there at his side, and if Zack was having to take on part of what should have been Riku's share of the fighting, it didn't seem to be slowing the man down any. Zack's fighting style was a weird mixture of Sephiroth's and Cloud's\textemdash or maybe, he realized distractedly, it was Cloud's that was a mixture of Zack's and Sephiroth's\textemdash and if those three were used to fighting together, maybe that explained why Zack never tried to get between Riku and any of his targets, even when it was clear the man was tempted. He had to be used to weird spells and weirder attacks when you least expected it\ldots or maybe he was just used to running interference for people accustomed to fighting alone.

``Not catching much of a break here, are we?'' Zack mentioned during a brief lull in the fighting, still grinning though they were being pressed hard now on every side\textemdash all of them, from every approach, including overhead.

``It's us,'' Riku admitted, stubbornly not thinking of the civilians at their backs, and Gaia, why hadn't Sora warned him? He wasn't used to people running to him in a fight\textemdash not to hide behind him, anyway. ``They're drawn to strong hearts, and the Keyblade isn't helping.''

``Huh,'' Zack said, lunging forward to meet a Wyvern at the end of its swoop, shearing clean through the streamlined body and whipping around to strike the head off a Gargoyle in the next instant. ``Well\ldots at least if they're coming to us, we won't have to track them down later, right?''

He couldn't laugh. He needed his breath for fighting. But\textemdash 

``You're going to rip a hole in the space-time continuum,'' he informed Zack with all the solemnity he could muster between Dark Firagas.

``Huh?''

``You and Sora. With the power of your combined optimism when you finally meet.''

Zack gave him a hangdog look. ``What? It's a clear strategic advantage.''

``Uh-huh.''

``Just because I look for solutions instead of problems\textemdash ''

``It's called realism, Zack.''

``You have been hanging out with Sephiroth too much,'' Zack groused, but he was wearing that look again, like he was half holding back laughter and half missing home.

Then there was no more time for anything but fighting as every Heartless for miles converged on their position at once.

Even dragging with exhaustion as he was, it was easy to lose himself in the necessity of block and attack, what spells he was good for tossed off as fast as he could get them out. More often than not that meant Dark magic, and he distracted himself from worrying what that would look like to the others by dwelling on his supply of ethers, wishing he'd thought to bring more and wondering if any of the worlds they'd be passing through would have any kind of market for that. Maybe he'd ask Hall, who had to be thinking the same thing. And who wasn't letting that stop him either if the pyrotechnics going off all around were any indication.

It was hard to spare much attention beyond the immediate: the wall of dark shapes before him and the drag and ache of overtaxed muscles, the crawling black starbursts at the edge of his vision that couldn't mean anything good. The Vera potions Ashley had pressed on him before they left helped; it kept him focused, kept him awake when he should have dropped, and one of these days he was going to have to make his way back to Ivalice and thank those two properly. If he'd been fighting alone, he might have fallen back, looked for better ground to make his stand, but there were the townsfolk to consider, trusting them all to hold fast.

And there was Zack, steadfast and tireless at his side, and something inside telling him to hang on, tough it out: some indefinable change in the scent of the air around them, the stink of darkness and corrupted hearts lifting by the moment.

He dropped back instinctively as Zack flared up with power on his right, some sort of Limit that involved a lot of lightning and scores of Heartless going up like fireworks, one after another. The glare of it seared Riku's eyes, and he turned his face sharply away, shifting his grip on his Keyblade and readying himself to dive stubbornly back into the fray. He wasn't going to let anyone fight alone, not when this was what he was for.

But when he blinked the last of the spots from his vision, ready to meet the next wave head-on, he found himself staring at a street empty of everything but a few bewildered guards startled to be alive. For the moment, the Heartless were gone.

``Good timing,'' he managed as Zack turned to him with a grin, just before everything went\ldots funny. He didn't quite black out, but that was probably because of the Cure someone hit him with\textemdash Hall, if he had to take a guess. He felt bad about that, because Gaia knew the guy had been tossing around enough spells already, and what was wrong with him wasn't something Cure would even fix. It kept him on his feet, though, long enough for him to turn to wave the guy off if he looked like he was thinking about doing it again.

Seeing one of the villagers standing with her hand stretched toward him and magic still glittering in the air around her distracted him from the warm, steady hand that planted itself between his shoulder blades. Zack, according to his nose; his heart was just telling him 'safe.'

It was the little girl still clinging to the woman's skirts that let Riku place where he'd seen them before: the ones Giese had saved, the first to run to them rather than away. They could have been from any one of a dozen worlds Riku could name offhand\textemdash the woman tall and fair, pretty but only in an ordinary sort of way, dressed in the same neat homespun as her little girl. She might have been a merchant's wife, or a servant from the castle, or a healer whose patients were common folk like herself. She looked very pale, her one outstretched hand trembling faintly while the other clutched the child to her hip, but her green eyes met his bravely without looking away.

``Thanks,'' he said, not letting on that he hadn't been hurt, not exactly. He was still on his feet, after all, and that definitely counted for something.

``I\ldots it's the least I could do,'' the woman said, offering a hesitant smile. ``Those things\ldots thank you, my lord.''

He blinked, startled, wondering where that had come from. Lord? Him? It wasn't like he looked the part\textemdash but then again, to an outsider's eyes, maybe he did. Not in the expensive wardrobe department, no, but he was the only one not dressed in what was clearly a uniform, and he was way too young to be the one those other guys were forming up around otherwise.

``Uh\ldots ''

Zack's cough at his back was the quiet but meaningful sort, and the eyebrow Titus gave him was as good as a nudge. Better than, maybe, because a meaningful cough was one thing, but he was pretty sure that a meaningful elbow from a guy like Titus would leave a mark.

``It was our pleasure,'' he managed as the woman's eyes turned confused, and that had her smiling again. Maybe this wouldn't be so bad.

He kept right on telling himself that until the soldiers showed up, bearing a summons from their king.

\fancybreak{\pfbreakdisplay}


It was a pretty good thing their brand-new lord had a poker face to rival Sephiroth's, Zack thought with a private grin, or else they might have been in trouble. Not that the kid was fooling them\textemdash every bit of that dumbfounded shock was right there in the eyes if you knew where to look\textemdash and that more than anything reminded Zack that it wasn't Sephiroth they were dealing with. Seph would have arched a brow at the `lord' and shrugged it off as unimportant, probably figuring 'general' translated to much the same thing without ever realizing that it really, really didn't. Riku not only got the difference; he looked like he didn't want anything to do with it, thank you very much.

At least the kid could take a hint. Twelve guys in uniform who could fight like they did appearing out of nowhere? That looked like an advance on an invading force. Add a thirteenth who gave off the trust-me vibe of a Keyblade master and who wasn't throwing his weight around like a real noble would have done? That kept the soldiers friendly when they finally worked up the nerve to approach, their captain clearing his throat diffidently for their attention.

Okay, and the fact that Titus had two kids perched on his shoulders and Giese was patiently letting the healer's girl bandage a scratch that had already disappeared maybe had something to do with it too.

``My lord,'' the captain began, jerking an awkward bow at Riku, like he wasn't sure whether he'd shown too much deference or not enough and was worried about giving offense either way. Or maybe it was just professional embarrassment, because his own men hadn't even put a dent in the Heartless before they'd arrived, and he'd maybe just heard all about that from his own lord. ``On behalf of king and country, we welcome you to these shores. News of your valor has spread, and His Majesty wishes to extend his greetings personally.''

More like `wishes to examine this worrisome new force personally,' but Zack didn't say that aloud. He was too busy examining the captain and his men, placing their armor, their weapons, on par with the rest of what he'd seen of this world. They wouldn't be finding any real tech here, he was sure of it, but he still didn't know what their magic was like. He wasn't too worried about being outgunned, not with Hall on their side, but it wouldn't do to get too cocky, either.

``It'd be an honor,'' Riku replied, nodding solemnly, eyes not wavering from the captain's. At least he'd gotten his color back, had the right sort of confidence to see him through when complete strangers started saluting. Maybe that was another thing he'd learned from Sephiroth; stranger things had happened.

Then Riku glanced at him sidelong, and it was all he could do not to laugh. That wasn't the `get me out of this' look Sephiroth used to give him when he couldn't politely bow out of some function or extricate himself from his admirers. It wasn't even the `if you tease me for this later, I will make you pay' look Cloud had been known to level on him.

``I hope you appreciate what I'm going through for you'' was what that brief flick of eyes was saying, and damned if Zack didn't feel like he owed the kid for this. Somehow. Which meant he was probably in trouble if Riku ever decided to collect.

Grateful for the distraction, he managed to keep his grin to himself as Riku turned from him to interrogate the soldiers.

``Those creatures,'' Riku began, face blandly impassive. ``Have they been giving you trouble for long?''

``Long enough, my lord,'' the captain muttered, shaking his head. ``We saw the first nearly a month ago\textemdash one of the little creeping things that melt into the earth.''

``Shadows,'' Riku said with a casual nod, eyes keen, face impassive. ``They're the weakest of the lot.''

``Aye, my lord, so we found. At first there were only a few, easy enough to handle, but then came more, and stronger. They started flocking a sevenday ago, but not in these numbers. I've never seen the like.''

``I have,'' Riku said flatly, gazing up the broad, straight thoroughfare, so flashy it could only be a parade route, to the castle at its end. ``I don't know who, but I can pretty much guarantee you that someone's up to no good.''

Zack would have expected to be met with suspicion at that, for the tables to be turned and pointed questions to be asked about just where they'd come barging in from. Instead the captain looked away, thoughtfully smoothing his bristling moustache with thumb and forefinger.

``The king might be able to tell you the who, my lord,'' the man said diffidently, not quite meeting Riku's eyes. ``It's finding them that's the trouble.''

``I see,'' Riku replied, and Zack was starting to think he did as well. If these people couldn't hold off the Heartless, they probably weren't up to tangling with a really determined wizard either, or a sorceress like the one Riku had mentioned. Not until they'd come along, dangerous strangers in need of hospitality. The king probably saw this as a win-win situation: if they proved themselves by taking out whoever had the royal knickers in a twist, all to the good. And if they didn't come back, well, they weren't his subjects, were they? At least they'd be out of his hair.

He kept his mouth shut the way a good soldier should until he realized they were taking a detour, not heading in through the main gates but being shuffled around to the side. Smart, maybe, if the king was trying to save face in front of his court and not draw too much attention to them, but it wasn't a precedent Zack wanted to see established. If Riku really was a lord, he wouldn't have allowed it.

``Sir,'' he spoke up, quiet but cold, more for the captain's benefit than Riku's.

``I'm aware,'' Riku replied, glancing sidelong at his escort. ``I assume there's a reason for this reception?''

The captain had the sense to look uncomfortable, but his nod was firm. ``King's orders,'' he said, ``but no insult intended, my lord. There's just\ldots something you need to see.''

Zack didn't like the sound of that, could practically feel the others going on point at his back, shaking off the tiredness of a long battle and gearing up to do it all over again. He heard the soft creak of leather that was Titus flexing his hands in his gloves, the whisper-faint click of Giese loosening his shortswords in their sheaths, and though he didn't relax for a moment, knowing the others had read the situation and had his back left him free to fix his attention where it needed to be: on Riku, watching for orders and danger alike.

The big iron gate up ahead looked like it led to the stables\textemdash full of horses, which he'd once thought were mythical, not the chocobos he was used to. There was a gaggle of geese milling about in the courtyard beyond, hissing at strangers and beating their wings at anyone who came too close, but no one seemed to be in a hurry to round them up. Maybe their usual keeper was gone. Zack didn't pay them much attention\textemdash animals didn't generally care for the smell of mako, and the birds took one look at them and bolted for the far side of the yard\textemdash but he was sort of preoccupied as it was.

Unless this world just had weird notions about what constituted appropriate signage, he had to say that hanging a horse's severed head up over the stable gate probably couldn't be too good for the beasts' morale.

Though he still had a better eye for two-legged mounts as compared to four, even he could see that the animal in question had once been quality. Death had dried the effigy out, the eyes long-since gone to feed the crows, but the lines of the skull beneath the thin black hide were clean and delicate, with a broad brow and a dainty muzzle. Even bird-plucked, the beast's forelock fell thick and long, a ragged banner when the breeze kicked up. Though he'd seen much worse, it was still simultaneously one of the most pitiful and the most creepy things Zack could remember coming across in years.

And that was before dim sparks, unearthly blue, lit in the thing's empty sockets, sad and faded until they fixed on Riku with a brightening gleam.

The lean jaw worked as they all stopped dead in their tracks, no one breathing, silent enough they could hear dry tendons scraping over bone as the dead thing struggled to speak. I want to try talking back, he remembered Riku saying in Leá Monde\textemdash remembered thinking the kid was out of his mind\textemdash only what did he know? Apparently that was perfectly normal in some places, because the local army wasn't trying to kill that thing with fire, and Riku was just standing there, waiting, listening.

Looking like he wanted to be anywhere else, yeah, but not surprised.

``You,'' the horsehead managed in a tired, breathy voice, distinctly female. ``Have you come to save my princess?''

That startled the guards, though not in a bad way; they looked hopeful now where they'd been nervous before.

It was Riku who looked faintly sick, and Zack could have sworn he heard the kid mutter: ``That'd be a change'' before Riku got a hold of himself, pushing aside whatever was troubling him to meet those eerie eyes with a firm nod.

``If I can,'' he said, and though it may not have sounded like much to the locals, Zack knew a promise when he heard one.

\fancybreak{\pfbreakdisplay}


Riku wasn't sure what to expect from the king after being met at the gate by a talking zombie horse, but actually the guy was pretty normal. Old, both for this sort of world and to still be on the throne without sixteen sons to distract each other with their ambitions, with thinning silver hair and a seamed face that seemed more tired than conniving. His only son was a tall, good-looking man in his twenties, one that could possibly use the plain, well-worn sword strapped to his hip, but the prince's eyes never settled on anyone for long. Mostly the prince watched the door, like he expected news or for his princess to appear by magic, the way a story was supposed to end.

Grateful for Mickey's coaching, Riku answered the royal greeting as formally as he could, reasonably sure he wasn't embarrassing himself, at least. He'd just have to make sure not to glance at Zack, who was probably shooting him incredulous looks, and who'd probably see too much if he caught Riku's eyes right now.

A missing princess. And he was sure to be sent after her.

Who said the universe didn't appreciate irony?

``So,'' he said at last, ``this princess. Your daughter?''

``My son's betrothed,'' the king said with a sigh. ``Our countries are neighbors, allies; to have her go missing under these circumstances\ldots '' He shook his head, glanced once at his son and returned his gaze to Riku. ``I'm afraid this has been an embarrassment to us all, and I hesitate to involve an outsider, but in light of those\ldots creatures, I'm not sure I have a choice. This entire affair has been irregular, practically since the princess began her journey. Our countries are at peace, but to set out with only a single waiting-maid\ldots ''

Riku glanced at the prince as well, but the man was looking past them again, right over their heads, his face stiff and still. ``Perhaps you'd better start at the beginning,'' Riku advised.

``Yes, well. As I've said, our countries have long been allies, and we had hoped to cement these ties with the bonds of marriage. A betrothal was contracted between my son and the Princess Elaine; the girl came of age this year. The wedding date was set, and we expected her to arrive with a proper retinue, but\ldots when she did arrive, it was with three carts in train to carry her dowry, but her only companion was a girl we believed to be her waiting-maid. No guards. No other servants. Just the girl.''

``Who turned out not to be a maid at all?'' Riku hazarded, keeping a smirk to himself. Not a maid but a sorceress, probably, and Gaia only knew what had happened to the rest of the party\textemdash 

``Who turned out to be the princess,'' the king admitted in clipped tones, nodding once at Riku's look of surprise. ``No one realized at the time, but the maid had forced her mistress to change places with her. She was\ldots very convincing, convincing enough that I agreed to set the true princess to tending geese,'' he admitted with a grimace. ``She even arranged to have slaughtered the one creature who could have proved her false\textemdash the princess' mare, Falada. As you've seen, that ruse was hardly successful, but the damage had already been done. Bad enough the rift this could cause between our countries if any of this ever comes to light\textemdash now both of them are missing from the castle, the false bride and the true princess alike, just as those things began attacking in earnest.''

``And you think there's some connection between them and the Heartless.''

``As near as we can tell, those beasts first appeared when Elaine left the protection of her mother's court, to the day. I hardly think it a coincidence.''

``You have a point,'' he said, casting one last glance at the prince. At least that stoic look made sense now, and it made him want to be very careful not to blow his own cover. Having been fooled once, this guy didn't look like he'd be too very happy about finding out Riku was about as highborn as his former fiancée. ``All right. I'll look for the princess. Can you tell me anything about where she might have been taken?''

``They came here by the Blue Road,'' the king replied, the thoughtful crease between his brows etched more sharply as he offered up his best guess. ``It follows the Quickslip River most of the way. There are caves half a day's ride from here; you can see them from the road, but few people go there. It was a place of ritual, once,'' he added, so meaningfully Riku suspected that if he'd been from this world, not another word would have needed to be said.

He nodded, saving his questions for later, when he could ask someone who didn't have royal dungeons to go along with royal paranoia if he managed to stick his foot in it. Tired as he was, he would have asked for directions to the cave on the spot, only for once he had more than just himself to worry about. There were the SOLDIERs, who'd been fighting just as hard as he had if not harder, and while it wasn't like they couldn't take care of themselves, on a world like this, keeping their cover changed everything. There wasn't much democratic about being a soldier in service to a lord, and no one was going to be looking out for the best interests of a bunch of strangers in the first place, no matter how well they could fight. Which left it up to him.

And it looked like he'd be having words with Sephiroth too, not just Sora, about warning him about these things before they came up.

``I'll need a guide or a map,'' he said, ``preferably a map. We're equipped to deal with the Heartless,'' he added when the king began to protest\textemdash more out of offended hospitality, Riku thought, than suspicion. ``If it comes to a fight, keeping the princess safe should be our main concern, not our guide. We'll set out first thing in the morning.''

``Of course,'' the king replied, and his pleased tone, the way his face relaxed, told Riku he'd done the right thing. Clearly the king had expected a delay, was probably just relieved this visiting petty lordling didn't intend to loaf around for a week before getting down to business. ``My steward will ensure you have all you require.''

The king let them go soon after, for which Riku was grateful. He'd gotten his breath back, and his heart no longer felt quite so thinly-stretched behind his ribs, but he wanted rather desperately to sit down somewhere quiet and just\ldots watch Titus loom and Stiegler sharpen his sword, listen to Hall wax enthusiastic about some spell picked up from Gaia-knew-where and Ochs crack wise until he had everybody laughing, while Zack unobtrusively made the rounds until he was absolutely certain everybody was okay. Wait for the hollow feeling inside to go away.

The castle steward\textemdash a quiet, urbane man with silvering hair and faint laugh lines cut around a mouth used to smiling\textemdash looked like a lord himself in his rings and dark, sober brocade, but he didn't have the stuffed mannequin air of most of the high servants Riku had met. Admittedly he hadn't been on friendly terms with any of the human ones; kidnapping their princesses, often in the midst of a Heartless invasion, didn't tend to leave a good impression. Still, the man reminded him a little of King Mickey's steward with his forthright stare, the unassuming pride in his confident stance.

``Welcome, my lord. I am Osenar, His Majesty's steward,'' the old man greeted them as they left the audience chamber, dark eyes sweeping them with friendly appraisal. Riku didn't know what they looked like to an outsider, but he was suddenly aware of Zack standing at attention just behind his left shoulder, of the quiet stillness of the others in their even ranks, solid and impressive and inseparable. ``I think,'' Osenar said slowly with a tiny curl of a smile, ``an ambassadorial suite would be appropriate for the occasion. Though if you'd rather, room could be found in the barracks for your men, I assure you.''

``No,'' Riku said quickly, ``that's fine. Nothing personal,'' he added with a half-shrug and a self-deprecating smirk, ``but with the Heartless around\ldots ''

``Of course. I quite understand,'' Osenar said, sounding as if he truly did. Probably he'd seen what the things could do. ``If you'd care to follow me\ldots ?''

The castle was pretty impressive as castles went: plenty of eye-catching architecture and expensive ornamentation, which in his experience generally pointed to a history of peace, prosperity, and a firmly-entrenched royal family. He was more interested in the castle's security, which looked to be tight, even after the fighting they'd just seen. There were pale faces all around, nervous eyes that tracked them curiously as they passed, but no one broke discipline and accosted them in the halls, whether to demand the secret of their success against the Heartless or just to bluster at the newcomers.

Zack looked like he approved the one time Riku caught a glimpse of the man, and he had to remind himself that it was Zack who had the right idea, that he wanted the local guard to be good at what they did, and that just because there was a princess involved, that didn't make him the enemy. Not this time.

``So,'' he said after they'd gone a little ways, ``the king mentioned something about caves along the river. Can someone draw us up a map, or\ldots ?''

``Certainly, my lord,'' Osenar replied with a faint wince, though he sounded willing enough to help. ``You can see the Howling Caverns from the road, as it happens, but it helps to know where to look.''

``That's quite a name,'' Zack spoke up, echoing Riku's own thought.

Osenar nodded, the brief flicker of his eyes traveling first to Riku and then to Zack so smooth it went almost unnoticed. ``There are those who say the name comes from the sound the wind makes through the cave system, which I understand is extensive,'' he offered, as courteous as before. ``It's very forward-thinking of them, I'm sure.''

``But you don't believe it,'' Riku finished for him.

Smiling ruefully, Osenar shook his head. ``If the opinions of an old servant count for anything\ldots no. I don't. The tales of that place are as old as history, and even in this day and age, there are those who believe magic should never have been tamed. There were still rituals held in secret there when I was a boy; it's unpleasant to think, but I daresay the caves earned their name then.''

The look Riku traded with Zack was unthinking, automatic, and almost turned into a startled double-take when he realized he could tell exactly what the man was thinking: And no campfire tales from him tonight, either.

Zack grinned at him, which made him snort very quietly, not wanting to blow their cover, but he was still smiling himself as he dragged his eyes back to their guide. It was probably his imagination that the old man was regarding him more warmly than before, with something like approval quirking the edges of his mouth. Odd\ldots or maybe not so strange at all. He couldn't judge every court by Mickey's, where even the assistant dishwasher's apprentice could talk to a king like an old friend.

``Well,'' Osenar said mildly, ``here we are, my lord.''

He was grateful for the warning; it reminded him to keep his poker face nailed on tight when the old man threw open an already-imposing door with a flourish.

\fancybreak{\pfbreakdisplay}


Even having the run of Radiant Garden's fortifications and being in and out of his fair share of castles since the tender age of fourteen, Zack had to admit these people knew how to do things in style. The ambassadorial 'suite' they'd been assigned was more of an ambassadorial 'wing,' complete with quarters fit for a small private army and a gaggle of servants when it came out that Riku had somehow misplaced his own.

He was pretty sure Riku had been trying to think up a polite way to turn down the honor of the latter until they started tossing around words like 'bath' and 'dinner.' That perked the kid up in a hurry, and he'd been hard-pressed not to laugh when Riku's eyes went warm and grateful, sending one woman all flustered at his heartfelt ``Please.''

He'd found it a little distracting himself, to be perfectly honest, but he wouldn't let himself think about that now.

Wandering over to the couch Riku had collapsed onto once the servants went haring off to find a fatted calf and enough hot water for a baker's dozen, he kicked lightly at one of Riku's feet with a grin. ``So,'' he began, drawing the word out to an indecent number of syllables until Riku peeked out at him from under the arm the kid had thrown across his eyes. ``Any commands for your loyal subjects?''

``Bite me,'' Riku offered pleasantly enough, burrowing back under his arm as Zack laughed, right along with everyone else in earshot.

``No, really,'' he said, nudging Riku's booted foot again. ``How are you holding up?''

``Fine,'' Riku said, dropping his arm and peeling open both eyes, though he didn't straighten from his boneless sprawl. ``Kind of hoping we'll have a few days before we have to do it again, but I think I could manage. For what it's worth, the trips should get shorter once we get closer to the hyperspace routes, but I think that's more to do with the nature of world-hearts than actual distance. It's\ldots hard to explain,'' he added, mouth twisting a little as he shook his head.

``I'll trust you for it,'' Zack said, not letting his smile slip even a fraction when Riku gave him a better-hidden echo of the same baffled look Sephiroth used to turn on him over the exact same promise. ``So what do you make of this place?''

Lacing his hands across his stomach, Riku frowned at nothing, gaze turning inward. ``I'm not sure. I mean\ldots I've been to weirder places, but they were mostly more up-front about it, too.''

``So I take it talking zombie horses aren't exactly the norm.''

Riku smirked. ``The talking horses? You'd be surprised. The zombie part\ldots actually, I guess that's not all that unusual either, now that I think about it. But the two together\ldots ? That's where it gets weird.''

``Oh, good,'' Zack said, playing up his relief just to see Riku's smirk warm into an honest grin. ``And here I thought it was just me.''

There were a lot of things he wanted to ask, like where an island brat had learned the courtly manners Riku had used on the king and what exactly constituted 'weirder' as far as worlds went. He figured it could wait, though, because while Riku didn't look nearly so wiped-out as he had coming out of that last portal, he still didn't look like he was quite up for a round of Twenty Questions yet either. Especially when Zack wasn't sure he'd be able to stop at twenty.

So he kept one eye on the kid but left him to his own devices, checking up on the others until he'd made certain no one was being a stoic bastard and trying to tough out more than he should. He thought at first they'd gotten lucky, or else Hall had been even quicker off the mark with his Cures than usual, only Hall was bending Stiegler's ear about something he was calling 'Regen' while the Sarge sharpened his sword, grunting now and then to show he was still listening.

He looked up curiously when Titus nudged him in passing, brows arching when he realized the big guy was wearing the faint little grin that made him look less like a sociopathic uncle and more like a benevolent stone idol. Turning to look when Titus tipped his head meaningfully in that direction, he found Riku still sprawled out where Zack had left him, eyes closed but probably still awake, considering that a dozen SOLDIERs in a single room were hardly ever what anyone would call quiet. He still had that look of distance Zack knew all too well\textemdash Cloud not sure of his welcome, Sephiroth not sure of people, not deep down where it counted\textemdash but at least he'd relaxed around them again, a far cry from that brief return to wariness of that morning.

It was definitely a step in the right direction, gave him hope that Riku might not turn out to be as tough a nut to crack as Sephiroth had been\textemdash or Cloud, for that matter. Then again, that was no reason to start slacking off.

When the servants came back to ask whether their `lord' would like any help in the bath, Zack stepped in before Riku's perfectly blank look could crack.

``No thanks. We've got it covered. Just lead the way,'' he said, grinning covertly at the disappointed looks the two girls didn't hide quite quickly enough. One blushed prettily at him, but the other smiled back, giving him a flirtatious look that let him know the supposed captain of a lord's personal guard wasn't exactly beneath her standards either. 'Sorry, kid; I'm taken,' was what he was tempted to say, only\ldots that probably wasn't exactly true anymore, was it? Still. The only way they were going to get back home was to treat it like a mission, where every world was enemy territory, and a smart SOLDIER didn't go consorting with the locals when he had a job to do.

And anyway, while sixteen hadn't been too young for him when he'd been eighteen himself, it was a little different now that he was older.

Which was a good thing to remind himself of\textemdash and that seventeen wasn't really that much different\textemdash when the girls split them up, one turning the guys over to an older man who led them off down the hall, the other waiting patiently until he and Riku took the hint and followed her deeper into the suite itself. ``Let me know when you're ready, and I'll have one drawn for you as well,'' their guide murmured when he hesitated at the door, pretty sure that he shouldn't follow Riku in, except that if he didn't, there might be talk. Especially seeing as the pretty, too-young bath servant\textemdash and one guess as to why it was the flirty one who'd stayed behind\textemdash seemed to have every intention of waiting right there until Riku was done.

``Zack,'' he heard from inside the bath chamber, utterly uninflected, and though the voice was all wrong, the tone itself was so familiar he found himself jumping to answer without thought. It was definitely one of Sephiroth's quirks, and it was a little weird to be hearing it now; Sephiroth mostly used that tone when he wasn't sure himself whether he ought to be rebuking, praising, or sending up a plea for help, and was leaving it to the other guy to figure it out.

Riku had already pulled off his boots by the time Zack closed the door, was half out of his shirt, arms still tangled in cloth and crossed over his chest when he tossed Zack a wry look. ``You did want rescuing, right?'' the kid asked quietly, mindful of the big ears outside.

``The thought did cross my mind,'' he admitted, watching curiously as Riku finished shrugging out of his sleeveless shirt, black like the rest of his gear. There was no particular hesitation as Riku's hands went for his belt, no body modesty that Zack could spot at all, which said 'military' to him but probably had more to do with growing up on a tropical island. Then again, Sephiroth had been just the same, and that hadn't been the military's doing alone, had it?

``It's a lot different from Mickey's court,'' Riku offered as Zack pulled his eyes contritely away, wandering around the steamy room and poking into things to give Riku as much privacy as he could. ``Wait. Did I tell you about Mickey?''

``Well\ldots I think you mentioned you were out here on his orders. Is he your king, then?'' he asked, ambushed by a mental image of grass skirts and flower crowns, torches and volcano gods.

``It's\ldots complicated,'' Riku said, down to his boxers and looking thoughtful when Zack glanced unthinkingly over his shoulder. ``He's Disney's king, actually\textemdash and if there's a center to the cosmos, Disney's pretty much it\textemdash and he's a friend. But if I were going to follow anybody, it'd probably be him.''

``Not Sephiroth?'' he asked lightly over a last, faint rustle of cloth, the splash of water, and he was not about to turn around now, no matter what Riku said.

Only Riku laughed, a helpless, snorting sound like Zack had just asked the completely unexpected, and when he turned around, he found Riku grinning like the thought had never even occurred to him. ``Are you kidding? He'd have an aneurysm. Besides\ldots he still doesn't listen, but I think he's had enough of telling people what to do. He mostly leaves that to the Restoration Committee these days.''

``He trained you, didn't he?'' Zack asked, focusing on that and not what was right in front of him. All that black really did make Riku look slighter than he was, because that was solid muscle he was looking at, still lean because Riku was still growing. Leaned against the high back of a gilt-filigreed tub that could have fit three easily, Riku looked more comfortable than he would have expected, not just with himself but with the company. He wasn't sure whether he ought to be flattered or not. ``I, uh\ldots you've got some of his moves.''

``Yeah,'' Riku said, reaching for the soap, ``but that's different. He used to be\ldots well, like I said. He'd have these weird spells where it was like his memory was just gone. He wanted to keep me in one piece, and to do that he had to make sure I could survive long enough for him to remember who I was. So he taught me pretty much everything he could think of and hoped I could keep up.''

He didn't sound riled by that; that was the funny thing. Being as good as Sephiroth was something everyone dreamed of; beating him was something he'd known guys to flog long past the point of any reasonable fantasy. Jealousy and resentment were the norm, not the exception, when relative skills started getting held up for comparison, and even guys who knew better got defensive now and then about how big the gap was between their best efforts and what Sephiroth appeared to have been born with.

So maybe it made perfect sense that Riku had gotten the one-on-one training half of Radiant Garden would have given their left arm for, with both legs thrown in. Something had apparently given the kid a good dose of perspective to go along with the natural talent, and as Zack knew from personal experience, a little of that could go a long way.

When Riku's head came up again suddenly, Zack almost took a step back, wondering if he'd been staring again. He couldn't have been, though\textemdash and he'd been distracted anyway, so it couldn't have been that creepy\textemdash because Riku's eyes were dead serious, warning him to listen and listen close.

``He's better now,'' Riku said slowly, holding Zack's eyes unblinking, ``but I don't know what he's going to do when he sees you guys again. If it gets crazy, just\ldots don't back down, and don't panic. He'll come around. But you might need to give him a few minutes before he does.''

``What? You think he's going to come after us with a sword?'' Zack asked, grinning until he remembered that Sephiroth had done just that to Cloud\textemdash and apparently to Riku, too\textemdash repeatedly.

``He might,'' Riku admitted with a lopsided smile. ``Let's just hope he has as good a nose for his friends as he does for me.''

Zack shook his head with a puzzled frown. Riku had mentioned something about having a good nose before, seemed to have a major case of heightened senses when it came to things like darkness and light, but\textemdash  ``What do you mean?''

Riku looked startled, but though Zack couldn't tell whether it was because Riku thought he'd already explained or whether he hadn't meant to bring it up in the first place, what he answered with wasn't what Zack had asked at all.

``Oh. We're, uh\ldots kind of together. Me and Seph. About two years now.''

Well. He guessed that made the question of whether or not Riku was too young for him pretty much a moot point.

\fancybreak{\pfbreakdisplay}


Lying awake in the middle of a bed so ridiculously oversized his fingers didn't even come close to touching the edges at their full reach, Riku stared up at the dark ceiling above and tried to wrap his mind around what his heart was telling him. Zack was good\textemdash at not reacting visibly to verbal landmines, which he supposed you had to be if you were going to be friends with Sephiroth, but also the man was just\ldots good. He was even starting to suspect Zack might be an impossibility on the same level of magnitude as Sora, with enough goodwill and self-sacrifice to revive a solar system or twenty, and he wasn't sure how he'd managed to miss that fact in the very instant they'd met. Distraction by Heartless, probably. That was his excuse, and he planned on sticking to it.

He'd figured out pretty quick that at least half of the obedience he'd been getting from the others had as much to do with his resemblance to their former commander as what he was, even aside from the fact that he was the person who was getting them home. As for Zack, he'd thought\ldots former second-in-command, good friend, and had left it at that. Probably he hadn't wanted to look at it any closer, for the same reason he'd never quite faced his own relief when Sephiroth had stopped stalking him and Cloud interchangeably and finally decided to pick one. Which was funny, because he was actually on pretty friendly terms with Cloud himself these days, even if Strife and Sephiroth were still taking it day by day. He just\ldots hadn't been prepared to deal with that much shared history at the time, and he wasn't entirely certain he'd grown past that even now.

He thought he was, though. Hoped so, anyway. Because there'd always been a name missing from every conversation he'd ever had with Sephiroth about the man's past, and though he'd never gotten the feeling they'd been lovers, he'd always known it was someone loved.

It made his stomach twist to even consider it, his fingers tightening slowly into the sheets, but he did think, very seriously, about doing a little self-sacrificing of his own and letting Sephiroth make that choice again. If Sephiroth wanted Zack\textemdash and Zack was clearly still carrying a torch for Sephiroth, if that instant of stunned embarrassment and swiftly-hidden disappointment was anything to go by\textemdash maybe he ought to just\ldots let it go, let it happen if it was going to, and see where that put them afterwards. If he backed off enough for long enough, he was bound to get his answer.

Then he snorted at himself in sheer disbelief, groping blindly for a pillow to smother himself with, as he was clearly too stupid to live. Like Sephiroth would let him get away with abandoning the man, however good his intentions. ``Get real,'' he muttered into silk and goosedown, huffing a laugh. Sephiroth had stuck by him through everything from Heartless possession to body alteration; the man was hardly going to kick him to the curb now.

Right. So maybe nothing had really changed, other than having his eyes opened a bit. And maybe what did change, if anything, was really going to depend on Sephiroth in the end, which meant it wasn't worth worrying about until they made it back home. He just hoped it wouldn't get too awkward in the meantime, because he honestly liked Zack. It was pretty much impossible not to, which was just another way the man reminded him of Sora. Although\ldots considering that he'd been more than a little obsessed with Sora himself once upon a time, maybe that was something he'd better watch.

Sora teased him enough about 'going native' without him trying to outdo Aeris in the boyfriend department too.

\fancybreak{\pfbreakdisplay}


Zack reminded himself firmly that being mounted was something of a universal status symbol, that nobility was probably expected to ride, and that he ought to be grateful that either Osenar or the king thought enough of the lot of them to have thirteen horses waiting in the stable yard when they mustered just before dawn. Anything to distract him from the laugh clenched behind his teeth as he watched Riku give his mount the most dubious look he'd yet seen from the kid, followed by a low-voiced, ``I don't suppose you talk, do you?''

His own sputter of laughter was covered by the fiery-looking white's uncomprehending snort, but Riku turned a betrayed look his way anyway.

``Not much of a rider, I take it?'' Titus rumbled, nudging Zack with an elbow before he could lose it entirely.

``Not exactly. It's just that the only horses I've ever ridden could tell me when I needed to fix my seat,'' Riku admitted, rubbing absently at the muzzle that pushed curiously into his chest. He didn't look particularly intimidated, though Zack suspected that was probably more horse than a beginner would usually want under him. Then again, he'd already figured out that Riku's guts sometimes outweighed his common sense and resolved to keep an eye on things as best he could. There'd been horses on their adopted world, after all. How much different could they be?

Famous last words, he found himself thinking not ten minutes later, glad he hadn't said any of them aloud.

It was a good job the streets were mostly deserted, because Riku's horse lit out the moment it was given its head, and the rest of the herd followed like they'd seen a good thing going and didn't want to be left out. Apparently someone had forgotten to mention that what they'd been issued before now were the steadiest beasts the cavalry had to offer, and that what got reserved for nobility was a different article entirely. Still, other than one bad moment when Riku's horse lunged from a snorty, pawing standstill to a gallop, the kid managed to find his seat quickly enough, tucking himself down over the stretched-out neck and letting the beast run itself out rather than sawing on the reins.

Clattering down the main thoroughfare and through the opened gates to the west of the castle, they flew past the lamp-lit windows of the town beyond the castle walls, their path marked by the curious eyes of sleepy domestics, a few tradesmen spilling out into the dawn to start their day. Closer to the castle's defenses, the houses were more impressive, some rivaling those inside the city proper, but the further they rode, more modest homes started cropping up, cottages giving way to farmsteads as the street cobbles petered out to hard-packed earth.

It was another few miles before he realized where the road had gotten its name, and by then the ground had fallen away on their right, opening up on a wide river cut deep into the mottled blue rock that lined its banks. It reminded him a little of home\textemdash the Crystal Fissure and the old ravine trails surrounding the Great Maw\textemdash but he wasn't much of a geologist, wasn't sure what made the rock look like that. He'd figured it was pretty common until he'd gotten a good, long look at how other worlds lived, seeing nothing but brown and tan and grey for years.

Little by little he watched Riku straighten in the saddle just ahead of him, watched the white horse's ears flicker back and forward again, listening this time to the hands on its reins. Slowing now was a smart idea; they still had a good ways to go, and tiring their mounts out in the first hour wouldn't help. Habit made him toss an approving grin Riku's way as he drew apace with the kid, but while Riku grinned back, he already looked distracted, all his attention fixed on what lay ahead.

It probably shouldn't surprise him that Sephiroth had settled on someone as driven as he was. Get them fixated on the same thing, and they were probably unstoppable.

It wasn't until Riku looked over at him again, calling, ``What?'' over the drumming of hooves, that he realized he was staring. Again.

Shaking his head, he said, ``Not bad for an occasional rider,'' nodding at Riku's horse. The white had settled down nicely, jogging along with a relaxed gait, ears pricked curiously forward though one cocked briefly back as Riku patted its neck.

``I'm used to crazy horses taking off for no good reason, actually. If he'd really wanted me out of the saddle, though, that's a different story.''

``At least you know the difference,'' Ochs called from a few horselengths back, a grin in his voice. ``Zack here still thinks that psychotic chocobo of his was just playing around.''

``What? She was!'' he protested, casting a disbelieving look over one shoulder. ``She could've thrown me easy if she'd really set out to do it.''

``Zack,'' Titus rumbled with exaggerated patience, ``I don't think Sephiroth could have stayed in the saddle through all that.''

``You know, I used Scan on her once,'' Hall offered while Zack was still sputtering. ``Thought she might've been an Aero summon that was just refusing to disperse.''

``Well?'' asked Stiegler. ``What's the verdict?''

``Uh\ldots I'm not actually sure,'' Hall admitted. ``I was too busy running away once she noticed I was using magic on her to stop and check.''

Rolling his eyes as the others erupted into laughter, Zack turned to the one friendly face there and said, ``Commedi\textemdash ''

``Gaia,'' Riku swore, staring at him in mingled awe and horror. ``You're talking about the White Demon, aren't you? Zack, I've seen her take out Heartless by herself. You don't ride a chocobo like that; you run away from it.''

``Wait\textemdash you've seen her?'' he demanded, ignoring the chuckles at his back even though he knew he'd just lit up like he'd gotten news of an old friend. In a way, that was exactly what he'd just gotten.

``Yeah\textemdash there's a small flock that lives up in the mountains near the Great Maw. Cloud's about the only one who can get close to them, but I've seen him up there with them now and then. I think they may have\ldots you know. With the rest of the ones who\ldots disappeared,'' Riku said with an uncomfortable shrug. ``Cloud says they're not as old as they should be, anyway, and since he's one of the ones who made it out, he actually remembers.''

That sobered them all a little, the reminder that more things had changed back home than just their world getting broken apart and put back together. Gaia might have boosted clear those she could, but there were a lot more who hadn't been that lucky, lost when the planet warped, hanging in limbo between bare survival and dissolution. Some of them had come back, but it'd taken the better part of a year before anyone realized that something wasn't right, that the returners had come back unchanged from the very day and hour of their disappearance, while the others had lived, grown older, moved on.

Not that that was all that surprising. Apparently it happened even when time wasn't running out of step for the people you were hoping to come back to.

``Man,'' he said at last, as much to lighten his own mood as the others'. ``Skadi's going to pluck me bald-headed for running off without her.''

``That's if she doesn't eat you,'' Hall agreed without much sympathy, beginning to smile again.

``Yep,'' Stiegler agreed. ``Give my regards to the Valkyries, Fair.''

``Aw, c'mon, guys!''

``Yeah, Stiegler,'' Riku said, shaking his head, ``be reasonable.''

It didn't exactly get quiet, but Zack would swear he knew that held-breath sense of waiting, the half-hidden, anticipatory grins he'd seen once years before, when Sephiroth had finally unbent enough to give as good as he'd heard the others getting. And maybe this wasn't quite the miracle that had been, but it marked the kid as theirs if Riku just didn't lose his nerve at the sticking point.

In the half-beat where Riku seemed to realize he had their undivided attention, there was an instant when his eyes flicked toward Zack in a way that hit him square in the gut, not Sephiroth but pure Cloud in the blind disbelief looking to him to make sense of it all. It was buried in an instant as Riku turned back to Stiegler, drawling, ``You know his soul's the first thing she's going to eat,'' but even as Zack was laughing along with the others\textemdash and protesting that his soul was perfectly safe, thank you very much\textemdash he couldn't get that look out of his head.

If Riku could live with everything Sephiroth had done, what exactly did the kid think he'd done that he couldn't quite live with himself?

He was still mulling that over an hour later when they nearly ran the girl down in the road.

\fancybreak{\pfbreakdisplay}


It hadn't seemed strange at first that they hadn't run into any travelers on the road. It'd been early, and he was still a little too used to thinking in terms of morning commuters. Take away all possibility of cars, and his brain tended to think of empty roads as a reasonable sort of thing. He should have been thinking of farmers, of traders heading off to market, but it took Titus wondering aloud whether they'd evacuated the countryside to somewhere more easily-defended before he really saw the place through SOLDIER eyes.

He didn't like what he saw, or rather, didn't see. It wasn't just the people. There wasn't anything moving in the empty lands around them, but the smell of Heartless was growing stronger. It didn't take a genius to figure they were massing somewhere close; the only question was how close, and how many. And whether anyone had managed to open any doors.

Coming over the top of a rise, he almost didn't see the girl standing panic-stiff in the middle of the road until it was far too late\textemdash as much for him as for her, because his mount dug in its back hooves and slid to an abrupt stop, nearly losing him from the saddle as it reared up, iron-shod hooves raking the air just inches from the girl's face. She stumbled back while he was still hanging on for dear life, trying to keep one hand on the reins and both feet in the stirrups, and not spill off into the road and under the hooves of the horses coming up fast behind. He was vaguely aware of the SOLDIERs circling up around them, their own mounts under better control, though from the way the horses were tossing their heads, eyes rolling white as they sidled nervously under their riders, not one of them wanted much to do with the strange girl they'd found.

He didn't blame them. She positively reeked of the Heartless.

As bedraggled as she was at the moment, her clothes had been expensive once: summery silks of a cut so impractical it could only be the height of fashion, which had probably grown heavier by the minute the longer she walked. It looked like she'd torn off the bottom few inches of her skirts at one point, the ragged hem falling just above her ankles to show off her fraying slippers. Funnily enough, he'd half expected a waif in distress, but while she was as blond and blue-eyed and ringleted as even the most idiotic prince could want, she was actually on the tall side, more svelte than slender, looked like she'd be just as happy tossing back warm ale as chilled wine.

``Oh, Goddess,'' she breathed, almost too softly to hear, and as he got his horse under control, he saw her cast one longing glance at the woods on his left before straightening up like a soldier for inspection\textemdash or a firing squad.

``Princess Elaine?'' Zack asked cautiously, and there\textemdash that flinch, not like she was afraid of being held for ransom or as a bargaining chip, but like she just didn't know which name would serve her best.

``I\textemdash ''

``No,'' Riku said before she had to make up her mind. ``You're the maid, aren't you?''

``Yes,'' she admitted, shoulders slumping briefly until she drew in a steadying breath. ``You have to let me go,'' she said, not with the arrogance of a princess but the forthright determination of a peasant girl who knew she was in the right. ``Go back to the castle. For the Goddess' sake, warn them. She'll set those things on me once she realizes I'm gone, but she'll call them to her if you take her back.''

``Who?'' Riku asked, just to be certain, and wasn't surprised at all at the look the maid gave him.

``Elaine, of course. Who else? She\textemdash I don't know. I don't know what happened, but\ldots I don't think she wanted very much to get married,'' the girl said with a half-hysterical little laugh. ``She\ldots she wanted me to take her place, said she had plans that didn't include being held under lock and key. She's carrying her mother's blood with her, did you know that? This awful\ldots there's so much of it. And you saw\textemdash you must have seen what she did to that poor horse. I don't know where she learned the rituals, but she's been in the Howling Caverns for days now, and there's no telling what she'll raise. Please. You have to warn the king. I don't think you have much time.''

``Weren't you going to warn him yourself?'' Zack asked, friendly but cautious, nothing in his tone giving away whether he believed her or thought that was the biggest crock of bullshit he'd heard in his life.

The maid's smile made Riku's own gut twist in sympathy, like watching someone counting down the final seconds of a curse. ``Do you know what the penalty for treason is in this country?'' she asked, so gently Riku was pretty sure he didn't want to know. ``They put you in a barrel, a barrel lined with spikes, and they drag you through the streets until you stop screaming. It takes longer than you might think.''

``But you were on your way back,'' Riku forced out, hunting for inconsistencies because he didn't dare be wrong. She stank of the Heartless, but he remembered what it was like living with Maleficent. Just because she smelled of them, it didn't necessarily make her their mistress.

``I guess I hoped I'd meet the prince on the way,'' she said, staring past them with a wistful little smile. ``But I don't think that's going to happen after all.''

He glanced at Zack, at the others, but all he found looking back at him was his own doubts reflected. It was a damned good story, but maybe that was all it was. He almost wished he had Sora with him, even though Sora's answer was generally to give everybody the benefit of the doubt. At least then he'd have an excuse to listen to his own heart for once. Or better yet, if he had Sydney's knack for listening to souls\textemdash 

The shock of dark magic was soundless\textemdash curiously muffling, like the cottony deafness just after an explosion\textemdash and between one instant and the next, the world had been emptied of everything but him and the girl. She gave a strangled squeak of horror, staring first at him and then down at herself, and he realized only belatedly that they'd both gone oddly colorless, grey-toned beings in a world of shadows and muted colors.

Caves, he realized abruptly, recognizing the flicker of firelight on bluestone walls, the furtive shine of Heartless eyes in the dark.

``What\ldots what happened? What did you do? What\textemdash ''

``Come now, Callie,'' someone crooned behind him, and as he turned reluctantly away from the terrified girl staring past his shoulder, he was already nearly positive of what he'd see at his back.

The girl holding the torch might have been the maid's twin except that her hair fell in loose waves, nearly twice as long, in an unbound curtain that reached almost to her knees. They had the same vivid blue eyes, the same perfect bow of a mouth, except that one was pinched in desperate courage while the other curved into a smirk worthy of Maleficent herself. It was easy enough to make the comparison between the two girls; the real maid was still frozen at his back. It was her memory he was looking at now, standing stiff and unwilling with the princess' arm looped familiarly about her waist.

``Didn't you enjoy being royalty?'' Elaine asked, smiling still. ``I thought that was every girl's dream. Though you're luckier than most; even your dream is half reality, did anyone but own they knew it.''

``I\textemdash I don't understand, my lady,'' Callie stammered humbly, not meeting the princess' eyes, her own fixed carefully on the floor.

``Of course you don't,'' Elaine said coldly. ``You've been brought up not to understand. But you know very well what I mean, and still you don't question. Blood is power, you little fool. Haven't I always treated you as the sister you are?''

``Yes, my lady.''

``That is not my name,'' Elaine snapped, pushing Callie away, clutching her upraised torch like a sword. ``You've seen the power I have\textemdash me, Elaine. And now you've seen what it's like to be the princess\textemdash as well be a prisoner! Why would you want any part of that, when I could set us both free?''

In the instant before Callie raised her eyes at last\textemdash Most people would be showing me the most wretched moment in their existence right about now\textemdash Riku realized he knew exactly what her answer would be.

``I love them,'' she said simply, lacing her hands tightly together as she straightened her shoulders, stiffened her spine. ``Your mother\textemdash she's always been kind to me. She only wants you to be safe, and happy. And the prince\textemdash ''

``Happy,'' Elaine broke in with a humorless laugh. ``Giving me away like property was supposed to make me happy?''

Caught by the wild gleam in Elaine's eyes\textemdash trapped, furious, and horribly familiar\textemdash he jumped at the touch on his shoulder, dragging him back from a sick rush of sympathy that made him wonder what Elaine's soul would show him if he asked. When he tore his eyes away, he almost expected the Dark to have anticipated his wish and done just that, but it was only Callie, the real one, her eyes suspiciously bright as she gripped his arm. ``Please,'' she said. ``Do we have to see the rest?''

``Elaine,'' Callie's soul-self was saying, voice breaking on the name. ``What happened to the guards on the way here? The servants didn't really run away, did they?''

``No,'' he said as Elaine began to laugh, brittle and lost\textemdash 

``You are a determined fool, aren't you? My mother's blood wasn't quite enough, you see\textemdash ''

\textemdash and as the world reformed around them in living color, this time only two things had changed: Zack's hand on the white horse's reins, holding it steady and still beneath him, and the dampness that spilled over Callie's lashes as she blinked against the sudden glare of the sun.

Though he was still reeling himself, he gathered his scattered thoughts as best he could, saying, ``I'm sorry. We can't spare anyone to take you back. If you're even still going back. But\textemdash ''

``She's found some sort of door,'' Callie said, pulling herself together and dashing a hand briskly across her eyes. ``If she wants it open that badly, you'd better stop her.''

``We will,'' Riku promised, glancing desperately at the others and\textemdash oh, Gaia, yes\textemdash finding them curious, baffled, but willing. ``Come on,'' he said. ``We've got to go.''

Zack was back in the saddle before the last word had quite left his mouth, was the first to follow when Riku clapped his heels to his horse's sides.

He really didn't know why he hadn't seen this coming. Not just that he was going to be the downfall of yet another princess. That the Dark wasn't done with him yet, and that he'd still walk right into its traps, even when the signs were impossible to miss. Sydney had warned him outright within five minutes of meeting the man.

You can't have been here a full day yet, or the city would have left its mark.

We should thank these people properly.

You should at least stay the night.

He ought to have been past being surprised by the so-called 'gifts' of the Dark.

It likes to change things.

But.

I won't keep you, Sydney had promised, and he'd been as good as his word\textemdash had let him go, the way Sephiroth had let him go, every single time, and when it came to the darkness, that was the one thing he knew to trust. And maybe this time, having come from Sydney, or his city, or the Dark itself\textemdash not gouged into him by Maleficent or grafted on by Xehanort's Heartless\textemdash maybe this time, it wouldn't be so bad.

And he was going to keep telling himself that until he had to explain it to the others, because he wasn't going to lay any bets that they'd see it the same way.

\fancybreak{\pfbreakdisplay}


The last leg of their ride to the caverns was nothing but a mad scramble, and though the map Osenar had drawn up for them was a good one, Zack was pretty sure it would only have been useful if it'd turned out to be a dead end. As closely as he'd been watching Riku, he noticed the instant the kid picked up the scent, probably literally, by the way his head jerked up, all that inward-looking worry just gone the moment he had a clear goal in front of him.

He didn't doubt that it was a useful trick to have, but it sort of made him want to sit the kid down and give him Standard Speech Fifty-Seven, which included the joys of sharing with others.

Well, that was his Standard Speech Fifty-Seven, anyway. Seph's went more like ``Risk yourself like that again, and I will hurt you with paperwork.'' Either one might possibly do in a pinch. With that Sora kid around, Riku had probably heard a paraphrase of Zack's before; at least Seph's would have the advantage of surprise.

He didn't know what had happened back there, but he had a pretty good guess, having seen that Losstarot guy do the same exact thing. Apparently somebody had been in a sharing mood and hadn't bothered to let anybody know in advance, but it wasn't like that was Riku's fault. As for worrying about it now\textemdash it wasn't like they didn't already know where mini-Boss' affinities lay, either. If anything, if anybody had to pick up weird new powers of darkness, he'd really rather it was someone like Riku, who at least had enough light to balance it out. Or Hall, who'd think it was the best thing since leveled materia, at least until the next new spell came along. Or Stiegler, who probably wouldn't even bother to use it unless it did something shiny to his weapons. Or\textemdash okay, so he was traveling with most of the people he'd trust like that, but that was exactly the point.

Apparently he had a little more work ahead of him before Riku came around to his way of thinking, but he was good for it. No one had ever accused him of being lazy.

Well, except for paperwork, but that didn't count.

It would have been cruel to hobble the horses when there were Heartless around, but they couldn't afford to be a man down when they didn't know what they were walking into, either. ``Never mind,'' Riku said as he slid out of the saddle under the cover of the trees, patting absently at his horse's neck but staring fixedly across the crumbling ford just down the slope, the dark cave mouth opening in the rock beyond. ``We can walk back if we have to. Is everyone ready?''

``Yeah,'' Zack said, taking a look around mainly for politeness' sake and getting back nothing but grim nods, a few cocky salutes. ``So it was the princess after all, huh?''

``Yeah. I think it's a curse,'' Riku muttered then looked immediately like he wished he'd kept his mouth shut. ``I'll try to talk to her, but\ldots once they start calling on the Heartless, they usually stop listening to anything else.'' From the bitter twist of his mouth, he sounded like he spoke from experience. ``Uh\ldots you'd probably better know. As princesses go, she completely looks the part.''

``Cute, sweet and innocent?'' Stiegler asked, arching a brow. When Riku nodded warily\textemdash and Zack wasn't going to ask how Riku knew that, not yet, anyway\textemdash the Sarge just grimaced. ``I fucking hate fairy tales. Bunch of idiots running around thinking a pretty face or some asshole prince is going to fix everything. Give me giants and crazy damn wizards any day.''

``He's all heart,'' Titus rumbled, laying a hand over his chest like he was touched, really, and Riku\textemdash 

Riku laughed, relaxing visibly, though he looked like there was plenty more he would have liked to add. For once the kid's eyes lacked that anticipatory gleam going into a fight, and that worried Zack. A lot.

Somehow he doubted it was a sudden attack of gentlemanly scruples that made Riku look like he was steeling himself for something unpleasant but necessary.

``All right,'' Riku said, shaking his head. ``But don't say I didn't warn you.''

It was dark inside the caverns, but not so dark SOLDIER eyes couldn't find enough light to navigate by. He was more worried about Riku, but when he glanced over to see whether the kid needed a guiding hand, he found Riku moving sure-footed as you please though he had his eyes closed. Trading disbelieving glances with Titus, Zack shrugged once, fought the urge to wave a hand in front of Riku's face just to see if he'd notice, and turned his attention back to the branching tunnels ahead. Two led off into the deeper gloom, smelled of stagnant water and dry bones, but from the third he caught a whiff of copper and iron, saw the far-off flicker of flame leaping against the rock.

A hand on Riku's shoulder had the kid turning his way, eyes peeling open and zeroing in on his own in the gloom, and there he went being surprised again when there was no bright aqua glow shining back at him. Not wanting to risk giving their arrival way with echoes if he spoke, he nodded instead toward the last tunnel, watched Riku narrow his eyes, take a deep breath, and nod back.

They closed in fast and quiet, warier by the moment as the expected resistance failed to materialize. There ought to at least have been Heartless, though Zack wasn't ruling out the possibility of an entire zombie army. After seeing what had happened to the horse, keeping an open mind was pretty much his motto.

Which wasn't to say that he didn't find what the torchlight revealed to be seriously disturbing. An open mind could only take you so far.

There were no cobwebs, no litter underfoot to suggest that bird or bat or beast had tried to den here in all the time the cavern must have stood abandoned, but it was hardly what you'd call clean. Slumped against the curving walls were the remains of a decent-sized escort: at least a dozen soldiers, a gaggle of maids and a small herd of teamsters, footmen, pages and heralds, a minstrel or a fool in motley who still looked surprised. The dusty rock at their backs was cluttered with freshly-drawn runes, and he hoped like anything that Hall would have the sense not to look too closely at any of it, because in the instant he recognized the clotted black ink for blood, something in his head sort of clicked, like seeing the buried image in a pattern of dots. Only what his eyes were telling him now was that those hastily-scrawled runes hadn't dripped\textemdash what they'd been written in had crawled right up the wall, black and lifeless before it ever left the pitiful vessels that had carried it, which meant someone had murdered thirty people in cold blood just to graffiti a wall by magic.

It must have worked, though. The thirtieth man\textemdash just a kid, really, in the plain homespun of a stableboy\textemdash was slumped at the foot of a door cut right into the rock, his blood not painting the wall behind him but crawling around the edges of the doorframe, runes glowing faintly blue around the edges.

Riku had warned them, but the girl standing at the dead boy's feet was still nothing Zack would have expected to see, not in a place like this. She had the sort of hair most women would kill for\textemdash longer than Tifa's, and that was saying something\textemdash looked as eerily innocent as a marble saint even in the midst of all this carnage. There was a sort of natural arrogance to the triumphant lift of her chin, the frustrated line of her mouth, like she wasn't at all surprised to have gotten this far and wasn't best pleased at being balked so close to her goal. Zack for one was grateful for the latter; if she'd managed to get that door open already, he imagined it'd probably be a lot more lively in here.

Slithering movement along the cavern floor caught his attention, and he darted a glance to the rock just in time to see a Shadow come oozing up out of the floor at the princess' feet. Antennae twitching urgently, it cocked its head as Elaine arched a brow, meeting round golden eyes with an attentive stare though the thing remained perfectly silent, like always.

Only maybe that was just a matter of perception, because when the princess turned, she was looking right at them, like she knew they'd be there even before she spotted them.

``Princess Elaine,'' Riku said abruptly, stepping out of the shadows all at once with his hands empty at his sides. If he'd hoped to catch the princess off-guard with that little stunt, it looked like he'd managed it. Holding her ground, Elaine looked him over with a wary, narrow-eyed stare, but there was curiosity in it too, and her first words were practically conversational.

``You're not from the court,'' she said, eyes flicking to the SOLDIERs behind Riku and back again. ``Any of you. Who are you, and why have you come?''

``Riku,'' the kid introduced himself, ``and I'm pretty sure you know why. The Heartless, and that door. You have no idea what's on the other side of it, do you?''

It hadn't occurred to Zack that the princess could maybe sense the darkness in Riku\textemdash and get it completely wrong\textemdash until the cautious friendliness buried under the haughty calm was snuffed out in a heartbeat.

``What's always on the other side of doors? A way out,'' Elaine replied with a delicate curl of lip, looking at Riku now like she'd just been propositioned by the goose boy.

``It's not like that,'' Riku said, letting the royal disdain roll right off him. ``That's not an exit; it's an invitation, and if anyone's told you differently\textemdash ''

``How would you know?'' the princess scoffed, glaring fiercely. ``Maybe you're the one who was lied to, my lord, to keep you obedient. Or did you think the world considers meekness a virtue only in princesses?''

It was the way Riku went utterly still, not looking at any of them or anywhere but the princess, and Zack just knew.

``I know because I've already opened one of those doors,'' Riku said, the words dragged from him with such raw honesty, you couldn't help believing him, even if it didn't seem possible. ``I wanted off my island, thought I'd do anything to escape, but I thought I'd be the one going through that door. I didn't realize I'd just be letting the Heartless in. They destroyed my world, Elaine\textemdash my friends died because of me, and the only ones that lived through it got flung halfway across the cosmos. I got my wish,'' he said wryly, with so much self-mockery Zack was surprised the edges didn't cut, ``but believe me, it wasn't worth it.''

Gaia. So that was it. Riku didn't just get Sephiroth; he'd been there himself, only without the comfort of insanity to blunt the awareness of what he'd done. It was no wonder he pushed himself so hard, was so determined to meet every challenge head-on, by himself. He was probably still trying to make up for that one mistake, so caught up in trying to save the universe he forgot to spare a little thought for himself while he was at it.

For just one moment, it looked like Riku might actually have gotten through to the girl as her eyes softened, her hand stealing to a necklace not nearly as fine as what he would have expected from a princess' wardrobe. It wasn't much of anything, just a pretty little flower of copper or brass, probably a gift from someone who couldn't afford gold or jewels, but her hand clenched on it until her knuckles stood out white as she made her choice.

``You're no hero, then,'' she said at last through a throat half-closed, her face hardening with determination.

Riku laughed like it cost him, shaking his head. ``About the furthest thing from it,'' he assured her, whipping out an arm and calling his Keyblade to hand in one fast burst of shadows. ``And you won't be the first princess to find that out.''

Riku was already moving as the princess shouted, ``Kill them!'' and all at once the caverns were full of Heartless. Neoshadows came bursting up through the floor and leaping down from the ceiling, Gargoyles and Armored Knights charging in from the tunnels at their backs. Nothing they couldn't handle; after so many years, fighting the Heartless had become as familiar as rifle drill cadence to a cadet. It was when the princess started chanting\textemdash and Hall went briefly cross-eyed, shaking his head like something nasty had just crawled up his ear\textemdash that Zack started to worry.

``We've got these,'' Titus called over his shoulder, one big hand closing on the scuff of a Neoshadow and driving it through a wall, stone cracking under his armor-plated knuckles. There was a weird moment where it looked like he was holding the stolen heart left behind after the Heartless shredded around it, a faint, ruddy glow nestled carefully in his half-curled hand, but then the heart drifted up and away, and Titus turned with a grin. ``Go remind mini-Boss that playing hero is a bad thing.''

``You got it,'' Zack promised, grinning back, and dove into the chaos of the main cavern with relief singing through him.

He was not at all surprised to find the dead had risen while he wasn't looking, slumped bodies standing clumsily up from the walls with their empty eye sockets shining with cold blue light. Unlike the dead of Leá Monde, these didn't look like they were seeing Riku as some sort of long-lost brother; they just looked hungry, like any one of them would do for a meal, Riku included. They were also a hell of a lot faster than they looked.

``Hey,'' Zack said between ducking the sweep of a pouncing Neoshadow's claws and throwing out an elbow to shatter the teeth that had been about to close on his arm. ``Mini-Boss.''

That got Riku's attention at least, though there was a little too much wariness in the clipped, ``What?'' he got in return.

``I owe you a lecture when we're done here. Number Fifty-Seven, standard version.''

Riku sidestepped, threw off a spell that bought them both a few yards of space, and risked a guarded glance Zack's way. ``Which one's that?''

``The joys of sharing with others.''

At least Riku's laugh this time didn't sound like he had teeth buried in his guts. He just wasn't prepared for it to cut off all at once, to follow Riku's horrified gaze and find the princess standing before that door, the door she was opening inch by inch, pulling with the help of the dead boy whose blood must have made it visible in the first place.

``Hall!'' Zack yelled, mostly on blind trust, but though he heard Hall start to rattle off a spell at his back\textemdash more of that tongue-knotting Ancient Kildean, if he had to take a guess\textemdash the floor-clearing blast of raw force that opened up a path before them came from the man on their right, from Steigler, who was staring at his sword like he'd never seen one in his life.

Break Art, one corner of Zack's mind was cataloging inanely, that must've been a Break Art, only Riot didn't show us any of those.

The rest of him was concerned with only one thing, and that was making it over to that door before they got it open any further, because the last thing he ever wanted to see was another planet trying to keep itself together long enough to throw its people safe.

He was halfway there, reminding himself that Hall did not fuck around as he dodged searing bolts of light that banished the dead in an instant, when a boiling rush of shadows shot past him, tight and focused. Riku, he thought\textemdash he'd seen that odd anti-light come from the Keyblade twice before\textemdash but where ordinary light could be deflected, diffused, this cut like a laser, slicing through lifeless meat and shadowflesh with the precision of a scalpel.

Apparently it worked on living flesh too, though maybe not the same way. All Zack knew was that Elaine must have heard him coming, because she left off tugging at the slowly-widening gap in that door long enough to turn his way, throw out her hands and draw breath to fire off a spell, though it never left her mouth. All that came out was a guttural cough as all the breath was forced from her chest, her huge eyes dropping in stunned disbelief to the long shaft of shadowlight piercing her heart.

Zack didn't stop to check on her\textemdash couldn't. Instead he sprinted the last few feet, turning so that it was his shoulder that hit the door first, and as he felt it slam seamlessly shut into the rock once more, he felt the click in his bones of the world locking shut. Which was bad for them, maybe, if Riku couldn't get them out again, but he wasn't about to ask for a do-over.

When he turned to look, the princess had already dropped to her knees, one hand pressing hard at her breastbone\textemdash or at that necklace again; he wasn't sure which. There wasn't time to ask, either, because he'd barely blinked before she began to dissolve at the edges, unraveling in ragged shadows and pale blue sparks that drifted like fireflies.

With their mistress gone and the world locked against reinforcements, the dead and the Heartless alike went down fast. Riku looked like he would have liked to have finished off the last of them himself, but not like his heart was really in it. More like he just needed the distraction. Zack might have indulged him, just this once, only that wouldn't go well with the lecture he still meant to give, and he didn't want to be the guy who taught mini-Boss bad habits. Sharing was good, whether it was sharing your troubles or sharing a fight. He was definitely pro-share.

So he kept Riku company while there were still Heartless to see to, stuck close even after the last Gargoyle went to pieces, and steeled himself for damage control, though he really hoped that was just pessimism on his part. It looked like he had a few minutes either way, at least, because Stiegler and Hall seemed to have everybody pretty well distracted.

``What the hell was that, anyway?'' Stiegler was grumbling, face screwed up in an offended snarl as Hall pushed him over to sit on what looked suspiciously like an old stone altar. ``I don't fucking do magic!''

``Well, I don't think it was magic you were burning, Sarge,'' Hall informed him distractedly. ``I think that was your body's own life energy, so will you sit the fuck down and let me look at you?''

``Goddamn mama chocobos,'' Stiegler muttered, rolling his eyes, but he took Hall's poking and prodding with what amounted to good grace, coming from him.

``That's\ldots I don't get it,'' Riku said suddenly, eyeing Stiegler in pure perplexity. They all looked up at that, but Riku barely seemed to notice. ``It's Leá Monde that's doing this\textemdash it's got to be\textemdash but\ldots you don't smell any different. Whatever it did to you, it wasn't dark.''

Stiegler frowned for a moment and scratched his nose, glancing swiftly at Zack and then back. ``Huh. That's good to know, I guess.'' He hunched a shoulder before Zack could leap into the silence that followed, saying, ``Wouldn't do me much good if it was; all that elemental crap just gives me a fucking headache.''

Riku opened his mouth but closed it again when nothing came out, his face going blank, Sephiroth-blank. And that was bad, but before he could close himself off entirely, something made him visibly start, half-turning with a dismayed curse to the door they'd closed.

``Think you can unlock it again?'' Zack asked lightly. He didn't remember seeing a Keyhole before, now that he thought about it, even when Riku had been locking the thing, and now even the door itself was hard to see, its edges blending smoothly with the blue rock around it.

``I'll have to try,'' Riku said, ``but later. We've got to get out of here.''

``Why's that?'' Titus asked, standing away from his comfortable lean against the wall, curious but willing.

``We've got to get back to the city,'' Riku said, looking faintly sick, ``before somebody sticks that maid in a barrel.''

Stiegler swore as he shot to his feet, and Hall didn't argue, hitting the Sarge with a double Curaga as the rest of them turned to scramble for the exit.

They didn't make it three steps before a flickering shine at their backs had them turning to look, all but Riku, who had his eyes closed in silent relief as the Keyhole flared to life where the now-vanished door had been.

Their horses had broken their tethers by the time they made it out, but someone had already done them the favor of rounding them up again. Several someones, in fact; it looked like the prince had brought his personal guard with him when he finally decided he'd had enough of waiting, and there were thirty well-armed men at his back as he watched them come out of the caverns and wade the ford to meet him. He didn't look nearly as pleased as Zack would have figured, and that was bad, but he had one arm looped around the princess' maid like he intended to protect her from all comers, and that was probably good. Especially when it looked like she was pleading their case, murmuring fast and urgent and casting worried glances Riku's way.

Riku didn't hesitate at all, pulling into the lead to march right up and give a perfectly formal bow\textemdash to the maid, not the prince.

``Princess Elaine,'' he said as he straightened, and Zack kept his own face solemn only with an effort. If Riku was about to pull off what he thought\textemdash 

The maid went pale, shaking her head. ``But\textemdash I'm not\textemdash ''

``It's all right,'' Riku said, his voice warmer than Zack could remember hearing it when Riku's friends weren't the topic of conversation, and he would have given a lot to know what look the kid was wearing at that moment. It left the prince torn between startled understanding and hope, but it just about melted the maid altogether, her eyes shining with the relief of a prisoner reprieved after the noose had already settled around her neck. ``The imposter is gone. Now the truth can come out.''

``Imposter,'' the prince echoed carefully, but already he looked lighter, the heavy air of a good man about to do something he'd sincerely regret lifting at Riku's earnest nod.

``It's a long story, but she confessed it all in the end. I'll explain the whole thing to the king.''

``In\ldots the end?'' the maid asked with a hitch in her voice, though she didn't sound surprised. Stricken but not surprised.

Riku nodded slowly. ``Yes. I'm sorry.''

He sounded like he meant it, but that wasn't exactly a surprise either.

\fancybreak{\pfbreakdisplay}


Half the city turned out for their return, which was something of a novel experience. He'd never had a crowd cheer him in the presence of a princess, and he was just as happy to hang back, let the prince take the lead. He could have the credit too, for all Riku cared; it was hardly going to matter after they left this world for good.

The one bad moment he had was when they circled around to the stable yard, with its big iron gate and the awful trophy that hung there\textemdash dark-eyed now, whatever magic that had animated it before faded to nothing. Falada, according to Callie\textemdash or Callisandra, he guessed he ought to call her\textemdash had always been able to talk, the enchantment a gift from Elaine's mother. Only the mare had been chocobo-stubborn, nearly ruining Elaine's disguise too many times by refusing to recognize any other mistress. Elaine had had it butchered in Callisandra's name, the head hung over the gate, half as a warning to her half-sister, half out of pure revenge as Elaine tried to force the creature to obey her in death as it hadn't in life. That even necromancy hadn't proven strong enough to break a mere horse's will had apparently been the last straw, what had convinced Elaine that her only options were escape or conquest.

He knew he'd done\ldots broadly the right thing, saved as many as he could, but he wished it hadn't happened like that. She'd just been\ldots like him, slowly strangling on the life everyone wanted for her, desperate to get out of that trap and make a life of her own devising. He'd just been luckier, because the people who loved him were enough when he let them be, and more than that\textemdash they'd loved him enough to let him go, to give him the push he needed to get there when he'd still been hesitating on the doorstep, afraid of hurting them again. And maybe Mickey was right, and living for other people wasn't really the answer, not in the long run, but at least it beat destroying a world just because he felt claustrophobic in his own skin.

So he'd remember this world, tuck it away and try to take some kind of meaning from it, but he wouldn't let himself wallow in guilt over it. Kairi would kick his ass if Sora didn't beat her to it, and Mickey would give him one of those level-eyed stares that made him feel like spilling his guts and paradoxically, preemptively better, all at the same time, and Sephiroth\ldots Sephiroth would just listen. He was pretty good at that, actually.

Which made it sort of ironic that Zack apparently wanted to talk. He couldn't imagine how those two could be more totally each other's opposite, but that was probably what made it work.

Funnily enough, that was just what people tended to say about him and Sora.

He'd expected the king to be a tougher nut to crack, but it only took a private audience and the recounting of a few hard facts to bring the guy around.

``They do look very similar,'' the old man granted, glancing tiredly from Riku to the prince and back, ignoring Zack standing at parade rest in place of the guards that should have been stationed at the privy chamber door. ``But\ldots you know very well that she is not the princess. Her family\textemdash ''

``Her family,'' Riku interrupted, ``are too busy squabbling over the succession and hoping you won't notice you've got what would have been the heir in your pocket. You're also talking about a girl who murdered her own mother, thirty soldiers and civilians, was apparently an accomplished necromancer, and who tried to open your world to the Heartless. I think they'd rather put up with having Elaine's half-sister on the neighboring throne than having all that made public. Besides\ldots they probably won't even notice,'' he added with a faint grimace. ``For a lot of people, a princess isn't much different than a servant. She just has better clothes.''

``True enough,'' the king said with a faint little smile, oddly nostalgic, and Riku wondered all at once where his queen was, what sort of princess she'd been and why the castle servants all looked so content. Maybe it was more than just living in the heart of a wealthy, peaceful country, under a king who wasn't growing old prematurely wondering when his heir would stick a knife in his back. He wondered if the queen had come up from the kitchens or the chambermaids, or if she'd been a goose girl herself, Callisandra's quiet hint that she'd stand aside if her sister ever came back to her senses.

``Very well,'' the king said, clapping his thin hands together as he took up a regal expression once more. ``Officially, I believe your report of the traitor's confession, that she conspired to supplant the Princess Elaine as my son's betrothed and called upon dark magics to muddle the minds of any who might oppose her plot. Privately,'' he added with a tiny smile, ``I think you are a dangerously clever young man and would grant you lands and title in my own court if I could. But I suspect we have different wishes on the matter.''

``It's an honor, Your Majesty,'' he said with a faint smirk, ``but I'm afraid we can't stay.''

``Well,'' the king replied, waving off any objection he might have made, ``you obviously can't go yet. You'll miss the wedding feast.''

He really would have liked to argue, but he was exhausted from two close battles in as many days, adrenaline-shaky from gearing himself up to outfox or outargue a king, heartsick from what he'd done to the real princess and heartsore from what he'd had to admit aloud in front of people he'd begun to think of as friends, and right now a good meal and a soft bed were nearly the only things he wanted in the world.

``I could eat,'' he admitted, forgetting his manners entirely, but that just made the king laugh outright in patent delight.

\fancybreak{\pfbreakdisplay}


He didn't catch up with Riku until the small army of tailors had been routed\textemdash by the chambermaids, actually, and it turned out the flirty one had a tongue that could strip paint and that the shy one wasn't actually shy in the least. He wouldn't want to be on their bad sides, but the pair had apparently adopted the SOLDIERs, so he guessed that meant he was probably safe.

Riku was still looking faintly traumatized by all the attention when Zack let himself into the master suite, knocking politely on the door but not waiting for an invitation. The girls had just been in here, so Riku had to be decent, and if he gave the guy a choice, they'd probably never have this conversation.

It felt a little weird, but he closed the door behind him anyway before wandering over to sit on the edge of the bed, leaning back on his hands. ``Hey,'' he said, waiting for Riku to look over at him from his perch on the window seat. ``Wanna talk about it?''

He hadn't been sure that would work\textemdash Cloud would have clammed up tighter than a bank vault, while Seph would have either flatly told him 'No,' or else just enough to make him really worried\textemdash but Riku just got very, very still\ldots then squared himself up, met Zack's eyes like he was facing his own firing squad, and let it all spill out.

Riku was already talking before Zack worked out it was because Riku thought he owed it to them, and by then it was too late to stop him.

So he heard it all. About the islands, and hearing a voice that for the longest time had claimed to be Ansem; about being found by Maleficent and going to work for her, thinking it was okay to be used so long as he could use her in return. Looking for his friends, and finding the princesses, and getting everything all mixed up. He talked about Sephiroth too, a Sephiroth Zack barely recognized, so crazy anyone sane would have run\textemdash and how bad had it been that in that place, in that time, he'd been the one steady thing Riku had? It was almost a relief to hear the rest of it\textemdash getting lost in the darkness but finding that Mickey of his on the way\textemdash and how crazy was it that the best and most powerful king in the known cosmos was a mouse? Losing his body to that Heartless again, but helping to put his friend back together with his own two hands. Becoming himself again, going home\ldots and when he realized he'd never fit there again, having his own best friends pack his bags and take him back to the place\textemdash the person\textemdash he was meant to be.

Riku looked sort of guilty about that\textemdash looked sort of like he was just waiting for Zack to stand in judgment over him, which meant he really wasn't thinking clearly\textemdash but Zack wasn't about to begrudge him. For all Riku kept saying how much Sephiroth had done for him, he didn't seem to see how much he'd done for Sephiroth at the same time, and it wasn't like Zack had had any claim on the man in the first place. He wished Sephiroth were here right now, in fact, because no one should look as alone as Riku did, sitting there waiting for the other boot to drop.

``Hey,'' he said as gently as he could, holding out an arm. ``C'mere.''

``What?'' Riku asked\textemdash a shell-shocked 'what,' not a suspicious 'why,' so Zack gave him the biggest, most ridiculous grin in his arsenal.

``Therapy hug,'' he explained, waggling his fingers, and found himself grinning even wider when Riku broke with a laugh.

``You're crazy,'' Riku protested, but damned if he didn't get up, stumbling over like the confession had exhausted him completely and dropping down at Zack's side. He didn't even complain much when Zack scruffled his hair, just sort of went limp with pure relief.

``You know,'' Zack said, propping Riku up against his side, ``you're going to have to get used to it eventually.''

He figured Riku would probably try to pull away, was prepared to hug him back to complacency if he had to, but Riku just asked, ``Used to what?'' More tired than wary.

``You've got excellent taste in friends,'' Zack explained, only about half teasing. ``One of these days, it's going to sink in that we're not going to tar and feather you for being human.''

And one of these days, Riku might even feel like he deserved that, but his wistful little smile was not pointing to today as being that day.

``Anyway, c'mon,'' he said, ruffling Riku's hair a final time and petting it flat again. ``That wedding's tomorrow, and we were thinking it'd only be polite to get them a gift. And Hall's got this awesome spell to alchemize pretty much any metal you can think of, and the Sarge can forge pretty much anything you can think of, but we're going to need you to convince the blacksmith to let us in.''

``You're going to get us kicked out of here,'' Riku groaned, but not like he meant it. More like he knew Zack was arranging a distraction and was grateful enough to let it happen.

No one seemed to be paying them any particular attention when they emerged from the bedroom, but that was the thing about SOLDIER senses; if you didn't want to find yourself eavesdropping, it usually meant you had to find excuse to take a long walk, and the guys were all there. Minding their own business, but definitely in earshot. He wondered for about half a moment whether he ought to be protesting his own innocence or thanking Gaia that Riku wasn't quite as familiar with all the quirks that made up a SOLDIER when Titus shot a pitying look in his direction and Riku gave him a completely gratuitous 'no-really-I'm-fine' smirk.

Which suggested firstly that the only one seriously worried about him molesting Sephiroth's boyfriend was him, and secondly that Riku understood the enhanced hearing thing just fine, thank you, and had only wanted to say it once, to one pair of eyes, and have it over with as painlessly as possible. And that was fine all around.

``Oh, hey,'' Hall said suddenly, sitting up straight like he'd just had a wonderful thought. ``So if Riku's manifesting Sydney's talents and the Sarge has picked up Break Arts\ldots does that mean the rest of us are going to start showing weird powers now too?''

``Oh, Gaia,'' Zack swore\ldots and since he had an echo, turned to the left.

And Riku grinned at him, battered but light-hearted, as they finished in unison: ``Well, now that you've jinxed us, anything's possible.''

